### 2022-03-27 inputs/data/datasheet_template.Rmd
Update scripts

---
title: "My title"
subtitle: "My subtitle if needed"
author: 
  - Pascal Lee Slew
  - Yunkyung Park
thanks: "Code and data are available at: LINK."
date: "`r format(Sys.time(), '%d %B %Y')`"
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
output:
  bookdown::pdf_document2
toc: FALSE
bibliography: references_datasheet.bib
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Extract of the questions from @gebru2021datasheets

**Motivation**

1. *For what purpose was the dataset created? Was there a specific task in mind? Was there a specific gap that needed to be filled? Please provide a description.*
    - The dataset was created to enable analysis of Australian politicians. We were unable to find a publicly available dataset in a structured format that had the biographical and political information on Australian politicians that was needed for modelling.
2. *Who created the dataset (for example, which team, research group) and on behalf of which entity (for example, company, institution, organization)?*
    - TBD
3. *Who funded the creation of the dataset? If there is an associated grant, please provide the name of the grantor and the grant name and number.*
    - TBD
4. *Any other comments?*
    - TBD

**Composition**

1. *What do the instances that comprise the dataset represent (for example, documents, photos, people, countries)? Are there multiple types of instances (for example, movies, users, and ratings; people and interactions between them; nodes and edges)? Please provide a description.*
	- TBD
2. *How many instances are there in total (of each type, if appropriate)?*
	- TBD
3. *Does the dataset contain all possible instances or is it a sample (not necessarily random) of instances from a larger set? If the dataset is a sample, then what is the larger set? Is the sample representative of the larger set (for example, geographic coverage)? If so, please describe how this representativeness was validated/verified. If it is not representative of the larger set, please describe why not (for example, to cover a more diverse range of instances, because instances were withheld or unavailable).*
	- TBD
4. *What data does each instance consist of? "Raw" data (for example, unprocessed text or images) or features? In either case, please provide a description.*
	- TBD
5. *Is there a label or target associated with each instance? If so, please provide a description.*
	- TBD
6. *Is any information missing from individual instances? If so, please provide a description, explaining why this information is missing (for example, because it was unavailable). This does not include intentionally removed information, but might include, for example, redacted text.*
	- TBD
7. *Are relationships between individual instances made explicit (for example, users' movie ratings, social network links)? If so, please describe how these relationships are made explicit.*
	- TBD
8. *Are there recommended data splits (for example, training, development/validation, testing)? If so, please provide a description of these splits, explaining the rationale behind them.*
	- TBD
9. *Are there any errors, sources of noise, or redundancies in the dataset? If so, please provide a description.*
	- TBD
10. *Is the dataset self-contained, or does it link to or otherwise rely on external resources (for example, websites, tweets, other datasets)? If it links to or relies on external resources, a) are there guarantees that they will exist, and remain constant, over time; b) are there official archival versions of the complete dataset (that is, including the external resources as they existed at the time the dataset was created); c) are there any restrictions (for example, licenses, fees) associated with any of the external resources that might apply to a dataset consumer? Please provide descriptions of all external resources and any restrictions associated with them, as well as links or other access points, as appropriate.*
	- TBD
11. *Does the dataset contain data that might be considered confidential (for example, data that is protected by legal privilege or by doctor-patient confidentiality, data that includes the content of individuals' non-public communications)? If so, please provide a description.*
	- TBD
12. *Does the dataset contain data that, if viewed directly, might be offensive, insulting, threatening, or might otherwise cause anxiety? If so, please describe why.*
	- TBD
13. *Does the dataset identify any sub-populations (for example, by age, gender)? If so, please describe how these subpopulations are identified and provide a description of their respective distributions within the dataset.*
	- TBD
14. *Is it possible to identify individuals (that is, one or more natural persons), either directly or indirectly (that is, in combination with other data) from the dataset? If so, please describe how.*
	- TBD
15. *Does the dataset contain data that might be considered sensitive in any way (for example, data that reveals race or ethnic origins, sexual orientations, religious beliefs, political opinions or union memberships, or locations; financial or health data; biometric or genetic data; forms of government identification, such as social security numbers; criminal history)? If so, please provide a description.*
	- TBD
16. *Any other comments?*
	- TBD

**Collection process**

1. *How was the data associated with each instance acquired? Was the data directly observable (for example, raw text, movie ratings), reported by subjects (for example, survey responses), or indirectly inferred/derived from other data (for example, part-of-speech tags, model-based guesses for age or language)? If the data was reported by subjects or indirectly inferred/derived from other data, was the data validated/verified? If so, please describe how.*
	- TBD
2. *What mechanisms or procedures were used to collect the data (for example, hardware apparatuses or sensors, manual human curation, software programs, software APIs)? How were these mechanisms or procedures validated?*
	- TBD
3. *If the dataset is a sample from a larger set, what was the sampling strategy (for example, deterministic, probabilistic with specific sampling probabilities)?*
	- TBD
4. *Who was involved in the data collection process (for example, students, crowdworkers, contractors) and how were they compensated (for example, how much were crowdworkers paid)?*
	- TBD
5. *Over what timeframe was the data collected? Does this timeframe match the creation timeframe of the data associated with the instances (for example, recent crawl of old news articles)? If not, please describe the timeframe in which the data associated with the instances was created.*
	- TBD
6. *Were any ethical review processes conducted (for example, by an institutional review board)? If so, please provide a description of these review processes, including the outcomes, as well as a link or other access point to any supporting documentation.*
	- TBD
7. *Did you collect the data from the individuals in question directly, or obtain it via third parties or other sources (for example, websites)?*
	- TBD
8. *Were the individuals in question notified about the data collection? If so, please describe (or show with screenshots or other information) how notice was provided, and provide a link or other access point to, or otherwise reproduce, the exact language of the notification itself.*
	- TBD
9. *Did the individuals in question consent to the collection and use of their data? If so, please describe (or show with screenshots or other information) how consent was requested and provided, and provide a link or other access point to, or otherwise reproduce, the exact language to which the individuals consented.*
	- TBD
10. *If consent was obtained, were the consenting individuals provided with a mechanism to revoke their consent in the future or for certain uses? If so, please provide a description, as well as a link or other access point to the mechanism (if appropriate).*
	- TBD
11. *Has an analysis of the potential impact of the dataset and its use on data subjects (for example, a data protection impact analysis) been conducted? If so, please provide a description of this analysis, including the outcomes, as well as a link or other access point to any supporting documentation.*
	- TBD
12. *Any other comments?*
	- TBD

**Preprocessing/cleaning/labeling**

1. *Was any preprocessing/cleaning/labeling of the data done (for example, discretization or bucketing, tokenization, part-of-speech tagging, SIFT feature extraction, removal of instances, processing of missing values)? If so, please provide a description. If not, you may skip the remaining questions in this section.*
	- TBD
2. *Was the "raw" data saved in addition to the preprocessed/cleaned/labeled data (for example, to support unanticipated future uses)? If so, please provide a link or other access point to the "raw" data.*
	- TBD
3. *Is the software that was used to preprocess/clean/label the data available? If so, please provide a link or other access point.*
	- TBD
4. *Any other comments?*
	- TBD

**Uses**

1. *Has the dataset been used for any tasks already? If so, please provide a description.*
	- TBD
2. *Is there a repository that links to any or all papers or systems that use the dataset? If so, please provide a link or other access point.*
	- TBD
3. *What (other) tasks could the dataset be used for?*
	- TBD
4. *Is there anything about the composition of the dataset or the way it was collected and preprocessed/cleaned/labeled that might impact future uses? For example, is there anything that a dataset consumer might need to know to avoid uses that could result in unfair treatment of individuals or groups (for example, stereotyping, quality of service issues) or other risks or harms (for example, legal risks, financial harms)? If so, please provide a description. Is there anything a dataset consumer could do to mitigate these risks or harms?*
	- TBD
5. *Are there tasks for which the dataset should not be used? If so, please provide a description.*
	- TBD
6. *Any other comments?*
	- TBD

**Distribution**

1. *Will the dataset be distributed to third parties outside of the entity (for example, company, institution, organization) on behalf of which the dataset was created? If so, please provide a description.*
	- TBD
2. *How will the dataset be distributed (for example, tarball on website, API, GitHub)? Does the dataset have a digital object identifier (DOI)?*
	- TBD
3. *When will the dataset be distributed?*
	- TBD
4. *Will the dataset be distributed under a copyright or other intellectual property (IP) license, and/or under applicable terms of use (ToU)? If so, please describe this license and/ or ToU, and provide a link or other access point to, or otherwise reproduce, any relevant licensing terms or ToU, as well as any fees associated with these restrictions.*
	- TBD
5. *Have any third parties imposed IP-based or other restrictions on the data associated with the instances? If so, please describe these restrictions, and provide a link or other access point to, or otherwise reproduce, any relevant licensing terms, as well as any fees associated with these restrictions.*
	- TBD
6. *Do any export controls or other regulatory restrictions apply to the dataset or to individual instances? If so, please describe these restrictions, and provide a link or other access point to, or otherwise reproduce, any supporting documentation.*
	- TBD
7. *Any other comments?*
	- TBD

**Maintenance**

1. *Who will be supporting/hosting/maintaining the dataset?*
	- TBD
2. *How can the owner/curator/manager of the dataset be contacted (for example, email address)?*
	- TBD
3. *Is there an erratum? If so, please provide a link or other access point.*
	- TBD
4. *Will the dataset be updated (for example, to correct labeling errors, add new instances, delete instances)? If so, please describe how often, by whom, and how updates will be communicated to dataset consumers (for example, mailing list, GitHub)?*
	- TBD
5. *If the dataset relates to people, are there applicable limits on the retention of the data associated with the instances (for example, were the individuals in question told that their data would be retained for a fixed period of time and then deleted)? If so, please describe these limits and explain how they will be enforced.*
	- TBD
6. *Will older versions of the dataset continue to be supported/hosted/maintained? If so, please describe how. If not, please describe how its obsolescence will be communicated to dataset consumers.*
	- TBD
7. *If others want to extend/augment/build on/contribute to the dataset, is there a mechanism for them to do so? If so, please provide a description. Will these contributions be validated/verified? If so, please describe how. If not, why not? Is there a process for communicating/distributing these contributions to dataset consumers? If so, please provide a description.*
	- TBD
8. *Any other comments?*
	- TBD

\newpage

# References

### 2022-03-27 scripts/00-simulation.R

@@ -1,11 +1,15 @@
 #### Preamble ####
-# Purpose: Simulate
+# Purpose: Clean the survey data downloaded from [...UPDATE ME!!!!!]
 # Author: Pascal Lee Slew, Yunkyung Park
-# Email: pascal.leeslew@mail.utoronto.ca, clara.park@mail.utoronto.ca
-# Date: 3 April 2022
-# Prerequisites: - 
+# Data: 3 April 2022
+# Contact: pascal.leeslew@mail.utoronto.ca, clara.park@mail.utoronto.ca
+# License: MIT
+# Pre-requisites: 
+# - Need to have downloaded the ACS data and saved it to inputs/data
+# - Don't forget to gitignore it!
 
 #### Workspace set-up ####
 library(janitor)
 library(lubridate)
 library(tidyverse)
+

### 2022-03-27 scripts/01-gather_data.R

@@ -1,95 +1,60 @@
 #### Preamble ####
+# Purpose: Download one 'Final Report' from the DHS Program in a PDF form
+# and gather the data by parsing the PDF
+# Author: Pascal Lee Slew, Yunkyung Park
+# Data: 3 April 2022
+# Contact: pascal.leeslew@mail.utoronto.ca, clara.park@mail.utoronto.ca
+# License: MIT
+# Pre-requisites: 
+# - Don't forget to gitignore it!
 
+#### Workspace set-up ####
 # install.packages('pdftools')
-# install.packages('purrr')
 # install.packages('stringi')
-# install.packages('janitor')
-# install.packages('tidyverse')
-
-library(janitor)
 library(pdftools)
-library(purrr)
 library(tidyverse)
 library(stringi)
 
 download.file("https://dhsprogram.com/pubs/pdf/FR106/FR106.pdf",
-              "1988_Ghana_DHS.pdf",
+              "outputs/literature/1988_Ghana_DHS.pdf",
               mode="wb")
 
+report <- pdf_text("outputs/literature/1988_Ghana_DHS.pdf")
 
-all_content <- pdf_text("1988_Ghana_DHS.pdf")
+page_45<-stri_split_lines(report[[45]])[[1]]
+page_45<-page_45[page_45 != ""]
 
-get_data <- function(i){
-  # i = 467
-  # Just look at the page of interest
-  # Based on Bob Rudis: https://stackoverflow.com/a/47793617
-  just_page_i <- stri_split_lines(all_content[[i]])[[1]] 
-  
-  just_page_i <- just_page_i[just_page_i != ""]
-  
-  # Grab the type of table
-  type_of_table <- just_page_i[1] %>% str_squish() # 1
-  
-  # Get rid of the top matter
-  # Manually for now, but could create some rules if needed
-  just_page_i_no_header <- just_page_i[12:43] # 12:43
-  
-  # Convert into a tibble
-  demography_data <- tibble(all = just_page_i_no_header)
-  
-  # Split columns
-  demography_data <-
-    demography_data %>%
-    mutate(all = str_squish(all)) %>% # Any space more than two spaces is reduced
-    mutate(all = str_replace(all, ",", "")) %>%
-    mutate(all = str_replace(all, "Greater Accra", "Greater_Accra")) %>%
-    mutate(all = str_replace(all, "Brong Ahafo", "Brong_Afaho")) %>%
[…]

### 2022-03-27 scripts/02-clean_and_prepare_data.R

@@ -1,28 +1,44 @@
 #### Preamble ####
+# Purpose: Clean and prepare the 1988 Ghana census data downloaded from the DHS Program
+# Author: Pascal Lee Slew, Yunkyung Park
+# Data: 3 April 2022
+# Contact: pascal.leeslew@mail.utoronto.ca, clara.park@mail.utoronto.ca
+# License: MIT
+# Pre-requisites: 
+# - Need to have downloaded the 1988 Ghana census data by following the process 
+# in 01-gather_data.R and saved it to outputs/data
+# - Don't forget to gitignore it!
 
-library(janitor)
+#### Workspace set-up ####
 library(tidyverse)
 
-raw_data <- read_csv("raw_data.csv")
+raw_data <- read_csv("outputs/data/raw_data.csv")
 
 col_len <- ncol(raw_data)
   
 clean <- as_tibble(raw_data)
-clean$charact <- (rowSums(is.na(clean)) == col_len-1)
+clean$character <- (rowSums(is.na(clean)) == col_len-1)
 
 index <- 1:nrow(clean)
 j<-0
 while (j < nrow(clean)-1){
   j<-j+1
-  if (clean[j,]$charact == TRUE){
+  if (clean[j,]$character == TRUE){
     i<-j
   }
   
   index[j]<-clean[i,]$background
 }
 
-index[nrow(clean)]<-""
-clean$charact<-index
+index[nrow(clean)]<-"Total"
+clean$character<-index
 clean <-
   clean %>%
   na.omit()
+
+rm(col_len,
+   index,
+   i,
+   j)
+
+write_csv(clean, "outputs/data/cleaned_data.csv")

### 2022-03-28 outputs/paper.Rmd
Initial commit

---
title: "paper"
author: 
  - Pascal Lee Slew
  - Yunkyung Park
thanks: "Code and data are available at: https://github.com/Pascal-304/dhs_analysis."
date: "`r format(Sys.time(), '%d %B %Y')`"
abstract: "Four sentences"
output:
  bookdown::pdf_document2
toc: FALSE
bibliography: references.bib
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r library, echo=FALSE, message=FALSE}
# install.packages('bookdown')
# install.packages("stringr")
library(stringr) 
library(dplyr)
library(tidyverse) 
library(janitor)
library(ggplot2)
library(knitr)
library(kableExtra)
library(bookdown)
```

```{r readdata, echo=FALSE}
ghana<-read_csv('data/cleaned_data.csv', show_col_types = FALSE)
```

# Introduction

# Data

```{r data, echo=FALSE, fig.cap="Data"}
ghana %>%
  group_by(character) %>%
  summarise(sum = sum(number_of_employed_women))
```

Table \@ref(tab:data) shows that 3,566 participated the survey, but there are 3 whom did not answer their employment status, etc.

\newpage

# References

### 2022-03-28 scripts/00-simulation.R

@@ -1,11 +1,10 @@
 #### Preamble ####
-# Purpose: Clean the survey data downloaded from [...UPDATE ME!!!!!]
+# Purpose: Simulate some data that could resemble the 1988 Ghana census dataset.
 # Author: Pascal Lee Slew, Yunkyung Park
 # Data: 3 April 2022
 # Contact: pascal.leeslew@mail.utoronto.ca, clara.park@mail.utoronto.ca
 # License: MIT
 # Pre-requisites: 
-# - Need to have downloaded the ACS data and saved it to inputs/data
 # - Don't forget to gitignore it!
 
 #### Workspace set-up ####
@@ -13,3 +12,56 @@ library(janitor)
 library(lubridate)
 library(tidyverse)
 
+#### Simulate data ####
+set.seed(304)
+
+items<-c("no_child_under_six", "one_more_child_under_six", 
+         "respondent", "partner", "other_relative", "neighbor", 
+         "hired", "child_in_school", "other_female_child", 
+         "other_male_child", "not_worked_since_birth", "other", 
+         "missing")
+
+num_of_items <- length(items)
+
+simulated_dhs <-
+  tibble(
+    background = 
+      c(
+        rep("Urban", num_of_items),
+        rep("Rural", num_of_items),
+        rep("Western", num_of_items),
+        rep("Central", num_of_items),
+        rep("Greater_Accra", num_of_items),
+        rep("Volta", num_of_items),
+        rep("Eastern", num_of_items),
+        rep("Ashanti", num_of_items),
+        rep("Brong_Ahafo", num_of_items),
+        rep("Northern", num_of_items),
+        rep("Upper_West", num_of_items),
+        rep("Upper_East", num_of_items),
+        rep("No_education", num_of_items),
+        rep("Primary", num_of_items),
+        rep("Middle", num_of_items),
+        rep("Secondary+", num_of_items),
+        rep("For_family_member", num_of_items),
+        rep("For_someone_else", num_of_items),
+        rep("Self-employed", num_of_items),
+        rep("Agricultural", num_of_items),
+        rep("Nonagricultural", num_of_items),
+        rep("All_year_full_week", num_of_items),
+        rep("All_year_part_week", num_of_items),
+        rep("Seasonal", num_of_items),
+        rep("Occasional", num_of_items),
+        rep("Total", num_of_items)
+      ),
+    item =
+      c(
+        rep(item, 26)
+      ),
+    proportion = 
[…]

### 2022-03-28 outputs/paper.Rmd
Update paper.Rmd

@@
 
+# Results
+
+# Mother's education
+
+```{r motheredu, echo=FALSE, fig.cap="Mother's Education level"}
+mother_edu <-
+  ghana %>%
+  filter(character=="Mother\'s_education") %>%
+  mutate(
+    background = factor(background,
+                        levels = c('No_education',
+                                   'Primary',
+                                   'Middle',
+                                   'Secondary+')
+    )
+  )
+
+mother_edu %>%
+  ggplot(mapping=aes(x=background, y=number_of_employed_women, fill=background)) +
+  geom_bar(width = 1, stat = "identity", color = "white") +
+  geom_text(aes(label=paste(round(number_of_employed_women/sum(number_of_employed_women),4)*100, '%')), size=4, position=position_stack(vjust = 0.5)) +
+  theme_minimal() +
+  labs(x='education level',y='count') +
+  theme(legend.position='none')
+```
+
 \newpage

### 2022-03-29 outputs/paper.Rmd
Include figures

--- 2022-03-28 outputs/paper.Rmd
@@
 
-```{r data, echo=FALSE, fig.cap="Data"}
+```{r total, echo=FALSE, fig.cap="Data"}
 ghana %>%
+  mutate(
+    character = factor(character,
+                       levels=c("Residence",
+                                "Region",
+                                "Mother\'s_education",
+                                "Work_status",
+                                "Occupation",
+                                "Employment_status",
+                                "Total"
+                                )
+                       )
+           ) %>%
   group_by(character) %>%
@@
 
-Table \@ref(tab:data) shows that 3,566 participated the survey, but there are 3 whom did not answer their employment status, etc.
+Table \@ref(tab:total) shows that 3,566 participated the survey, but there are 3 whom did not answer their employment status, etc.
+
+```{r data, echo=FALSE}
+ghana %>%
+  select(background, no_child_under_six, one_more_child_under_six, caretaker_respondent, character) %>%
+  slice(1:10) %>%
+  kable(caption='A subset of key features',
+        col.names = c('Background', 'No child under six', '1+ child under six', 
+                      'Child\'s caretaker - respondent', 'Character'),
+        digits = 1,
+        booktabs = FALSE,
+        linesep = "")
+```
+
+# Results
+
+## Mother's education
+
+```{r motheredu, echo=FALSE, message=FALSE, fig.cap="Mother's Education level"}
+mother_edu <-
+  ghana %>%
+  filter(character=="Mother\'s_education") %>%
+  mutate(
+    no_child_under_six = round(no_child_under_six/100 * number_of_employed_women, 0),
+    one_more_child_under_six = round(one_more_child_under_six/100 * number_of_employed_women, 0)
+  )
+
+mother_edu_tb<-
+  tibble(
+    background =
+      c(""),
+    child_under_six = 
+      c("")
+  )
+
+for (r in 1:nrow(mother_edu)){
+  level <- mother_edu$background[r]
+  edu <-
+    tibble(
+      background = 
+        c(
+          rep(level, mother_edu$number_of_employed_women[r])
+        ),
+      child_under_six = 
+        c(
+          rep("No_child_under_six", mother_edu$no_child_under_six[r]),
+          rep("One_more_child_under_six", mother_edu$one_more_child_under_six[r])
+        )
+      )
+
+  mother_edu_tb <- bind_rows(mother_edu_tb, edu)
+  rm(level,
+     edu)
+}
+rm(r)
+mother_edu_tb <- mother_edu_tb[-c(1),]
+
+mother_edu_tb <-
+  mother_edu_tb %>%
+  mutate(
+    background = factor(background,
+                        levels = c('No_education',
+                                   'Primary',
+                                   'Middle',
+                                   'Secondary+')
+                        )
+    )
+
+mother_edu_tb %>%
+  ggplot(mapping=aes(x=background, fill=child_under_six)) +
+  geom_bar(position='dodge') +
+  theme_minimal() +
+  labs(x='education level', y='number of employed', fill='Child under six') +
+  scale_x_discrete(labels = c("No_education" = "No education")) +
+  scale_fill_discrete(labels = c("No child under six", 
+                                 "One or more child under six"))
+
+rm(mother_edu_tb)
+```
+
+Figure \@ref(fig:motheredu) shows that there are less women who studied more than secondary school, and only the secondary+ turned out to be more likely to have no child under six.
+
+```{r mothereduchildcare, echo=FALSE, fig.cap="Distribution of child's caretaker by mother's education level"}
+mother_edu <-
+  mother_edu %>%
+  mutate(
+    caretaker_respondent = round(caretaker_respondent/100 * one_more_child_under_six, 0),
+    caretaker_partner = round(caretaker_partner/100 * one_more_child_under_six, 0),
+    caretaker_other_relative = round(caretaker_other_relative/100 * one_more_child_under_six, 0),
+    caretaker_neighbor = round(caretaker_neighbor/100 * one_more_child_under_six, 0),
+    caretaker_hired = round(caretaker_hired/100 * one_more_child_under_six, 0),
+    caretaker_child_in_school = round(caretaker_child_in_school/100 * one_more_child_under_six, 0),
+    caretaker_other_female_child = round(caretaker_other_female_child/100 * one_more_child_under_six, 0),
+    caretaker_other_male_child = round(caretaker_other_male_child/100 * one_more_child_under_six, 0),
+    caretaker_not_worked_since_birth = round(caretaker_not_worked_since_birth/100 * one_more_child_under_six, 0),
+    caretaker_other = round(caretaker_other/100 * one_more_child_under_six, 0),
+    caretaker_missing = round(caretaker_missing/100 * one_more_child_under_six, 0)
+    ) %>%
+  mutate(
+    caretaker_other_female_child = caretaker_other_female_child + caretaker_other_male_child
+  ) %>%
+  select(-caretaker_other_male_child) %>%
+  rename(caretaker_other_child = caretaker_other_female_child)
+
+mother_edu_tb<-
+  tibble(
+    background =
+      c(""),
+    child_caretaker = 
+      c("")
+  )
+
+# clean_caretaker <- 
+#   mother_edu %>%
+#   select(starts_with("caretaker_")) %>%
+#   mutate(sum_caretaker = rowSums(.))
+# clean_caretaker$num <-
+#   mother_edu$one_more_child_under_six
+
+mother_edu[3, 13] <- 0
+mother_edu[3, 11] <- mother_edu[3, 11] - 1
+
+for (r in 1:nrow(mother_edu)){
+  level <- mother_edu$background[r]
+  edu <-
+    tibble(
+      background = 
+        c(
+          rep(level, mother_edu$one_more_child_under_six[r])
+        ),
+      child_caretaker = 
+        c(
+          rep("respondent", mother_edu$caretaker_respondent[r]),
+          rep("partner", mother_edu$caretaker_partner[r]),
+          rep("other_relative", mother_edu$caretaker_other_relative[r]),
+          rep("neighbor", mother_edu$caretaker_neighbor[r]),
+          rep("hired", mother_edu$caretaker_hired[r]),
+          rep("child_in_school", mother_edu$caretaker_child_in_school[r]),
+          rep("other_child", mother_edu$caretaker_other_child[r]),
+          rep("not_worked_since_birth", mother_edu$caretaker_not_worked_since_birth[r]),
+          rep("other", mother_edu$caretaker_other[r]),
+          rep("missing", mother_edu$caretaker_missing[r])
+        )
+      )
+
+  mother_edu_tb <- bind_rows(mother_edu_tb, edu)
+  rm(level,
+     edu)
+}
+rm(r)
+mother_edu_tb <- mother_edu_tb[-c(1),]
+
+mother_edu_tb <-
+  mother_edu_tb %>%
+  mutate(
+    background = factor(background,
+                        levels = c('No_education',
+                                   'Primary',
+                                   'Middle',
+                                   'Secondary+')
+                        ),
+    child_caretaker = factor(child_caretaker,
+                             levels = c('respondent',
+                                        'partner',
+                                        'other_relative',
+                                        'neighbor',
+                                        'hired',
+                                        'child_in_school',
+                                        'other_child',
+                                        'not_worked_since_birth',
+                                        'other',
+                                        'missing')
+                             )
+    )
+
+mother_edu_tb %>%
+  ggplot(mapping=aes(x=child_caretaker, fill=child_caretaker)) +
+  geom_bar() +
+  theme_minimal() +
+  labs(x='',
+       y='number of employed',
+       caption = 'Respondent is currently employed but has not worked since last birth.') +
+  theme(axis.text.x = element_text(angle=15), legend.position='none') +
+  scale_x_discrete(
+    labels = 
+      c("respondent" = "respondent", 
+        "partner" = "partner",
+        "other_relative" = "relative",
+        "neighbor" = "neighbor",
+        "hired" = "hired",
+        "child_in_school" = "schooling",
+        "other_child" = "siblings",
+        "not_worked_since_birth" = "not worked since birth",
+        "other" = "other",
+        "missing" = "missing")
+  ) +
+  facet_wrap(vars(background),
+             dir = "v",
+             scales = "free",
+             labeller = labeller(background = 
+                                   c("No_education" = "No education",
+                                     "Primary" = "Primary",
+                                     "Middle" = "Middle",
+                                     "Secondary+" = "Secondary+")
+                                 )
+  )
+
+rm(mother_edu_tb)
+```
+
+## Work status
+
+```{r workstatus, echo=FALSE, message=FALSE, fig.cap="Work status"}
+work_status <-
+  ghana %>%
+  filter(character=="Work_status") %>%
+  mutate(
+    no_child_under_six = round(no_child_under_six/100 * number_of_employed_women, 0),
+    one_more_child_under_six = round(one_more_child_under_six/100 * number_of_employed_women, 0)
+  )
+
+work_status_tb<-
+  tibble(
+    background =
+      c(""),
+    child_under_six = 
+      c("")
+  )
+
+for (r in 1:nrow(work_status)){
+  status <- work_status$background[r]
+  work <-
+    tibble(
+      background = 
+        c(
+          rep(status, work_status$number_of_employed_women[r])
+        ),
+      child_under_six = 
+        c(
+          rep("No_child_under_six", work_status$no_child_under_six[r]),
+          rep("One_more_child_under_six", work_status$one_more_child_under_six[r])
+        )
+      )
+
+  work_status_tb <- bind_rows(work_status_tb, work)
+  rm(status,
+     work)
+}
+rm(r)
+work_status_tb <- work_status_tb[-c(1),]
+
+work_status_tb <-
+  work_status_tb %>%
+  mutate(
+    background = factor(background,
+                        levels = c('For_family_member',
+                                   'For_someone_else',
+                                   'Self-employed')
+                        )
+    )
+
+work_status_tb %>%
+  ggplot(mapping=aes(x=background, fill=child_under_six)) +
+  geom_bar(position='dodge') +
+  theme_minimal() +
+  labs(x='Work status', y='number of employed', fill='Child under six') +
+  scale_x_discrete(labels = c("For_family_member" = "For family member",
+                              "For_someone_else" = "For someone else")) + 
+  scale_fill_discrete(labels = c("No child under six", 
+                                 "One or more child under six"))
+
+rm(work_status_tb)
+```
+
+Figure \@ref(fig:workstatus) shows that
+
+```{r workstatuschildcare, echo=FALSE, fig.cap="Distribution of child's caretaker by work status"}
+work_status <-
+  work_status %>%
+  mutate(
+    caretaker_respondent = round(caretaker_respondent/100 * one_more_child_under_six, 0),
+    caretaker_partner = round(caretaker_partner/100 * one_more_child_under_six, 0),
+    caretaker_other_relative = round(caretaker_other_relative/100 * one_more_child_under_six, 0),
+    caretaker_neighbor = round(caretaker_neighbor/100 * one_more_child_under_six, 0),
+    caretaker_hired = round(caretaker_hired/100 * one_more_child_under_six, 0),
+    caretaker_child_in_school = round(caretaker_child_in_school/100 * one_more_child_under_six, 0),
+    caretaker_other_female_child = round(caretaker_other_female_child/100 * one_more_child_under_six, 0),
+    caretaker_other_male_child = round(caretaker_other_male_child/100 * one_more_child_under_six, 0),
+    caretaker_not_worked_since_birth = round(caretaker_not_worked_since_birth/100 * one_more_child_under_six, 0),
+    caretaker_other = round(caretaker_other/100 * one_more_child_under_six, 0),
+    caretaker_missing = round(caretaker_missing/100 * one_more_child_under_six, 0)
+    ) %>%
+  mutate(
+    caretaker_other_female_child = caretaker_other_female_child + caretaker_other_male_child
+  ) %>%
+  select(-caretaker_other_male_child) %>%
+  rename(caretaker_other_child = caretaker_other_female_child)
+
+work_status_tb<-
+  tibble(
+    background =
+      c(""),
+    child_caretaker = 
+      c("")
+  )
+
+work_status[1, 13] <- 0
+work_status[2, 13] <- 0
+work_status[3, 13] <- work_status[3, 13] + 1
+
+for (r in 1:nrow(work_status)){
+  status <- work_status$background[r]
+  work <-
+    tibble(
+      background = 
+        c(
+          rep(status, work_status$one_more_child_under_six[r])
+        ),
+      child_caretaker = 
+        c(
+          rep("respondent", work_status$caretaker_respondent[r]),
+          rep("partner", work_status$caretaker_partner[r]),
+          rep("other_relative", work_status$caretaker_other_relative[r]),
+          rep("neighbor", work_status$caretaker_neighbor[r]),
+          rep("hired", work_status$caretaker_hired[r]),
+          rep("child_in_school", work_status$caretaker_child_in_school[r]),
+          rep("other_child", work_status$caretaker_other_child[r]),
+          rep("not_worked_since_birth", work_status$caretaker_not_worked_since_birth[r]),
+          rep("other", work_status$caretaker_other[r]),
+          rep("missing", work_status$caretaker_missing[r])
+        )
+      )
+
+  work_status_tb <- bind_rows(work_status_tb, work)
+  rm(status,
+     work)
+}
+rm(r)
+work_status_tb <- work_status_tb[-c(1),]
+
+work_status_tb <-
+  work_status_tb %>%
+  mutate(
+    background = factor(background,
+                        levels = c('For_family_member',
+                                   'For_someone_else',
+                                   'Self-employed')
+                        ),
+    child_caretaker = factor(child_caretaker,
+                             levels = c('respondent',
+                                        'partner',
+                                        'other_relative',
+                                        'neighbor',
+                                        'hired',
+                                        'child_in_school',
+                                        'other_child',
+                                        'not_worked_since_birth',
+                                        'other',
+                                        'missing')
+                             )
+    )
+
+work_status_tb %>%
+  ggplot(mapping=aes(x=child_caretaker, fill=child_caretaker)) +
+  geom_bar() +
+  theme_minimal() +
+  labs(x='',
+       caption = 'Respondent is currently employed but has not worked since last birth.') +
+  theme(axis.text.x = element_text(angle=15), legend.position='none') +
+  scale_x_discrete(
+    labels = 
+      c("respondent" = "respondent", 
+        "partner" = "partner",
+        "other_relative" = "relative",
+        "neighbor" = "neighbor",
+        "hired" = "hired",
+        "child_in_school" = "schooling",
+        "other_child" = "siblings",
+        "not_worked_since_birth" = "not worked since birth",
+        "other" = "other",
+        "missing" = "missing")
+  ) +
+  facet_wrap(vars(background),
+             dir = "v",
+             scales = "free",
+             labeller = labeller(background = c("For_family_member" = "For family member",
+                                                "For_someone_else" = "For someone else",
+                                                "Self-employed" = "Self-employed")
+                                 )
+  )
+
+rm(work_status_tb)
+```
+
+## Occupation
+
+```{r occupation, echo=FALSE, message=FALSE, fig.cap="Occupation"}
+occupation <-
+  ghana %>%
+  filter(character=="Occupation") %>%
+  mutate(
+    no_child_under_six = round(no_child_under_six/100 * number_of_employed_women, 0),
+    one_more_child_under_six = round(one_more_child_under_six/100 * number_of_employed_women, 0)
+  )
+
+occupation_tb<-
+  tibble(
+    background =
+      c(""),
+    child_under_six = 
+      c("")
+  )
+
+for (r in 1:nrow(occupation)){
+  type <- occupation$background[r]
+  occup <-
+    tibble(
+      background = 
+        c(
+          rep(type, occupation$number_of_employed_women[r])
+        ),
+      child_under_six = 
+        c(
+          rep("No_child_under_six", occupation$no_child_under_six[r]),
+          rep("One_more_child_under_six", occupation$one_more_child_under_six[r])
+        )
+      )
+
+  occupation_tb <- bind_rows(occupation_tb, occup)
+  rm(type,
+     occup)
+}
+rm(r)
+occupation_tb <- occupation_tb[-c(1),]
+
+occupation_tb <-
+  occupation_tb %>%
+  mutate(
+    background = factor(background,
+                        levels = c('Agricultural',
+                                   'Nonagricultural')
+                        )
+    )
+
+occupation_tb %>%
+  ggplot(mapping=aes(x=background, fill=child_under_six)) +
+  geom_bar(position='dodge') +
+  theme_minimal() +
+  labs(x='work status', y='number of employed', fill='Child under six') +
+  scale_fill_discrete(labels = c("No child under six", 
+                                 "One or more child under six"))
+
+rm(occupation_tb)
+```
+
+Figure \@ref(fig:occupation) shows that
+
+```{r occupationchildcare, echo=FALSE, fig.cap="Distribution of child's caretaker by work status"}
+occupation <-
+  occupation %>%
+  mutate(
+    caretaker_respondent = round(caretaker_respondent/100 * one_more_child_under_six, 0),
+    caretaker_partner = round(caretaker_partner/100 * one_more_child_under_six, 0),
+    caretaker_other_relative = round(caretaker_other_relative/100 * one_more_child_under_six, 0),
+    caretaker_neighbor = round(caretaker_neighbor/100 * one_more_child_under_six, 0),
+    caretaker_hired = round(caretaker_hired/100 * one_more_child_under_six, 0),
+    caretaker_child_in_school = round(caretaker_child_in_school/100 * one_more_child_under_six, 0),
+    caretaker_other_female_child = round(caretaker_other_female_child/100 * one_more_child_under_six, 0),
+    caretaker_other_male_child = round(caretaker_other_male_child/100 * one_more_child_under_six, 0),
+    caretaker_not_worked_since_birth = round(caretaker_not_worked_since_birth/100 * one_more_child_under_six, 0),
+    caretaker_other = round(caretaker_other/100 * one_more_child_under_six, 0),
+    caretaker_missing = round(caretaker_missing/100 * one_more_child_under_six, 0)
+    ) %>%
+  mutate(
+    caretaker_other_female_child = caretaker_other_female_child + caretaker_other_male_child
+  ) %>%
+  select(-caretaker_other_male_child) %>%
+  rename(caretaker_other_child = caretaker_other_female_child)
+
+occupation_tb<-
+  tibble(
+    background =
+      c(""),
+    child_caretaker = 
+      c("")
+  )
+
+occupation[2, 13] <- occupation[2, 13] + 1
+
+for (r in 1:nrow(occupation)){
+  type <- occupation$background[r]
+  occup <-
+    tibble(
+      background = 
+        c(
+          rep(type, occupation$one_more_child_under_six[r])
+        ),
+      child_caretaker = 
+        c(
+          rep("respondent", occupation$caretaker_respondent[r]),
+          rep("partner", occupation$caretaker_partner[r]),
+          rep("other_relative", occupation$caretaker_other_relative[r]),
+          rep("neighbor", occupation$caretaker_neighbor[r]),
+          rep("hired", occupation$caretaker_hired[r]),
+          rep("child_in_school", occupation$caretaker_child_in_school[r]),
+          rep("other_child", occupation$caretaker_other_child[r]),
+          rep("not_worked_since_birth", occupation$caretaker_not_worked_since_birth[r]),
+          rep("other", occupation$caretaker_other[r]),
+          rep("missing", occupation$caretaker_missing[r])
+        )
+      )
+
+  occupation_tb <- bind_rows(occupation_tb, occup)
+  rm(type,
+     occup)
+}
+rm(r)
+occupation_tb <- occupation_tb[-c(1),]
+
+occupation_tb <-
+  occupation_tb %>%
+  mutate(
+    background = factor(background,
+                        levels = c('Agricultural',
+                                   'Nonagricultural')
+                        ),
+    child_caretaker = factor(child_caretaker,
+                             levels = c('respondent',
+                                        'partner',
+                                        'other_relative',
+                                        'neighbor',
+                                        'hired',
+                                        'child_in_school',
+                                        'other_child',
+                                        'not_worked_since_birth',
+                                        'other',
+                                        'missing')
+                             )
+    )
+
+occupation_tb %>%
+  ggplot(mapping=aes(x=child_caretaker, fill=child_caretaker)) +
+  geom_bar() +
+  theme_minimal() +
+  labs(x='',
+       caption = 'Respondent is currently employed but has not worked since last birth.') +
+  theme(axis.text.x = element_text(angle=15), legend.position='none') + 
+  scale_x_discrete(
+    labels = 
+      c("respondent" = "respondent", 
+        "partner" = "partner",
+        "other_relative" = "relative",
+        "neighbor" = "neighbor",
+        "hired" = "hired",
+        "child_in_school" = "schooling",
+        "other_child" = "siblings",
+        "not_worked_since_birth" = "not worked since birth",
+        "other" = "other",
+        "missing" = "missing")
+  ) +
+  facet_wrap(vars(background),
+             dir = "v",
+             scales = "free")
+
+rm(occupation_tb)
+```
+
+## Employment status
+
+```{r employmentstatus, echo=FALSE, message=FALSE, fig.cap="Employment status"}
+employment_status <-
+  ghana %>%
+  filter(character=="Employment_status") %>%
+  mutate(
+    no_child_under_six = round(no_child_under_six/100 * number_of_employed_women, 0),
+    one_more_child_under_six = round(one_more_child_under_six/100 * number_of_employed_women, 0)
+  )
+
+employment_status_tb<-
+  tibble(
+    background =
+      c(""),
+    child_under_six = 
+      c("")
+  )
+
+for (r in 1:nrow(employment_status)){
+  status <- employment_status$background[r]
+  employment <-
+    tibble(
+      background = 
+        c(
+          rep(status, employment_status$number_of_employed_women[r])
+        ),
+      child_under_six = 
+        c(
+          rep("No_child_under_six", employment_status$no_child_under_six[r]),
+          rep("One_more_child_under_six", employment_status$one_more_child_under_six[r])
+        )
+      )
+
+  employment_status_tb <- bind_rows(employment_status_tb, employment)
+  rm(status,
+     employment)
+}
+rm(r)
+employment_status_tb <- employment_status_tb[-c(1),]
+
+employment_status_tb <-
+  employment_status_tb %>%
+  mutate(
+    background = factor(background,
+                        levels = c('All_year_full_week',
+                                   'All_year_part_week',
+                                   'Seasonal',
+                                   'Occasional')
+                        )
+    )
+
+employment_status_tb %>%
+  ggplot(mapping=aes(x=background, fill=child_under_six)) +
+  geom_bar(position='dodge') +
+  theme_minimal() +
+  labs(x='Work status', y='number of employed', fill='Child under six') +
+  scale_x_discrete(labels = c("All_year_full_week" = "All year, full week",
+                              "All_year_part_week" = "All year, part week")) +
+  theme(axis.text.x = element_text(angle=15)) +
+  scale_fill_discrete(labels = c("No child under six", 
+                                 "One or more child under six"))
+
+rm(employment_status_tb)
+```
+
+Figure \@ref(fig:employmentstatus) shows that
+
+```{r employment_statuschildcare, echo=FALSE, fig.cap="Distribution of child's caretaker by work status"}
+employment_status <-
+  employment_status %>%
+  mutate(
+    caretaker_respondent = round(caretaker_respondent/100 * one_more_child_under_six, 0),
+    caretaker_partner = round(caretaker_partner/100 * one_more_child_under_six, 0),
+    caretaker_other_relative = round(caretaker_other_relative/100 * one_more_child_under_six, 0),
+    caretaker_neighbor = round(caretaker_neighbor/100 * one_more_child_under_six, 0),
+    caretaker_hired = round(caretaker_hired/100 * one_more_child_under_six, 0),
+    caretaker_child_in_school = round(caretaker_child_in_school/100 * one_more_child_under_six, 0),
+    caretaker_other_female_child = round(caretaker_other_female_child/100 * one_more_child_under_six, 0),
+    caretaker_other_male_child = round(caretaker_other_male_child/100 * one_more_child_under_six, 0),
+    caretaker_not_worked_since_birth = round(caretaker_not_worked_since_birth/100 * one_more_child_under_six, 0),
+    caretaker_other = round(caretaker_other/100 * one_more_child_under_six, 0),
+    caretaker_missing = round(caretaker_missing/100 * one_more_child_under_six, 0)
+    ) %>%
+  mutate(
+    caretaker_other_female_child = caretaker_other_female_child + caretaker_other_male_child
+  ) %>%
+  select(-caretaker_other_male_child) %>%
+  rename(caretaker_other_child = caretaker_other_female_child)
+
+employment_status_tb<-
+  tibble(
+    background =
+      c(""),
+    child_caretaker = 
+      c("")
+  )
+
+employment_status[3,13] <- employment_status[3,13] - 1
+
+for (r in 1:nrow(employment_status)){
+  status <- employment_status$background[r]
+  employment <-
+    tibble(
+      background = 
+        c(
+          rep(status, employment_status$one_more_child_under_six[r])
+        ),
+      child_caretaker = 
+        c(
+          rep("respondent", employment_status$caretaker_respondent[r]),
+          rep("partner", employment_status$caretaker_partner[r]),
+          rep("other_relative", employment_status$caretaker_other_relative[r]),
+          rep("neighbor", employment_status$caretaker_neighbor[r]),
+          rep("hired", employment_status$caretaker_hired[r]),
+          rep("child_in_school", employment_status$caretaker_child_in_school[r]),
+          rep("other_child", employment_status$caretaker_other_child[r]),
+          rep("not_worked_since_birth", employment_status$caretaker_not_worked_since_birth[r]),
+          rep("other", employment_status$caretaker_other[r]),
+          rep("missing", employment_status$caretaker_missing[r])
+        )
+      )
+
+  employment_status_tb <- bind_rows(employment_status_tb, employment)
+  rm(status,
+     employment)
+}
+rm(r)
+employment_status_tb <- employment_status_tb[-c(1),]
+
+employment_status_tb <-
+  employment_status_tb %>%
+  mutate(
+    background = factor(background,
+                        levels = c('All_year_full_week',
+                                   'All_year_part_week',
+                                   'Seasonal',
+                                   'Occasional')
+                        ),
+    child_caretaker = factor(child_caretaker,
+                             levels = c('respondent',
+                                        'partner',
+                                        'other_relative',
+                                        'neighbor',
+                                        'hired',
+                                        'child_in_school',
+                                        'other_child',
+                                        'not_worked_since_birth',
+                                        'other',
+                                        'missing')
+                             )
+    )
+
+employment_status_tb %>%
+  ggplot(mapping=aes(x=child_caretaker, fill=child_caretaker)) +
+  geom_bar() +
+  theme_minimal() +
+  labs(x='',
+       caption = 'Respondent is currently employed but has not worked since last birth.') +
+  theme(axis.text.x = element_text(angle=15), legend.position='none') +
+  scale_x_discrete(
+    labels = 
+      c("respondent" = "respondent",
+        "partner" = "partner",
+        "other_relative" = "relative",
+        "neighbor" = "neighbor",
+        "hired" = "hired",
+        "child_in_school" = "schooling",
+        "other_child" = "siblings",
+        "not_worked_since_birth" = "not worked since birth",
+        "other" = "other",
+        "missing" = "missing")
+  ) +
+  facet_wrap(vars(background),
+             dir = "v",
+             scales = "free",
+             labeller = labeller(background = c("All_year_full_week" = "All year, full week",
+                                                "All_year_part_week" = "All year, part week",
+                                                "Seasonal" = "Seasonal",
+                                                "Occasional" = "Occasional")
+                                 )
+  )
+
+rm(employment_status_tb)
+```
+
+# Discussions
+
+## Limitation and weaknesses
+
+The number does not add up to 100. (truncation error)
 

### 2022-03-29 scripts/01-gather_data.R

@@ -44,10 +44,12 @@ data <-
   mutate(all = str_replace(all, "([:alpha:]|_) ([:alpha:])", "\\1_\\2")) %>%
   separate(col = all,
            into = c("background", "no_child_under_six", "one_more_child_under_six", 
-                    "respondent", "partner", "other_relative", "neighbor", 
-                    "hired", "child_in_school", "other_female_child", 
-                    "other_male_child", "not_worked_since_birth", "other", 
-                    "missing", "total", "number_of_employed_women"),
+                    "caretaker_respondent", "caretaker_partner", 
+                    "caretaker_other_relative", "caretaker_neighbor", 
+                    "caretaker_hired", "caretaker_child_in_school", 
+                    "caretaker_other_female_child", "caretaker_other_male_child", 
+                    "caretaker_not_worked_since_birth", "caretaker_other", 
+                    "caretaker_missing", "total", "number_of_employed_women"),
            sep = " ", # Works fine because the tables are nicely laid out
            remove = TRUE,
            fill = "right",

### 2022-03-29 scripts/02-clean_and_prepare_data.R

@@ -1,11 +1,11 @@
 #### Preamble ####
-# Purpose: Clean and prepare the 1988 Ghana census data downloaded from the DHS Program
+# Purpose: Clean and prepare the 1988 clean census data downloaded from the DHS Program
 # Author: Pascal Lee Slew, Yunkyung Park
 # Data: 3 April 2022
 # Contact: pascal.leeslew@mail.utoronto.ca, clara.park@mail.utoronto.ca
 # License: MIT
 # Pre-requisites: 
-# - Need to have downloaded the 1988 Ghana census data by following the process 
+# - Need to have downloaded the 1988 clean census data by following the process 
 # in 01-gather_data.R and saved it to outputs/data
 # - Don't forget to gitignore it!
 
@@ -40,5 +40,45 @@ rm(col_len,
    index,
    i,
    j)
+
+# check the numbers add up to a hundred
+clean$sum_child <- (clean$no_child_under_six + clean$one_more_child_under_six) == 100
+clean_caretaker <- 
+  clean %>%
+  select(starts_with("caretaker_")) %>%
+  mutate(sum_caretaker = rowSums(.))
+
+clean_caretaker <-
+  bind_cols(clean$background, clean_caretaker, clean$character)
+
+clean<-
+  clean %>%
+  select(-sum_child)
+
+clean2<-
+  clean %>%
+  mutate(
+    no_child_under_six = round(no_child_under_six/100 * number_of_employed_women, 0),
+    one_more_child_under_six = round(one_more_child_under_six/100 * number_of_employed_women, 0)
+  ) %>%
+  mutate(
+    caretaker_respondent = round(caretaker_respondent/100 * one_more_child_under_six, 0),
+    caretaker_partner = round(caretaker_partner/100 * one_more_child_under_six, 0),
+    caretaker_other_relative = round(caretaker_other_relative/100 * one_more_child_under_six, 0),
+    caretaker_neighbor = round(caretaker_neighbor/100 * one_more_child_under_six, 0),
+    caretaker_hired = round(caretaker_hired/100 * one_more_child_under_six, 0),
+    caretaker_child_in_school = round(caretaker_child_in_school/100 * one_more_child_under_six, 0),
+    caretaker_other_female_child = round(caretaker_other_female_child/100 * one_more_child_under_six, 0),
+    caretaker_other_male_child = round(caretaker_other_male_child/100 * one_more_child_under_six, 0),
[…]

### 2022-03-30 outputs/paper.Rmd
Map of Ghana Distribution of the number of women employed in different regions

@@
 ```{r readdata, echo=FALSE}
-ghana<-read_csv('data/cleaned_data.csv', show_col_types = FALSE)
+ghana <- read_csv('data/cleaned_data.csv', show_col_types = FALSE)
 ```
@@
     character = factor(character,
-                       levels=c("Residence",
+                       levels = c("Residence",
                                 "Region",
@@
 
+```{r map, warning = FALSE, echo = FALSE}
+library(rnaturalearth)
+library(sf)
+#devtools::install_github("ropensci/rnaturalearthhires")
+# The st_centroid function takes the sf object and returns the center of 
+# the polygon, again as a sf object.
+map_ghana <- ne_states(country = 'Ghana', 
+                       returnclass = 'sf')  # grab provinces within Ghana
+
+map_ghana %>% 
+  ggplot() +
+  geom_sf( ) + 
+  geom_text(data = st_centroid(map_ghana), 
+            size = 3,
+             aes(x = longitude, 
+                 y = latitude,
+                 label= woe_name)) +
+  labs(title='Ghana Administrative Regions') +
+  theme_minimal()
+```
+
+```{r, echo=FALSE}
+# Urban vs Rural
+
+# Obtain subset of dataset for residence area
+residence <- ghana %>% 
+  filter(character == 'Residence')
+
+# look at survey respondents distribution in urban and rural areas
+residence %>% 
+  ggplot(aes(x = background, y = number_of_employed_women)) +
+  geom_bar(stat = 'identity', fill = "burlywood") +
+  labs(x = "Area",
+       y = "Number of employed women") +
+  theme_minimal()
+```
+
+```{r, echo=FALSE}
+# region subdataset
+region <- ghana %>% 
+  filter(character == "Region") %>% 
+  mutate(background = recode(background,
+                             'Western' = 'Western',
+                             'Central' = 'Central',
+                             'Greater_Accra' = 'Greater Accra',
+                             'Volta' = 'Volta',
+                             'Eastern' = 'Eastern',
+                             'Ashanti' = 'Ashanti',
+                             'Brong_Ahafo' = 'Brong Ahafo',
+                             'Northen' = 'Northern',
+                             'Upper_West' = 'Upper West',
+                             'Upper_East' = 'Upper East'))
+
+# number of survey respondents in the different administrative regions
+region %>% 
+  ggplot(aes(x = background,
+             y = number_of_employed_women)) +
+  geom_bar(stat = 'identity',
+           fill = 'burlywood') +
+  labs(x = "Administrative regions",
+       y = "Number of employed women") +
+  theme_minimal()
+```
+
+```{r}
+
+```
+
 # Discussions

### 2022-03-30 outputs/paper.Rmd
bar graph for the comparison of the no child under six and one or more child under six in urban vs rural areas

@@
 
+```{r, echo = FALSE}
+# make dataset in long format
+resid_long <- residence %>% 
+  select(-c(character)) %>% 
+  pivot_longer(!background, names_to = "variables", values_to = "percentage")
+
+# create label names list
+label_list <- list('no_child_under_six' = "No child under six", 
+                   'one_more_child_under_six' = "One or more child under six")
+
+labellers <- function(variable, value) {
+  return(label_list[value])
+}
+
+# plot bar graph
+resid_long %>% 
+  filter(variables == 'no_child_under_six' | variables == 'one_more_child_under_six') %>% 
+  ggplot(aes(x = background, 
+             y = percentage,
+             fill = background)) +
+  geom_bar(stat = 'identity',
+           fill = "lightblue") +
+  labs(x = "Area",
+       y = "Percentage of women") +
+  theme_minimal() +
+  facet_wrap(~variables, labeller = labellers) +
+  theme(strip.text = element_text(face = "bold", size = rel(1)),
+    strip.background = element_rect(fill = "lightblue", colour = "black", size = 0.5))
+```
+
 ```{r}
+# caretaker aspect
 

### 2022-03-30 outputs/paper.Rmd
Caretaker aspect comparison for urban versus rural areas

--- 2022-03-30 outputs/paper.Rmd
@@
 
+```{r, echo = FALSE}
+# make dataset in long format
+resid_long <- residence %>% 
+  select(-c(character)) %>% 
+  pivot_longer(!background, names_to = "variables", values_to = "percentage")
+
+# create label names list
+label_list <- list('no_child_under_six' = "No child under six", 
+                   'one_more_child_under_six' = "One or more child under six")
+
+labellers <- function(variable, value) {
+  return(label_list[value])
+}
+
+# plot bar graph
+resid_long %>% 
+  filter(variables == 'no_child_under_six' | variables == 'one_more_child_under_six') %>% 
+  ggplot(aes(x = background, 
+             y = percentage,
+             fill = variables)) +
+  geom_bar(stat = 'identity',
+           position = 'dodge') +
+  labs(x = "Area",
+       y = "Percentage of women",
+       fill = "Children under six") +
+  theme_minimal() +
+  scale_fill_brewer() +
+  theme(legend.position = "bottom")
+
+# need to recode names
+# change legends name
+```
+
 ```{r}
+# caretaker aspect
+
+# make dataset into long format
+# rename 
+caretaker <- residence %>% 
+  select(-c(character, no_child_under_six, one_more_child_under_six, total, number_of_employed_women)) %>% 
+  pivot_longer(!background, names_to = "caretakers", values_to = "percentage") %>% 
+  mutate(caretakers = recode(caretakers,
+                             'caretaker_respondent' = 'respondent',
+                             'caretaker_partner' = 'partner',
+                             'caretaker_other_relative' = 'other relative',
+                             'caretaker_other_male_child' = 'other male child',
+                             'caretaker_other_female_child' = 'other female child',
+                             'caretaker_other' = 'other',
+                             'caretaker_not_worked since_birth' = 'not worked since birth',
+                             'caretaker_neighbor' = 'neighbour',
+                             'caretaker_missing' = 'missing',
+                             'caretaker_hired' = 'hired',
+                             'caretaker_child_in_school' = 'child in school'))
+
+# plot bar graph
+caretaker %>% 
+  ggplot(aes(x = caretakers, 
+             y = percentage,
+             fill = background)) +
+  geom_bar(stat = 'identity',
+           position = "dodge") +
+  labs(x = "Caretaker",
+       y = "Percentage of women",
+       fill = "Area") +
+  theme_minimal() +
+  coord_flip() +
+  scale_fill_brewer(palette = "Set1") +
+  theme(legend.position = "bottom")
 
 ```
+
+## Also comparison among the different administrative regions
 

### 2022-03-30 scripts/00-simulation.R
rework simulation of data

@@ -15,53 +15,20 @@ library(tidyverse)
 #### Simulate data ####
 set.seed(304)
 
-items<-c("no_child_under_six", "one_more_child_under_six", 
-         "respondent", "partner", "other_relative", "neighbor", 
-         "hired", "child_in_school", "other_female_child", 
-         "other_male_child", "not_worked_since_birth", "other", 
-         "missing")
-
-num_of_items <- length(items)
-
-simulated_dhs <-
+simulated_data <-
   tibble(
-    background = 
-      c(
-        rep("Urban", num_of_items),
-        rep("Rural", num_of_items),
-        rep("Western", num_of_items),
-        rep("Central", num_of_items),
-        rep("Greater_Accra", num_of_items),
-        rep("Volta", num_of_items),
-        rep("Eastern", num_of_items),
-        rep("Ashanti", num_of_items),
-        rep("Brong_Ahafo", num_of_items),
-        rep("Northern", num_of_items),
-        rep("Upper_West", num_of_items),
-        rep("Upper_East", num_of_items),
-        rep("No_education", num_of_items),
-        rep("Primary", num_of_items),
-        rep("Middle", num_of_items),
-        rep("Secondary+", num_of_items),
-        rep("For_family_member", num_of_items),
-        rep("For_someone_else", num_of_items),
-        rep("Self-employed", num_of_items),
-        rep("Agricultural", num_of_items),
-        rep("Nonagricultural", num_of_items),
-        rep("All_year_full_week", num_of_items),
-        rep("All_year_part_week", num_of_items),
-        rep("Seasonal", num_of_items),
-        rep("Occasional", num_of_items),
-        rep("Total", num_of_items)
+    # Use 1 through to 3565 to represent each region
+    'Index' = 1:3565,
+    # Randomly choose one of the two options, with replacement, 3565 times
+    'Region' = sample(
+      x = c(
+        'Urban',
+        'Rural'
       ),
-    item =
-      c(
-        rep(item, 26)
-      ),
-    proportion = 
-      runif(n = num_of_items * 26,
-            min = 0, 
-            max = 100)
-  )
+      size = 3565,
+      replace = TRUE
+    ))
 
-head(simulated_dhs)
+
+
+

### 2022-03-31 scripts/00-simulation.R
Update scripts/00-simulation.R

@@ -9,59 +9,108 @@
 
 #### Workspace set-up ####
 library(janitor)
-library(lubridate)
 library(tidyverse)
 
 #### Simulate data ####
 set.seed(304)
 
-items<-c("no_child_under_six", "one_more_child_under_six", 
-         "respondent", "partner", "other_relative", "neighbor", 
-         "hired", "child_in_school", "other_female_child", 
-         "other_male_child", "not_worked_since_birth", "other", 
-         "missing")
-
-num_of_items <- length(items)
-
 simulated_dhs <-
   tibble(
-    background = 
-      c(
-        rep("Urban", num_of_items),
-        rep("Rural", num_of_items),
-        rep("Western", num_of_items),
-        rep("Central", num_of_items),
-        rep("Greater_Accra", num_of_items),
-        rep("Volta", num_of_items),
-        rep("Eastern", num_of_items),
-        rep("Ashanti", num_of_items),
-        rep("Brong_Ahafo", num_of_items),
-        rep("Northern", num_of_items),
-        rep("Upper_West", num_of_items),
-        rep("Upper_East", num_of_items),
-        rep("No_education", num_of_items),
-        rep("Primary", num_of_items),
-        rep("Middle", num_of_items),
-        rep("Secondary+", num_of_items),
-        rep("For_family_member", num_of_items),
-        rep("For_someone_else", num_of_items),
-        rep("Self-employed", num_of_items),
-        rep("Agricultural", num_of_items),
-        rep("Nonagricultural", num_of_items),
-        rep("All_year_full_week", num_of_items),
-        rep("All_year_part_week", num_of_items),
-        rep("Seasonal", num_of_items),
-        rep("Occasional", num_of_items),
-        rep("Total", num_of_items)
+    # Unique identifier
+    'caseID' = 1:3565,
+    # Randomly choose one of the two options, with replacement, 3565 times
+    'Residence' = sample(
+      x = c(
+        'Urban',
+        'Rural'
       ),
-    item =
-      c(
-        rep(item, 26)
+      size = 3565,
+      replace = TRUE
+    ),
+    'Region' = sample(
+      x = c(
+        'Western',
+        'Central',
+        'Greater_Accra',
+        'Volta',
+        'Eastern',
+        'Ashanti',
+        'Brong_Ahafo',
+        'Northern',
+        'Upper_West',
+        'Upper_East'
       ),
-    proportion = 
[…]

### 2022-03-31 outputs/paper.Rmd
Update paper.Rmd

@@
 # install.packages("stringr")
+# install.packages("ggforce")
 library(stringr) 
@@
 library(bookdown)
+library(ggforce)
 ```
@@
 
-```{r motheredu, echo=FALSE, message=FALSE, fig.cap="Mother's Education level"}
+```{r motheredu, echo=FALSE, fig.cap="Mother's Education level"}
+# select mother edu
 mother_edu <-
@@
 
-mother_edu_tb<-
-  tibble(
-    background =
-      c(""),
-    child_under_six = 
-      c("")
-  )
-
-for (r in 1:nrow(mother_edu)){
-  level <- mother_edu$background[r]
-  edu <-
-    tibble(
-      background = 
-        c(
-          rep(level, mother_edu$number_of_employed_women[r])
-        ),
-      child_under_six = 
-        c(
-          rep("No_child_under_six", mother_edu$no_child_under_six[r]),
-          rep("One_more_child_under_six", mother_edu$one_more_child_under_six[r])
-        )
-      )
-
-  mother_edu_tb <- bind_rows(mother_edu_tb, edu)
-  rm(level,
-     edu)
-}
-rm(r)
-mother_edu_tb <- mother_edu_tb[-c(1),]
-
-mother_edu_tb <-
-  mother_edu_tb %>%
+# make dataset in long format
+edu_long <-
+  mother_edu %>%
+  select(-c(character, total)) %>%
+  pivot_longer(!background, names_to = "variable", values_to = "count") %>%
   mutate(
@@
 
-mother_edu_tb %>%
-  ggplot(mapping=aes(x=background, fill=child_under_six)) +
-  geom_bar(position='dodge') +
+edu_long %>%
+  filter(variable == 'no_child_under_six' | variable == 'one_more_child_under_six') %>%
+  ggplot(aes(x = background, y = count, fill = variable)) +
+  geom_bar(stat = "identity", position = "dodge") +
+  labs(x = "Mother's education", y = "Number of employed women", fill = "Child under six") +
   theme_minimal() +
-  labs(x='education level', y='number of employed', fill='Child under six') +
-  scale_x_discrete(labels = c("No_education" = "No education")) +
   scale_fill_discrete(labels = c("No child under six", 
-                                 "One or more child under six"))
-
-rm(mother_edu_tb)
+                                 "One or more child under six")) +
+  scale_x_discrete(labels = c("No_education" = "No education"))
 ```
@@
 ```{r mothereduchildcare, echo=FALSE, fig.cap="Distribution of child's caretaker by mother's education level"}
-mother_edu <-
-  mother_edu %>%
+# caretaker aspect
+edu_caretaker <-
+  edu_long %>%
+  filter(str_detect(variable, "^caretaker_")) %>%
+  mutate(variable = str_replace_all(variable, "caretaker_", "")) %>%
+  rename(caretaker = variable,
+         percentage = count) %>%
   mutate(
-    caretaker_respondent = round(caretaker_respondent/100 * one_more_child_under_six, 0),
-    caretaker_partner = round(caretaker_partner/100 * one_more_child_under_six, 0),
-    caretaker_other_relative = round(caretaker_other_relative/100 * one_more_child_under_six, 0),
-    caretaker_neighbor = round(caretaker_neighbor/100 * one_more_child_under_six, 0),
-    caretaker_hired = round(caretaker_hired/100 * one_more_child_under_six, 0),
-    caretaker_child_in_school = round(caretaker_child_in_school/100 * one_more_child_under_six, 0),
-    caretaker_other_female_child = round(caretaker_other_female_child/100 * one_more_child_under_six, 0),
-    caretaker_other_male_child = round(caretaker_other_male_child/100 * one_more_child_under_six, 0),
-    caretaker_not_worked_since_birth = round(caretaker_not_worked_since_birth/100 * one_more_child_under_six, 0),
-    caretaker_other = round(caretaker_other/100 * one_more_child_under_six, 0),
-    caretaker_missing = round(caretaker_missing/100 * one_more_child_under_six, 0)
-    ) %>%
-  mutate(
-    caretaker_other_female_child = caretaker_other_female_child + caretaker_other_male_child
-  ) %>%
-  select(-caretaker_other_male_child) %>%
-  rename(caretaker_other_child = caretaker_other_female_child)
-
-mother_edu_tb<-
-  tibble(
-    background =
-      c(""),
-    child_caretaker = 
-      c("")
-  )
-
-# clean_caretaker <- 
-#   mother_edu %>%
-#   select(starts_with("caretaker_")) %>%
-#   mutate(sum_caretaker = rowSums(.))
-# clean_caretaker$num <-
-#   mother_edu$one_more_child_under_six
-
-mother_edu[3, 13] <- 0
-mother_edu[3, 11] <- mother_edu[3, 11] - 1
-
-for (r in 1:nrow(mother_edu)){
-  level <- mother_edu$background[r]
-  edu <-
-    tibble(
-      background = 
-        c(
-          rep(level, mother_edu$one_more_child_under_six[r])
-        ),
-      child_caretaker = 
-        c(
-          rep("respondent", mother_edu$caretaker_respondent[r]),
-          rep("partner", mother_edu$caretaker_partner[r]),
-          rep("other_relative", mother_edu$caretaker_other_relative[r]),
-          rep("neighbor", mother_edu$caretaker_neighbor[r]),
-          rep("hired", mother_edu$caretaker_hired[r]),
-          rep("child_in_school", mother_edu$caretaker_child_in_school[r]),
-          rep("other_child", mother_edu$caretaker_other_child[r]),
-          rep("not_worked_since_birth", mother_edu$caretaker_not_worked_since_birth[r]),
-          rep("other", mother_edu$caretaker_other[r]),
-          rep("missing", mother_edu$caretaker_missing[r])
-        )
-      )
-
-  mother_edu_tb <- bind_rows(mother_edu_tb, edu)
-  rm(level,
-     edu)
-}
-rm(r)
-mother_edu_tb <- mother_edu_tb[-c(1),]
-
-mother_edu_tb <-
-  mother_edu_tb %>%
-  mutate(
-    background = factor(background,
-                        levels = c('No_education',
-                                   'Primary',
-                                   'Middle',
-                                   'Secondary+')
-                        ),
-    child_caretaker = factor(child_caretaker,
+    caretaker = factor(caretaker, 
                        levels = c('respondent',
@@
                                   'child_in_school',
-                                        'other_child',
+                                  'other_female_child',
+                                  'other_male_child',
                                   'not_worked_since_birth',
@@
 
-mother_edu_tb %>%
-  ggplot(mapping=aes(x=child_caretaker, fill=child_caretaker)) +
-  geom_bar() +
+# plot the bar graph
+edu_caretaker %>%
+  ggplot(mapping=aes(x=caretaker, y=percentage, fill=caretaker)) +
+  geom_bar(stat = "identity", position="dodge") + 
   theme_minimal() +
   labs(x='',
-       y='number of employed',
        caption = 'Respondent is currently employed but has not worked since last birth.') +
-  theme(axis.text.x = element_text(angle=15), legend.position='none') +
+  theme(legend.position='none') +
+  coord_flip() + 
   scale_x_discrete(
@@
         "child_in_school" = "schooling",
-        "other_child" = "siblings",
+        "other_female_child" = "female child",
+        "other_male_child" = "male child",
         "not_worked_since_birth" = "not worked since birth",
@@
   )
-
-rm(mother_edu_tb)
 ```
@@
 ```{r workstatus, echo=FALSE, message=FALSE, fig.cap="Work status"}
+# select work status
 work_status <-
@@
 
-work_status_tb<-
-  tibble(
-    background =
-      c(""),
-    child_under_six = 
-      c("")
-  )
-
-for (r in 1:nrow(work_status)){
-  status <- work_status$background[r]
-  work <-
-    tibble(
-      background = 
-        c(
-          rep(status, work_status$number_of_employed_women[r])
-        ),
-      child_under_six = 
-        c(
-          rep("No_child_under_six", work_status$no_child_under_six[r]),
-          rep("One_more_child_under_six", work_status$one_more_child_under_six[r])
-        )
-      )
-
-  work_status_tb <- bind_rows(work_status_tb, work)
-  rm(status,
-     work)
-}
-rm(r)
-work_status_tb <- work_status_tb[-c(1),]
-
-work_status_tb <-
-  work_status_tb %>%
+# make dataset in long format
+work_long <-
+  work_status %>%
+  select(-c(character, total)) %>%
+  pivot_longer(!background, names_to = "variable", values_to = "count") %>%
   mutate(
@@
 
-work_status_tb %>%
-  ggplot(mapping=aes(x=background, fill=child_under_six)) +
-  geom_bar(position='dodge') +
+work_long %>%
+  filter(variable == 'no_child_under_six' | variable == 'one_more_child_under_six') %>%
+  ggplot(aes(x = background, y = count, fill = variable)) +
+  geom_bar(stat = "identity", position = "dodge") +
+  labs(x = "Work status", y = "Number of employed women", fill = "Child under six") +
   theme_minimal() +
@@
                                  "One or more child under six"))
-
-rm(work_status_tb)
 ```
@@
 ```{r workstatuschildcare, echo=FALSE, fig.cap="Distribution of child's caretaker by work status"}
-work_status <-
-  work_status %>%
+# caretaker aspect
+work_caretaker <-
+  work_long %>%
+  filter(str_detect(variable, "^caretaker_")) %>%
+  mutate(variable = str_replace_all(variable, "caretaker_", "")) %>%
+  rename(caretaker = variable,
+         percentage = count) %>%
   mutate(
-    caretaker_respondent = round(caretaker_respondent/100 * one_more_child_under_six, 0),
-    caretaker_partner = round(caretaker_partner/100 * one_more_child_under_six, 0),
-    caretaker_other_relative = round(caretaker_other_relative/100 * one_more_child_under_six, 0),
-    caretaker_neighbor = round(caretaker_neighbor/100 * one_more_child_under_six, 0),
-    caretaker_hired = round(caretaker_hired/100 * one_more_child_under_six, 0),
-    caretaker_child_in_school = round(caretaker_child_in_school/100 * one_more_child_under_six, 0),
-    caretaker_other_female_child = round(caretaker_other_female_child/100 * one_more_child_under_six, 0),
-    caretaker_other_male_child = round(caretaker_other_male_child/100 * one_more_child_under_six, 0),
-    caretaker_not_worked_since_birth = round(caretaker_not_worked_since_birth/100 * one_more_child_under_six, 0),
-    caretaker_other = round(caretaker_other/100 * one_more_child_under_six, 0),
-    caretaker_missing = round(caretaker_missing/100 * one_more_child_under_six, 0)
-    ) %>%
-  mutate(
-    caretaker_other_female_child = caretaker_other_female_child + caretaker_other_male_child
-  ) %>%
-  select(-caretaker_other_male_child) %>%
-  rename(caretaker_other_child = caretaker_other_female_child)
-
-work_status_tb<-
-  tibble(
-    background =
-      c(""),
-    child_caretaker = 
-      c("")
-  )
-
-work_status[1, 13] <- 0
-work_status[2, 13] <- 0
-work_status[3, 13] <- work_status[3, 13] + 1
-
-for (r in 1:nrow(work_status)){
-  status <- work_status$background[r]
-  work <-
-    tibble(
-      background = 
-        c(
-          rep(status, work_status$one_more_child_under_six[r])
-        ),
-      child_caretaker = 
-        c(
-          rep("respondent", work_status$caretaker_respondent[r]),
-          rep("partner", work_status$caretaker_partner[r]),
-          rep("other_relative", work_status$caretaker_other_relative[r]),
-          rep("neighbor", work_status$caretaker_neighbor[r]),
-          rep("hired", work_status$caretaker_hired[r]),
-          rep("child_in_school", work_status$caretaker_child_in_school[r]),
-          rep("other_child", work_status$caretaker_other_child[r]),
-          rep("not_worked_since_birth", work_status$caretaker_not_worked_since_birth[r]),
-          rep("other", work_status$caretaker_other[r]),
-          rep("missing", work_status$caretaker_missing[r])
-        )
-      )
-
-  work_status_tb <- bind_rows(work_status_tb, work)
-  rm(status,
-     work)
-}
-rm(r)
-work_status_tb <- work_status_tb[-c(1),]
-
-work_status_tb <-
-  work_status_tb %>%
-  mutate(
-    background = factor(background,
-                        levels = c('For_family_member',
-                                   'For_someone_else',
-                                   'Self-employed')
-                        ),
-    child_caretaker = factor(child_caretaker,
+    caretaker = factor(caretaker, 
                        levels = c('respondent',
@@
 
-work_status_tb %>%
-  ggplot(mapping=aes(x=child_caretaker, fill=child_caretaker)) +
-  geom_bar() +
+# plot the bar graph
+work_caretaker %>%
+  ggplot(mapping=aes(x=caretaker, y=percentage, fill=caretaker)) +
+  geom_bar(stat = "identity", position="dodge") + 
   theme_minimal() +
@@
        caption = 'Respondent is currently employed but has not worked since last birth.') +
-  theme(axis.text.x = element_text(angle=15), legend.position='none') +
+  theme(legend.position='none') +
+  coord_flip() + 
   scale_x_discrete(
@@
   ) +
-  facet_wrap(vars(background),
-             dir = "v",
+  facet_wrap_paginate(vars(background),
+                      ncol=2,
+                      nrow=2,
+                      dir = "h",
                       scales = "free",
@@
 
-rm(work_status_tb)
 ```
@@
 ```{r occupation, echo=FALSE, message=FALSE, fig.cap="Occupation"}
+# select occupation
 occupation <-
@@
 
-occupation_tb<-
-  tibble(
-    background =
-      c(""),
-    child_under_six = 
-      c("")
-  )
-
-for (r in 1:nrow(occupation)){
-  type <- occupation$background[r]
-  occup <-
-    tibble(
-      background = 
-        c(
-          rep(type, occupation$number_of_employed_women[r])
-        ),
-      child_under_six = 
-        c(
-          rep("No_child_under_six", occupation$no_child_under_six[r]),
-          rep("One_more_child_under_six", occupation$one_more_child_under_six[r])
-        )
-      )
-
-  occupation_tb <- bind_rows(occupation_tb, occup)
-  rm(type,
-     occup)
-}
-rm(r)
-occupation_tb <- occupation_tb[-c(1),]
-
-occupation_tb <-
-  occupation_tb %>%
+# make dataset in long format
+occup_long <-
+  occupation %>%
+  select(-c(character, total)) %>%
+  pivot_longer(!background, names_to = "variable", values_to = "count") %>%
   mutate(
@@
 
-occupation_tb %>%
-  ggplot(mapping=aes(x=background, fill=child_under_six)) +
-  geom_bar(position='dodge') +
+occup_long %>%
+  filter(variable == 'no_child_under_six' | variable == 'one_more_child_under_six') %>%
+  ggplot(aes(x = background, 
+             y = count,
+             fill = variable)) +
+  geom_bar(stat = "identity",
+           position = "dodge") +
+  labs(x = "Occupation",
+       y = "Number of employed women",
+       fill = "Child under six") +
   theme_minimal() +
-  labs(x='work status', y='number of employed', fill='Child under six') +
   scale_fill_discrete(labels = c("No child under six", 
                                  "One or more child under six"))
-
-rm(occupation_tb)
 ```
@@
 ```{r occupationchildcare, echo=FALSE, fig.cap="Distribution of child's caretaker by work status"}
-occupation <-
-  occupation %>%
+# caretaker aspect
+occup_caretaker <-
+  occup_long %>%
+  filter(str_detect(variable, "^caretaker_")) %>%
+  mutate(variable = str_replace_all(variable, "caretaker_", "")) %>%
+  rename(caretaker = variable,
+         percentage = count) %>%
   mutate(
-    caretaker_respondent = round(caretaker_respondent/100 * one_more_child_under_six, 0),
-    caretaker_partner = round(caretaker_partner/100 * one_more_child_under_six, 0),
-    caretaker_other_relative = round(caretaker_other_relative/100 * one_more_child_under_six, 0),
-    caretaker_neighbor = round(caretaker_neighbor/100 * one_more_child_under_six, 0),
-    caretaker_hired = round(caretaker_hired/100 * one_more_child_under_six, 0),
-    caretaker_child_in_school = round(caretaker_child_in_school/100 * one_more_child_under_six, 0),
-    caretaker_other_female_child = round(caretaker_other_female_child/100 * one_more_child_under_six, 0),
-    caretaker_other_male_child = round(caretaker_other_male_child/100 * one_more_child_under_six, 0),
-    caretaker_not_worked_since_birth = round(caretaker_not_worked_since_birth/100 * one_more_child_under_six, 0),
-    caretaker_other = round(caretaker_other/100 * one_more_child_under_six, 0),
-    caretaker_missing = round(caretaker_missing/100 * one_more_child_under_six, 0)
-    ) %>%
-  mutate(
-    caretaker_other_female_child = caretaker_other_female_child + caretaker_other_male_child
-  ) %>%
-  select(-caretaker_other_male_child) %>%
-  rename(caretaker_other_child = caretaker_other_female_child)
-
-occupation_tb<-
-  tibble(
-    background =
-      c(""),
-    child_caretaker = 
-      c("")
-  )
-
-occupation[2, 13] <- occupation[2, 13] + 1
-
-for (r in 1:nrow(occupation)){
-  type <- occupation$background[r]
-  occup <-
-    tibble(
-      background = 
-        c(
-          rep(type, occupation$one_more_child_under_six[r])
-        ),
-      child_caretaker = 
-        c(
-          rep("respondent", occupation$caretaker_respondent[r]),
-          rep("partner", occupation$caretaker_partner[r]),
-          rep("other_relative", occupation$caretaker_other_relative[r]),
-          rep("neighbor", occupation$caretaker_neighbor[r]),
-          rep("hired", occupation$caretaker_hired[r]),
-          rep("child_in_school", occupation$caretaker_child_in_school[r]),
-          rep("other_child", occupation$caretaker_other_child[r]),
-          rep("not_worked_since_birth", occupation$caretaker_not_worked_since_birth[r]),
-          rep("other", occupation$caretaker_other[r]),
-          rep("missing", occupation$caretaker_missing[r])
-        )
-      )
-
-  occupation_tb <- bind_rows(occupation_tb, occup)
-  rm(type,
-     occup)
-}
-rm(r)
-occupation_tb <- occupation_tb[-c(1),]
-
-occupation_tb <-
-  occupation_tb %>%
-  mutate(
-    background = factor(background,
-                        levels = c('Agricultural',
-                                   'Nonagricultural')
-                        ),
-    child_caretaker = factor(child_caretaker,
+    caretaker = factor(caretaker, 
                        levels = c('respondent',
@@
                                   'child_in_school',
-                                        'other_child',
+                                  'other_female_child',
+                                  'other_male_child',
                                   'not_worked_since_birth',
                                   'other',
-                                        'missing')
-                             )
+                                  'missing'))
   )
 
-occupation_tb %>%
-  ggplot(mapping=aes(x=child_caretaker, fill=child_caretaker)) +
-  geom_bar() +
+# plot bar graph
+occup_caretaker %>%
+  ggplot(aes(x=caretaker, y=percentage, fill=background)) +
+  geom_bar(stat = "identity", position="dodge") + 
+  labs(x="Caretaker", y="Percentage (in %)", fill="Occupation") +
   theme_minimal() +
-  labs(x='',
-       caption = 'Respondent is currently employed but has not worked since last birth.') +
-  theme(axis.text.x = element_text(angle=15), legend.position='none') + 
+  coord_flip() +
   scale_x_discrete(
@@
         "child_in_school" = "schooling",
-        "other_child" = "siblings",
+        "other_female_child" = "other female child",
+        "other_male_child" = "other male child",
         "not_worked_since_birth" = "not worked since birth",
@@
         "missing" = "missing")
-  ) +
-  facet_wrap(vars(background),
-             dir = "v",
-             scales = "free")
-
-rm(occupation_tb)
+  )
 ```
@@
 ```{r employmentstatus, echo=FALSE, message=FALSE, fig.cap="Employment status"}
+# select employment status
 employment_status <-
@@
 
-employment_status_tb<-
-  tibble(
-    background =
-      c(""),
-    child_under_six = 
-      c("")
-  )
-
-for (r in 1:nrow(employment_status)){
-  status <- employment_status$background[r]
-  employment <-
-    tibble(
-      background = 
-        c(
-          rep(status, employment_status$number_of_employed_women[r])
-        ),
-      child_under_six = 
-        c(
-          rep("No_child_under_six", employment_status$no_child_under_six[r]),
-          rep("One_more_child_under_six", employment_status$one_more_child_under_six[r])
-        )
-      )
-
-  employment_status_tb <- bind_rows(employment_status_tb, employment)
-  rm(status,
-     employment)
-}
-rm(r)
-employment_status_tb <- employment_status_tb[-c(1),]
-
-employment_status_tb <-
-  employment_status_tb %>%
+# make dataset in long format
+emply_long <-
+  employment_status %>%
+  select(-c(character, total)) %>%
+  pivot_longer(!background, names_to = "variable", values_to = "count") %>%
   mutate(
@@
                                    'Seasonal',
-                                   'Occasional')
-                        )
+                                   'Occasional'))
   )
 
-employment_status_tb %>%
-  ggplot(mapping=aes(x=background, fill=child_under_six)) +
-  geom_bar(position='dodge') +
+emply_long %>%
+  filter(variable == 'no_child_under_six' | variable == 'one_more_child_under_six') %>%
+  ggplot(aes(x = background, y = count, fill = variable)) +
+  geom_bar(stat = "identity", position = "dodge") +
+  labs(x = "Employment status", y = "Number of employed women", fill = "Child under six") +
   theme_minimal() +
-  labs(x='Work status', y='number of employed', fill='Child under six') +
+  scale_fill_discrete(labels = c("No child under six", 
+                                 "One or more child under six")) +
   scale_x_discrete(labels = c("All_year_full_week" = "All year, full week",
                               "All_year_part_week" = "All year, part week")) +
-  theme(axis.text.x = element_text(angle=15)) +
-  scale_fill_discrete(labels = c("No child under six", 
-                                 "One or more child under six"))
-
-rm(employment_status_tb)
+  theme(axis.text.x = element_text(angle=15))
 ```
@@
 ```{r employment_statuschildcare, echo=FALSE, fig.cap="Distribution of child's caretaker by work status"}
-employment_status <-
-  employment_status %>%
+# caretaker aspect
+emply_caretaker <-
+  emply_long %>%
+  filter(str_detect(variable, "^caretaker_")) %>%
+  mutate(variable = str_replace_all(variable, "caretaker_", "")) %>%
+  rename(caretaker = variable,
+         percentage = count) %>%
   mutate(
-    caretaker_respondent = round(caretaker_respondent/100 * one_more_child_under_six, 0),
-    caretaker_partner = round(caretaker_partner/100 * one_more_child_under_six, 0),
-    caretaker_other_relative = round(caretaker_other_relative/100 * one_more_child_under_six, 0),
-    caretaker_neighbor = round(caretaker_neighbor/100 * one_more_child_under_six, 0),
-    caretaker_hired = round(caretaker_hired/100 * one_more_child_under_six, 0),
-    caretaker_child_in_school = round(caretaker_child_in_school/100 * one_more_child_under_six, 0),
-    caretaker_other_female_child = round(caretaker_other_female_child/100 * one_more_child_under_six, 0),
-    caretaker_other_male_child = round(caretaker_other_male_child/100 * one_more_child_under_six, 0),
-    caretaker_not_worked_since_birth = round(caretaker_not_worked_since_birth/100 * one_more_child_under_six, 0),
-    caretaker_other = round(caretaker_other/100 * one_more_child_under_six, 0),
-    caretaker_missing = round(caretaker_missing/100 * one_more_child_under_six, 0)
-    ) %>%
-  mutate(
-    caretaker_other_female_child = caretaker_other_female_child + caretaker_other_male_child
-  ) %>%
-  select(-caretaker_other_male_child) %>%
-  rename(caretaker_other_child = caretaker_other_female_child)
-
-employment_status_tb<-
-  tibble(
-    background =
-      c(""),
-    child_caretaker = 
-      c("")
-  )
-
-employment_status[3,13] <- employment_status[3,13] - 1
-
-for (r in 1:nrow(employment_status)){
-  status <- employment_status$background[r]
-  employment <-
-    tibble(
-      background = 
-        c(
-          rep(status, employment_status$one_more_child_under_six[r])
-        ),
-      child_caretaker = 
-        c(
-          rep("respondent", employment_status$caretaker_respondent[r]),
-          rep("partner", employment_status$caretaker_partner[r]),
-          rep("other_relative", employment_status$caretaker_other_relative[r]),
-          rep("neighbor", employment_status$caretaker_neighbor[r]),
-          rep("hired", employment_status$caretaker_hired[r]),
-          rep("child_in_school", employment_status$caretaker_child_in_school[r]),
-          rep("other_child", employment_status$caretaker_other_child[r]),
-          rep("not_worked_since_birth", employment_status$caretaker_not_worked_since_birth[r]),
-          rep("other", employment_status$caretaker_other[r]),
-          rep("missing", employment_status$caretaker_missing[r])
-        )
-      )
-
-  employment_status_tb <- bind_rows(employment_status_tb, employment)
-  rm(status,
-     employment)
-}
-rm(r)
-employment_status_tb <- employment_status_tb[-c(1),]
-
-employment_status_tb <-
-  employment_status_tb %>%
-  mutate(
-    background = factor(background,
-                        levels = c('All_year_full_week',
-                                   'All_year_part_week',
-                                   'Seasonal',
-                                   'Occasional')
-                        ),
-    child_caretaker = factor(child_caretaker,
+    caretaker = factor(caretaker, 
                        levels = c('respondent',
@@
 
-employment_status_tb %>%
-  ggplot(mapping=aes(x=child_caretaker, fill=child_caretaker)) +
-  geom_bar() +
+# plot the bar graph
+emply_caretaker %>%
+  ggplot(mapping=aes(x=caretaker, y=percentage, fill=caretaker)) +
+  geom_bar(stat = "identity", position="dodge") + 
   theme_minimal() +
@@
 
-rm(employment_status_tb)
 ```
 
+## Region
+
 ```{r map, warning = FALSE, echo = FALSE}
+# install.packages('rnaturalearth')
+# install.packages('sf')
 library(rnaturalearth)
 library(sf)
-#devtools::install_github("ropensci/rnaturalearthhires")
+# devtools::install_github("ropensci/rnaturalearthhires")
 # The st_centroid function takes the sf object and returns the center of 
@@
 
-```{r, echo=FALSE}
+```{r residence, echo=FALSE}
 # Urban vs Rural
@@
 
-```{r, echo=FALSE}
+```{r region, echo=FALSE}
 # region subdataset
@@
 
-```{r}
+```{r, echo=FALSE}
 # caretaker aspect
@@
 
-The number does not add up to 100. (truncation error)
+The number does not add up to 100. (round-off error)
 

### 2022-03-31 outputs/paper.Rmd
update

--- 2022-03-30 outputs/paper.Rmd
@@
                              'caretaker_other' = 'other',
-                             'caretaker_not_worked since_birth' = 'not worked since birth',
+                             'caretaker_not_worked_since_birth' = 'not worked since birth',
                              'caretaker_neighbor' = 'neighbour',
@@
 
+```{r}
+# region
+
+child <- region %>% 
+  select(-c(character, total)) %>% 
+  pivot_longer(!background, names_to = "x", values_to = "percentage")
+
+```
+
 # Discussions

### 2022-03-31 scripts/00-simulation.R

@@ -32,3 +32,4 @@ simulated_data <-
 
 
 
+a

### 2022-03-31 outputs/paper.Rmd
commit to update my file

--- 2022-03-31 outputs/paper.Rmd
@@
 
-```{r}
-# region
-
+```{r, echo = FALSE}
+# make dataset into long format
+# recode names
 child <- region %>% 
   select(-c(character, total)) %>% 
-  pivot_longer(!background, names_to = "x", values_to = "percentage")
+  pivot_longer(!background, names_to = "x", values_to = "percentage") %>% 
+  mutate(x = recode(x,
+                    'caretaker_respondent' = 'respondent',
+                    'caretaker_partner' = 'partner',
+                    'caretaker_other_relative' = 'other relative',
+                    'caretaker_other_male_child' = 'other male child',
+                    'caretaker_other_female_child' = 'other female child',
+                    'caretaker_other' = 'other',
+                    'caretaker_not_worked_since_birth' = 'not worked since birth',
+                    'caretaker_neighbor' = 'neighbour',
+                    'caretaker_missing' = 'missing',
+                    'caretaker_hired' = 'hired',
+                    'caretaker_child_in_school' = 'child in school',
+                    'no_child_under_six' = 'no child under six',
+                    'one_more_child_under_six' = 'one or more child under six',
+                    'number_of_employed_women' = 'number of employed women'))
+
+# plot bar graph for caretaker comparisons and administrative regions
+child %>% 
+  filter(x != 'number of employed women', x != 'no child under six', x!= 'one or more child under six') %>% 
+  ggplot(aes(x = x,
+             y = percentage,
+             fill = background)) +
+  geom_bar(stat = 'identity') + 
+  labs(x = "caretaker",
+       y = "percentage of XXX",
+       fill = "Administrative regions") +
+  theme_minimal() +
+  coord_flip() +
+  facet_wrap(~background) +
+  theme(legend.position = "bottom")
+
+```
+
+```{r, echo = FALSE}
+# number of employed women selected in the admiistrative regions
+child %>% 
+  filter(x == "number of employed women") %>% 
+  ggplot(aes(x = x,
+             y = percentage,
+             fill = background)) +
+  geom_bar(stat = 'identity',
+           position = 'dodge') +
+  labs(x = 'Administrative regions',
+       y = 'Number of employed women') +
+  theme_minimal() +
+  scale_fill_brewer(palette = 'Set3') +
+  theme(legend.position = "bottom")
+```
+
+```{r, echo = FALSE}
+# looking at the number of employed women selected in the different administrative regions
+# with the child under six
+child %>% 
+  filter(x == "no child under six" | x == "one or more child under six") %>% 
+  ggplot(aes(x = x,
+             y = percentage,
+             fill = background)) +
+  geom_bar(stat = 'identity') +
+  labs(x = "child",
+       y = "percentage of XXX",
+       fill = "Administrative regions") +
+  theme_minimal() +
+  coord_flip() +
+  facet_wrap(~background)
 

### 2022-03-31 outputs/paper.Rmd

--- 2022-03-31 outputs/paper.Rmd
@@
 # install.packages("stringr")
-# install.packages("ggforce")
 library(stringr) 
@@
 library(bookdown)
-library(ggforce)
 ```
@@
 
-## Mother's education
-
-```{r motheredu, echo=FALSE, fig.cap="Mother's Education level"}
-# select mother edu
-mother_edu <-
-  ghana %>%
-  filter(character=="Mother\'s_education") %>%
-  mutate(
-    no_child_under_six = round(no_child_under_six/100 * number_of_employed_women, 0),
-    one_more_child_under_six = round(one_more_child_under_six/100 * number_of_employed_women, 0)
-  )
-
-# make dataset in long format
-edu_long <-
-  mother_edu %>%
-  select(-c(character, total)) %>%
-  pivot_longer(!background, names_to = "variable", values_to = "count") %>%
-  mutate(
-    background = factor(background,
-                        levels = c('No_education',
-                                   'Primary',
-                                   'Middle',
-                                   'Secondary+')
-    )
-  )
-
-edu_long %>%
-  filter(variable == 'no_child_under_six' | variable == 'one_more_child_under_six') %>%
-  ggplot(aes(x = background, y = count, fill = variable)) +
-  geom_bar(stat = "identity", position = "dodge") +
-  labs(x = "Mother's education", y = "Number of employed women", fill = "Child under six") +
-  theme_minimal() +
-  scale_fill_discrete(labels = c("No child under six", 
-                                 "One or more child under six")) +
-  scale_x_discrete(labels = c("No_education" = "No education"))
-```
-
-Figure \@ref(fig:motheredu) shows that there are less women who studied more than secondary school, and only the secondary+ turned out to be more likely to have no child under six.
-
-```{r mothereduchildcare, echo=FALSE, fig.cap="Distribution of child's caretaker by mother's education level"}
-# caretaker aspect
-edu_caretaker <-
-  edu_long %>%
-  filter(str_detect(variable, "^caretaker_")) %>%
-  mutate(variable = str_replace_all(variable, "caretaker_", "")) %>%
-  rename(caretaker = variable,
-         percentage = count) %>%
-  mutate(
-    caretaker = factor(caretaker, 
-                       levels = c('respondent',
-                                  'partner',
-                                  'other_relative',
-                                  'neighbor',
-                                  'hired',
-                                  'child_in_school',
-                                  'other_female_child',
-                                  'other_male_child',
-                                  'not_worked_since_birth',
-                                  'other',
-                                  'missing')
-    )
-  )
-
-# plot the bar graph
-edu_caretaker %>%
-  ggplot(mapping=aes(x=caretaker, y=percentage, fill=caretaker)) +
-  geom_bar(stat = "identity", position="dodge") + 
-  theme_minimal() +
-  labs(x='',
-       caption = 'Respondent is currently employed but has not worked since last birth.') +
-  theme(legend.position='none') +
-  coord_flip() + 
-  scale_x_discrete(
-    labels = 
-      c("respondent" = "respondent",
-        "partner" = "partner",
-        "other_relative" = "relative",
-        "neighbor" = "neighbor",
-        "hired" = "hired",
-        "child_in_school" = "schooling",
-        "other_female_child" = "female child",
-        "other_male_child" = "male child",
-        "not_worked_since_birth" = "not worked since birth",
-        "other" = "other",
-        "missing" = "missing")
-  ) +
-  facet_wrap(vars(background),
-             dir = "v",
-             scales = "free",
-             labeller = labeller(background = 
-                                   c("No_education" = "No education",
-                                     "Primary" = "Primary",
-                                     "Middle" = "Middle",
-                                     "Secondary+" = "Secondary+")
-                                 )
-  )
-```
-
-## Work status
-
-```{r workstatus, echo=FALSE, message=FALSE, fig.cap="Work status"}
-# select work status
-work_status <-
-  ghana %>%
-  filter(character=="Work_status") %>%
-  mutate(
-    no_child_under_six = round(no_child_under_six/100 * number_of_employed_women, 0),
-    one_more_child_under_six = round(one_more_child_under_six/100 * number_of_employed_women, 0)
-  )
-
-# make dataset in long format
-work_long <-
-  work_status %>%
-  select(-c(character, total)) %>%
-  pivot_longer(!background, names_to = "variable", values_to = "count") %>%
-  mutate(
-    background = factor(background,
-                        levels = c('For_family_member',
-                                   'For_someone_else',
-                                   'Self-employed')
-    )
-  )
-
-work_long %>%
-  filter(variable == 'no_child_under_six' | variable == 'one_more_child_under_six') %>%
-  ggplot(aes(x = background, y = count, fill = variable)) +
-  geom_bar(stat = "identity", position = "dodge") +
-  labs(x = "Work status", y = "Number of employed women", fill = "Child under six") +
-  theme_minimal() +
-  labs(x='Work status', y='number of employed', fill='Child under six') +
-  scale_x_discrete(labels = c("For_family_member" = "For family member",
-                              "For_someone_else" = "For someone else")) + 
-  scale_fill_discrete(labels = c("No child under six", 
-                                 "One or more child under six"))
-```
-
-Figure \@ref(fig:workstatus) shows that
-
-```{r workstatuschildcare, echo=FALSE, fig.cap="Distribution of child's caretaker by work status"}
-# caretaker aspect
-work_caretaker <-
-  work_long %>%
-  filter(str_detect(variable, "^caretaker_")) %>%
-  mutate(variable = str_replace_all(variable, "caretaker_", "")) %>%
-  rename(caretaker = variable,
-         percentage = count) %>%
-  mutate(
-    caretaker = factor(caretaker, 
-                       levels = c('respondent',
-                                  'partner',
-                                  'other_relative',
-                                  'neighbor',
-                                  'hired',
-                                  'child_in_school',
-                                  'other_female_child',
-                                  'other_male_child',
-                                  'not_worked_since_birth',
-                                  'other',
-                                  'missing')
-    )
-  )
-
-# plot the bar graph
-work_caretaker %>%
-  ggplot(mapping=aes(x=caretaker, y=percentage, fill=caretaker)) +
-  geom_bar(stat = "identity", position="dodge") + 
-  theme_minimal() +
-  labs(x='',
-       caption = 'Respondent is currently employed but has not worked since last birth.') +
-  theme(legend.position='none') +
-  coord_flip() + 
-  scale_x_discrete(
-    labels = 
-      c("respondent" = "respondent",
-        "partner" = "partner",
-        "other_relative" = "relative",
-        "neighbor" = "neighbor",
-        "hired" = "hired",
-        "child_in_school" = "schooling",
-        "other_child" = "siblings",
-        "not_worked_since_birth" = "not worked since birth",
-        "other" = "other",
-        "missing" = "missing")
-  ) +
-  facet_wrap_paginate(vars(background),
-                      ncol=2,
-                      nrow=2,
-                      dir = "h",
-                      scales = "free",
-                      labeller = labeller(background = c("For_family_member" = "For family member",
-                                                         "For_someone_else" = "For someone else",
-                                                         "Self-employed" = "Self-employed")
-                      )
-  )
-
-```
-
-## Occupation
-
-```{r occupation, echo=FALSE, message=FALSE, fig.cap="Occupation"}
-# select occupation
-occupation <-
-  ghana %>%
-  filter(character=="Occupation") %>%
-  mutate(
-    no_child_under_six = round(no_child_under_six/100 * number_of_employed_women, 0),
-    one_more_child_under_six = round(one_more_child_under_six/100 * number_of_employed_women, 0)
-  )
-
-# make dataset in long format
-occup_long <-
-  occupation %>%
-  select(-c(character, total)) %>%
-  pivot_longer(!background, names_to = "variable", values_to = "count") %>%
-  mutate(
-    background = factor(background,
-                        levels = c('Agricultural',
-                                   'Nonagricultural')
-    )
-  )
-
-occup_long %>%
-  filter(variable == 'no_child_under_six' | variable == 'one_more_child_under_six') %>%
-  ggplot(aes(x = background, 
-             y = count,
-             fill = variable)) +
-  geom_bar(stat = "identity",
-           position = "dodge") +
-  labs(x = "Occupation",
-       y = "Number of employed women",
-       fill = "Child under six") +
-  theme_minimal() +
-  scale_fill_discrete(labels = c("No child under six", 
-                                 "One or more child under six"))
-```
-
-Figure \@ref(fig:occupation) shows that
-
-```{r occupationchildcare, echo=FALSE, fig.cap="Distribution of child's caretaker by work status"}
-# caretaker aspect
-occup_caretaker <-
-  occup_long %>%
-  filter(str_detect(variable, "^caretaker_")) %>%
-  mutate(variable = str_replace_all(variable, "caretaker_", "")) %>%
-  rename(caretaker = variable,
-         percentage = count) %>%
-  mutate(
-    caretaker = factor(caretaker, 
-                       levels = c('respondent',
-                                  'partner',
-                                  'other_relative',
-                                  'neighbor',
-                                  'hired',
-                                  'child_in_school',
-                                  'other_female_child',
-                                  'other_male_child',
-                                  'not_worked_since_birth',
-                                  'other',
-                                  'missing'))
-  )
-
-# plot bar graph
-occup_caretaker %>%
-  ggplot(aes(x=caretaker, y=percentage, fill=background)) +
-  geom_bar(stat = "identity", position="dodge") + 
-  labs(x="Caretaker", y="Percentage (in %)", fill="Occupation") +
-  theme_minimal() +
-  coord_flip() +
-  scale_x_discrete(
-    labels = 
-      c("respondent" = "respondent", 
-        "partner" = "partner",
-        "other_relative" = "relative",
-        "neighbor" = "neighbor",
-        "hired" = "hired",
-        "child_in_school" = "schooling",
-        "other_female_child" = "other female child",
-        "other_male_child" = "other male child",
-        "not_worked_since_birth" = "not worked since birth",
-        "other" = "other",
-        "missing" = "missing")
-  )
-```
-
-## Employment status
-
-```{r employmentstatus, echo=FALSE, message=FALSE, fig.cap="Employment status"}
-# select employment status
-employment_status <-
-  ghana %>%
-  filter(character=="Employment_status") %>%
-  mutate(
-    no_child_under_six = round(no_child_under_six/100 * number_of_employed_women, 0),
-    one_more_child_under_six = round(one_more_child_under_six/100 * number_of_employed_women, 0)
-  )
-
-# make dataset in long format
-emply_long <-
-  employment_status %>%
-  select(-c(character, total)) %>%
-  pivot_longer(!background, names_to = "variable", values_to = "count") %>%
-  mutate(
-    background = factor(background,
-                        levels = c('All_year_full_week',
-                                   'All_year_part_week',
-                                   'Seasonal',
-                                   'Occasional'))
-  )
-
-emply_long %>%
-  filter(variable == 'no_child_under_six' | variable == 'one_more_child_under_six') %>%
-  ggplot(aes(x = background, y = count, fill = variable)) +
-  geom_bar(stat = "identity", position = "dodge") +
-  labs(x = "Employment status", y = "Number of employed women", fill = "Child under six") +
-  theme_minimal() +
-  scale_fill_discrete(labels = c("No child under six", 
-                                 "One or more child under six")) +
-  scale_x_discrete(labels = c("All_year_full_week" = "All year, full week",
-                              "All_year_part_week" = "All year, part week")) +
-  theme(axis.text.x = element_text(angle=15))
-```
-
-Figure \@ref(fig:employmentstatus) shows that
-
-```{r employment_statuschildcare, echo=FALSE, fig.cap="Distribution of child's caretaker by work status"}
-# caretaker aspect
-emply_caretaker <-
-  emply_long %>%
-  filter(str_detect(variable, "^caretaker_")) %>%
-  mutate(variable = str_replace_all(variable, "caretaker_", "")) %>%
-  rename(caretaker = variable,
-         percentage = count) %>%
-  mutate(
-    caretaker = factor(caretaker, 
-                       levels = c('respondent',
-                                  'partner',
-                                  'other_relative',
-                                  'neighbor',
-                                  'hired',
-                                  'child_in_school',
-                                  'other_female_child',
-                                  'other_male_child',
-                                  'not_worked_since_birth',
-                                  'other',
-                                  'missing')
-    )
-  )
-
-# plot the bar graph
-emply_caretaker %>%
-  ggplot(mapping=aes(x=caretaker, y=percentage, fill=caretaker)) +
-  geom_bar(stat = "identity", position="dodge") + 
-  theme_minimal() +
-  labs(x='',
-       caption = 'Respondent is currently employed but has not worked since last birth.') +
-  theme(legend.position='none') +
-  coord_flip() + 
-  scale_x_discrete(
-    labels = 
-      c("respondent" = "respondent",
-        "partner" = "partner",
-        "other_relative" = "relative",
-        "neighbor" = "neighbor",
-        "hired" = "hired",
-        "child_in_school" = "schooling",
-        "other_child" = "siblings",
-        "not_worked_since_birth" = "not worked since birth",
-        "other" = "other",
-        "missing" = "missing")
-  ) +
-  facet_wrap(vars(background),
-             dir = "v",
-             scales = "free",
-             labeller = labeller(background = c("All_year_full_week" = "All year, full week",
-                                                "All_year_part_week" = "All year, part week",
-                                                "Seasonal" = "Seasonal",
-                                                "Occasional" = "Occasional")
-                                 )
-  )
-
-```
-
-## Region
-
-```{r map, warning = FALSE, echo = FALSE}
-# install.packages('rnaturalearth')
-# install.packages('sf')
-library(rnaturalearth)
-library(sf)
-# devtools::install_github("ropensci/rnaturalearthhires")
-# The st_centroid function takes the sf object and returns the center of 
-# the polygon, again as a sf object.
-map_ghana <- ne_states(country = 'Ghana', 
-                       returnclass = 'sf')  # grab provinces within Ghana
-
-map_ghana %>% 
-  ggplot() +
-  geom_sf( ) + 
-  geom_text(data = st_centroid(map_ghana), 
-            size = 3,
-             aes(x = longitude, 
-                 y = latitude,
-                 label= woe_name)) +
-  labs(title='Ghana Administrative Regions') +
-  theme_minimal()
-```
-
-```{r residence, echo=FALSE}
+```{r, echo=FALSE}
 # Urban vs Rural
@@
 
-```{r region, echo=FALSE}
+```{r, echo=FALSE}
 # region subdataset
@@
 
-```{r, echo=FALSE}
+```{r}
 # caretaker aspect
@@
 
-The number does not add up to 100. (round-off error)
+The number does not add up to 100. (truncation error)
 

### 2022-03-31 outputs/paper.Rmd
nothing much

@@
 ```{r, echo = FALSE}
-# number of employed women selected in the admiistrative regions
+# number of employed women selected in the administrative regions
 child %>% 

### 2022-03-31 outputs/paper.Rmd
Update Paper.Rmd

--- 2022-03-31 outputs/paper.Rmd
@@
 
+## Key features
+
 ```{r data, echo=FALSE}
@@
   select(background, no_child_under_six, one_more_child_under_six, caretaker_respondent, character) %>%
-  slice(1:10) %>%
+  slice(5:6, 13:20) %>%
   kable(caption='A subset of key features',
         col.names = c('Background', 'No child under six', '1+ child under six', 
-                      'Child\'s caretaker - respondent', 'Character'),
+                      'Child\'s caretaker- respondent', 'Category'),
         digits = 1,
         booktabs = FALSE,
-        linesep = "")
+        linesep = "") %>%
+  add_footnote("Numbers are in percentage (%).")
 ```
+
+The raw data contains the table created in 
+Some key features include background, no child under six, one or more child under six, and character.
+If the respondent answered to have one or more child under six, then they were further asked to indicate the caretaker of the child such as the respondent themselves, their partner, whether they hired a person for it, etc.
+The dataset is processed and analyzed using 'R' [@citeR] mainly with the 'tidyverse' [@citetidyverse] and 'dplyr' [@citedplyr] packages.
+The package 'janitor' [@citejanitor] is used to clean data, and the graphs and the tables are created in 'ggplot2' [@citeggplot2] and 'ggforce' [@citeggforce], and 'kableExtra' [@citekableExtra], respectively.
+The package 'stringr' [@citestringr] is used to manipulate the character string.
+The packages 'bookdown' [@citebookdown] and 'knitr' [@citeknitr] are used in generating the R Markdown report.
+Table \@ref(tab:data) created using 'kableExtra' [@citekableExtra] shows a subset of key features that will be discussed in this paper.
 
@@
 
-```{r, echo=FALSE}
+## Region
+
+```{r map, message=FALSE, echo = FALSE, warning=FALSE}
+# install.packages('rnaturalearth')
+# install.packages('sf')
+library(rnaturalearth) # we need to cite these packages as well
+library(sf)
+# devtools::install_github("ropensci/rnaturalearthhires")
+# The st_centroid function takes the sf object and returns the center of 
+# the polygon, again as a sf object.
+map_ghana <- ne_states(country = 'Ghana', 
+                       returnclass = 'sf')  # grab provinces within Ghana
+
+map_ghana %>% 
+  ggplot() +
+  geom_sf( ) + 
+  geom_text(data = st_centroid(map_ghana), 
+            size = 3,
+             aes(x = longitude, 
+                 y = latitude,
+                 label= woe_name)) +
+  labs(title='Ghana Administrative Regions') +
+  theme_minimal()
+```
+
+```{r residence, echo=FALSE}
 # Urban vs Rural
@@
 
-```{r}
+```{r areachildcare, echo=FALSE}
 # caretaker aspect
@@
                              'caretaker_other' = 'other',
-                             'caretaker_not_worked_since_birth' = 'not worked since birth',
+                             'caretaker_not_worked since_birth' = 'not worked since birth',
                              'caretaker_neighbor' = 'neighbour',
@@
 
-```{r, echo = FALSE}
-# make dataset into long format
-# recode names
-child <- region %>% 
+## Mother's education
+
+```{r motheredu, echo=FALSE, fig.cap="Mother's Education level", fig.width=6, fig.height=4}
+# select mother edu
+mother_edu <-
+  ghana %>%
+  filter(character=="Mother\'s_education") %>%
+  mutate(
+    no_child_under_six = round(no_child_under_six/100 * number_of_employed_women, 0),
+    one_more_child_under_six = round(one_more_child_under_six/100 * number_of_employed_women, 0)
+  )
+
+# make dataset in long format
+edu_long <-
+  mother_edu %>%
   select(-c(character, total)) %>%
-  pivot_longer(!background, names_to = "x", values_to = "percentage") %>% 
-  mutate(x = recode(x,
-                    'caretaker_respondent' = 'respondent',
-                    'caretaker_partner' = 'partner',
-                    'caretaker_other_relative' = 'other relative',
-                    'caretaker_other_male_child' = 'other male child',
-                    'caretaker_other_female_child' = 'other female child',
-                    'caretaker_other' = 'other',
-                    'caretaker_not_worked_since_birth' = 'not worked since birth',
-                    'caretaker_neighbor' = 'neighbour',
-                    'caretaker_missing' = 'missing',
-                    'caretaker_hired' = 'hired',
-                    'caretaker_child_in_school' = 'child in school',
-                    'no_child_under_six' = 'no child under six',
-                    'one_more_child_under_six' = 'one or more child under six',
-                    'number_of_employed_women' = 'number of employed women'))
+  pivot_longer(!background, names_to = "variable", values_to = "count") %>%
+  mutate(
+    background = factor(background,
+                        levels = c('No_education',
+                                   'Primary',
+                                   'Middle',
+                                   'Secondary+')
+    )
+  )
 
-# plot bar graph for caretaker comparisons and administrative regions
-child %>% 
-  filter(x != 'number of employed women', x != 'no child under six', x!= 'one or more child under six') %>% 
-  ggplot(aes(x = x,
-             y = percentage,
-             fill = background)) +
-  geom_bar(stat = 'identity') + 
-  labs(x = "caretaker",
-       y = "percentage of XXX",
-       fill = "Administrative regions") +
+edu_long %>%
+  filter(variable == 'no_child_under_six' | variable == 'one_more_child_under_six') %>%
+  ggplot(aes(x = background, y = count, fill = variable)) +
+  geom_bar(stat = "identity", position = "dodge") +
+  labs(x = "Mother's education", y = "Number of employed women", fill = "Child under six") +
   theme_minimal() +
+  scale_fill_discrete(labels = c("No child under six", 
+                                 "One or more child under six")) +
+  scale_x_discrete(labels = c("No_education" = "No education")) +
+  theme(legend.position = 'bottom')
+```
+
+Figure \@ref(fig:motheredu) shows that there are significantly less employed women who studied at secondary school and beyond it.
+Also, it can be observed that the employed women who did not continue their education until the secondary school are more likely to have a child under six, whereas there are more employed women who studied beyond the secondary school and have no child under six.
+In addition, when we take a look at the number of employed women who did not get any education, we can see that there are a lot more women with a child under six than without, and the difference between them is notably big.
+However, as the level of mother's education gets higher, the gap between having a child under six and no child under six decreases, and it gets reversed when the women completed the secondary school.
+
+```{r mothereduchildcare, echo=FALSE, fig.cap="Distribution of child's caretaker by mother's education level"}
+# caretaker aspect
+edu_caretaker <-
+  edu_long %>%
+  filter(str_detect(variable, "^caretaker_")) %>%
+  mutate(variable = str_replace_all(variable, "caretaker_", "")) %>%
+  rename(caretaker = variable,
+         percentage = count) %>%
+  mutate(
+    caretaker = factor(caretaker, 
+                       levels = c('respondent',
+                                  'partner',
+                                  'other_relative',
+                                  'neighbor',
+                                  'hired',
+                                  'child_in_school',
+                                  'other_female_child',
+                                  'other_male_child',
+                                  'not_worked_since_birth',
+                                  'other',
+                                  'missing')
+    )
+  )
+
+# plot the bar graph
+edu_caretaker %>%
+  ggplot(mapping=aes(x=caretaker, y=percentage, fill=caretaker)) +
+  geom_bar(stat = "identity", position="dodge") + 
+  theme_minimal() +
+  labs(x='',
+       caption = 'Respondent is currently employed but has not worked since last birth.') +
+  theme(legend.position='none') +
   coord_flip() + 
-  facet_wrap(~background) +
-  theme(legend.position = "bottom")
+  scale_x_discrete(
+    labels = 
+      c("respondent" = "respondent",
+        "partner" = "partner",
+        "other_relative" = "relative",
+        "neighbor" = "neighbor",
+        "hired" = "hired",
+        "child_in_school" = "schooling",
+        "other_female_child" = "female child",
+        "other_male_child" = "male child",
+        "not_worked_since_birth" = "not worked since birth",
+        "other" = "other",
+        "missing" = "missing")
+  ) +
+  facet_wrap(vars(background),
+             dir = "v",
+             scales = "free",
+             labeller = labeller(background = 
+                                   c("No_education" = "No education",
+                                     "Primary" = "Primary",
+                                     "Middle" = "Middle",
+                                     "Secondary+" = "Secondary+")
+                                 )
+  )
+```
+
+Figure \@ref(fig:mothereduchildcare) demonstrates that no matter what their education level is, it is mostly the employed women who take care of their children.
+When the level of the women's education is below high school, then it is followed by the relative.
+As the level of the women's education gets higher, then the percentage of schooling their children gets higher as well.
+Moreover, it is worthwhile to mention that the women who completed high school are more likely to stop working after having a birth compare to the women whose education level is lower than secondary school.
+
+## Work status
+
+```{r workstatus, echo=FALSE, message=FALSE, fig.cap="Work status", fig.width=6, fig.height=4}
+# select work status
+work_status <-
+  ghana %>%
+  filter(character=="Work_status") %>%
+  mutate(
+    no_child_under_six = round(no_child_under_six/100 * number_of_employed_women, 0),
+    one_more_child_under_six = round(one_more_child_under_six/100 * number_of_employed_women, 0)
+  )
+
+# make dataset in long format
+work_long <-
+  work_status %>%
+  select(-c(character, total)) %>%
+  pivot_longer(!background, names_to = "variable", values_to = "count") %>%
+  mutate(
+    background = factor(background,
+                        levels = c('For_family_member',
+                                   'For_someone_else',
+                                   'Self-employed')
+    )
+  )
+
+work_long %>%
+  filter(variable == 'no_child_under_six' | variable == 'one_more_child_under_six') %>%
+  ggplot(aes(x = background, y = count, fill = variable)) +
+  geom_bar(stat = "identity", position = "dodge") +
+  labs(x = "Work status", y = "Number of employed women", fill = "Child under six") +
+  theme_minimal() +
+  scale_x_discrete(labels = c("For_family_member" = "For family member",
+                              "For_someone_else" = "For someone else")) + 
+  scale_fill_discrete(labels = c("No child under six", 
+                                 "One or more child under six")) +
+  theme(legend.position='bottom')
+```
+
+Figure \@ref(fig:workstatus) shows that most of the employed women are self-employed.
+If the women work for themselves or for their family, then it is more likely to have one or more than one child under six, whereas when they work for someone else, there are more women who do not have a child under six.
+It should be noted that no child under six does not mean that they have no child.
+
+```{r workstatuschildcare, echo=FALSE, fig.cap="Distribution of child's caretaker by work status"}
+# caretaker aspect
+work_caretaker <-
+  work_long %>%
+  filter(str_detect(variable, "^caretaker_")) %>%
+  mutate(variable = str_replace_all(variable, "caretaker_", "")) %>%
+  rename(caretaker = variable,
+         percentage = count) %>%
+  mutate(
+    caretaker = factor(caretaker, 
+                       levels = c('respondent',
+                                  'partner',
+                                  'other_relative',
+                                  'neighbor',
+                                  'hired',
+                                  'child_in_school',
+                                  'other_female_child',
+                                  'other_male_child',
+                                  'not_worked_since_birth',
+                                  'other',
+                                  'missing')
+    )
+  )
+
+# plot the bar graph
+work_caretaker %>%
+  ggplot(mapping=aes(x=caretaker, y=percentage, fill=caretaker)) +
+  geom_bar(stat = "identity", position="dodge") + 
+  theme_minimal() +
+  labs(x='',
+       caption = 'Respondent is currently employed but has not worked since last birth.') +
+  theme(legend.position='none') +
+  coord_flip() + 
+  scale_x_discrete(
+    labels = 
+      c("respondent" = "respondent",
+        "partner" = "partner",
+        "other_relative" = "relative",
+        "neighbor" = "neighbor",
+        "hired" = "hired",
+        "child_in_school" = "schooling",
+        "other_child" = "siblings",
+        "not_worked_since_birth" = "not worked since birth",
+        "other" = "other",
+        "missing" = "missing")
+  ) +
+  facet_wrap_paginate(vars(background),
+                      ncol=2,
+                      nrow=2,
+                      dir = "h",
+                      scales = "free",
+                      labeller = labeller(background = c("For_family_member" = "For family member",
+                                                         "For_someone_else" = "For someone else",
+                                                         "Self-employed" = "Self-employed")
+                      )
+  )
 
@@
 
-```{r, echo = FALSE}
-# number of employed women selected in the admiistrative regions
-child %>% 
-  filter(x == "number of employed women") %>% 
-  ggplot(aes(x = x,
-             y = percentage,
-             fill = background)) +
-  geom_bar(stat = 'identity',
-           position = 'dodge') +
-  labs(x = 'Administrative regions',
-       y = 'Number of employed women') +
+It can be observed from Figure \@ref(fig:workstatuschildcare) that most of the employed women take care of their children by themselves regardless of whom they work for, and then it is their relatives who take care of their children.
+We can tell that if they are self-employed or work for the family, then it is more likely to have a family member taking care of their children under six, whereas the percentage of schooling their child under six is relatively higher when they work for someone else.
+
+## Occupation
+
+```{r occupation, echo=FALSE, message=FALSE, fig.cap="Occupation", fig.width=6, fig.height=4}
+# select occupation
+occupation <-
+  ghana %>%
+  filter(character=="Occupation") %>%
+  mutate(
+    no_child_under_six = round(no_child_under_six/100 * number_of_employed_women, 0),
+    one_more_child_under_six = round(one_more_child_under_six/100 * number_of_employed_women, 0)
+  )
+
+# make dataset in long format
+occup_long <-
+  occupation %>%
+  select(-c(character, total)) %>%
+  pivot_longer(!background, names_to = "variable", values_to = "count") %>%
+  mutate(
+    background = factor(background,
+                        levels = c('Agricultural',
+                                   'Nonagricultural')
+    )
+  )
+
+occup_long %>%
+  filter(variable == 'no_child_under_six' | variable == 'one_more_child_under_six') %>%
+  ggplot(aes(x = background, 
+             y = count,
+             fill = variable)) +
+  geom_bar(stat = "identity",
+           position = "dodge") +
+  labs(x = "Occupation",
+       y = "Number of employed women",
+       fill = "Child under six") +
   theme_minimal() +
-  scale_fill_brewer(palette = 'Set3') +
-  theme(legend.position = "bottom")
+  scale_fill_discrete(labels = c("No child under six", 
+                                 "One or more child under six")) +
+  theme(legend.position = 'bottom')
 ```
 
-```{r, echo = FALSE}
-# looking at the number of employed women selected in the different administrative regions
-# with the child under six
-child %>% 
-  filter(x == "no child under six" | x == "one or more child under six") %>% 
-  ggplot(aes(x = x,
-             y = percentage,
-             fill = background)) +
-  geom_bar(stat = 'identity') +
-  labs(x = "child",
-       y = "percentage of XXX",
-       fill = "Administrative regions") +
+Figure \@ref(fig:occupation) shows that there are more women working in the non-agricultural industry.
+When they work in the agricultural industry, the number of women who have a child under six is twice as many as the number of the ones who have no child under six.
+On the contrary, the number of women with no child under six is slightly higher than that of the ones with a child in the non-agricultural industry.
+
+```{r occupationchildcare, echo=FALSE, fig.cap="Distribution of child's caretaker by Occupation"}
+# caretaker aspect
+occup_caretaker <-
+  occup_long %>%
+  filter(str_detect(variable, "^caretaker_")) %>%
+  mutate(variable = str_replace_all(variable, "caretaker_", "")) %>%
+  rename(caretaker = variable,
+         percentage = count) %>%
+  mutate(
+    caretaker = factor(caretaker, 
+                       levels = c('respondent',
+                                  'partner',
+                                  'other_relative',
+                                  'neighbor',
+                                  'hired',
+                                  'child_in_school',
+                                  'other_female_child',
+                                  'other_male_child',
+                                  'not_worked_since_birth',
+                                  'other',
+                                  'missing'))
+  )
+
+# plot bar graph
+occup_caretaker %>%
+  ggplot(aes(x=caretaker, y=percentage, fill=background)) +
+  geom_bar(stat = "identity", position="dodge") + 
+  labs(x="Caretaker", y="Percentage (in %)", fill="Occupation") +
   theme_minimal() +
+  theme(legend.position='bottom') +
   coord_flip() +
-  facet_wrap(~background)
+  scale_x_discrete(
+    labels = 
+      c("respondent" = "respondent", 
+        "partner" = "partner",
+        "other_relative" = "relative",
+        "neighbor" = "neighbor",
+        "hired" = "hired",
+        "child_in_school" = "schooling",
+        "other_female_child" = "other female child",
+        "other_male_child" = "other male child",
+        "not_worked_since_birth" = "not worked since birth",
+        "other" = "other",
+        "missing" = "missing")
+  )
+```
+
+Figure \@ref(fig:occupationchildcare) illustrates that the percentage of the child's caretaker is highest in the respondent followed by the relative and schooling.
+This means that it is mostly the case that the employed women taking care of their children under six.
+In particular, more than a half of the employed women working in the agricultural industry are the primary caretaker of the child under six.
+Also, we can see that it is more likely for the female sibling to take care of the kids under six than the male sibling.
+
+## Employment status
+
+```{r employmentstatus, echo=FALSE, message=FALSE, fig.cap="Employment status", fig.width=6, fig.height=4}
+# select employment status
+employment_status <-
+  ghana %>%
+  filter(character=="Employment_status") %>%
+  mutate(
+    no_child_under_six = round(no_child_under_six/100 * number_of_employed_women, 0),
+    one_more_child_under_six = round(one_more_child_under_six/100 * number_of_employed_women, 0)
+  )
+
+# make dataset in long format
+emply_long <-
+  employment_status %>%
+  select(-c(character, total)) %>%
+  pivot_longer(!background, names_to = "variable", values_to = "count") %>%
+  mutate(
+    background = factor(background,
+                        levels = c('All_year_full_week',
+                                   'All_year_part_week',
+                                   'Seasonal',
+                                   'Occasional'))
+  )
+
+emply_long %>%
+  filter(variable == 'no_child_under_six' | variable == 'one_more_child_under_six') %>%
+  ggplot(aes(x = background, y = count, fill = variable)) +
+  geom_bar(stat = "identity", position = "dodge") +
+  labs(x = "Employment status", y = "Number of employed women", fill = "Child under six") +
+  theme_minimal() +
+  scale_fill_discrete(labels = c("No child under six", 
+                                 "One or more child under six")) +
+  scale_x_discrete(labels = c("All_year_full_week" = "All year, full week",
+                              "All_year_part_week" = "All year, part week")) +
+  theme(axis.text.x = element_text(angle=15), legend.position = 'bottom')
+```
+
+Figure \@ref(fig:employmentstatus) illustrates that majority of the employed women work for the entire year.
+Specifically, majority of them work full week.
+There are few women who work occasionally.
+On top of that, regardless of what their employment status is, there are more women who have one or more child under six.
+
+```{r employmentstatuschildcare, echo=FALSE, fig.cap="Distribution of child's caretaker by work status"}
+# caretaker aspect
+emply_caretaker <-
+  emply_long %>%
+  filter(str_detect(variable, "^caretaker_")) %>%
+  mutate(variable = str_replace_all(variable, "caretaker_", "")) %>%
+  rename(caretaker = variable,
+         percentage = count) %>%
+  mutate(
+    caretaker = factor(caretaker, 
+                       levels = c('respondent',
+                                  'partner',
+                                  'other_relative',
+                                  'neighbor',
+                                  'hired',
+                                  'child_in_school',
+                                  'other_female_child',
+                                  'other_male_child',
+                                  'not_worked_since_birth',
+                                  'other',
+                                  'missing')
+    )
+  )
+
+# plot the bar graph
+emply_caretaker %>%
+  ggplot(mapping=aes(x=caretaker, y=percentage, fill=caretaker)) +
+  geom_bar(stat = "identity", position="dodge") + 
+  theme_minimal() +
+  labs(x='',
+       caption = 'Respondent is currently employed but has not worked since last birth.') +
+  theme(legend.position='none') +
+  coord_flip() + 
+  scale_x_discrete(
+    labels = 
+      c("respondent" = "respondent",
+        "partner" = "partner",
+        "other_relative" = "relative",
+        "neighbor" = "neighbor",
+        "hired" = "hired",
+        "child_in_school" = "schooling",
+        "other_child" = "siblings",
+        "not_worked_since_birth" = "not worked since birth",
+        "other" = "other",
+        "missing" = "missing")
+  ) +
+  facet_wrap(vars(background),
+             dir = "v",
+             scales = "free",
+             labeller = labeller(background = c("All_year_full_week" = "All year, full week",
+                                                "All_year_part_week" = "All year, part week",
+                                                "Seasonal" = "Seasonal",
+                                                "Occasional" = "Occasional")
+                                 )
+  )
 
@@
 
+We can see from Figure \@ref(fig:employmentstatuschildcare) that the percentage of the respondent being the primary caretaker of the child under six is remarkably higher than the others in all four employment status.
+It exceeds 40% in all four cases, and in particular, it is close to 50% when they work all year, full week.
+Next, it is the relatives who mainly take care of the child under six.
+It should be noted that there are more women sending their kids under six to school when they work all year compare to the ones who do not work throughout the entire year.
+
 # Discussions
+
+## Child's caretaker
+
+Every figure that demonstrates the distribution of the child's caretaker shows that it is most likely to be the mother primarily taking care of their child under six.
+In other words, no matter where they live, what their education level is, and what type of a job they have, majority of the employed women is the primary caregiver of a child under six.
+Therefore, we can deduce that in Ghana it was common that the mother is primarily responsible for the care and raising of a child back in 1988.
+
+Besides the mother being the primary caregiver of a child under six, it can be observed from Figure \@ref(fig:mothereduchildcare), Figure \@ref(fig:workstatuschildcare), Figure \@ref(fig:occupationchildcare), Figure \@ref(fig:employmentstatuschildcare) that the relatives are likely to be the primary caregiver.
+Also, there are some family where the older siblings take care of their kids under six.
+Thus, we can tell that if there is a child under six in the family, then it was usual for the family member to take care of them in Ghana, 1988.
+
+In addition, we can observe that it is uncommon to hire a person to take care of the child under six.
+Instead of hiring a person, there are more cases reported that they sent the kids to school.
+Figure \@ref(fig:areachildcare) demonstrates that the percentage of the employed women sending their kids to school is higher in urban areas than in rural areas.
+Figure \@ref(fig:mothereduchildcare) shows that there are more women who send their kids to school as their education level gets higher.
+Figure \@ref(fig:workstatuschildcare) illustrates that it is more likely to have their kids in school when they work for someone else than when they work for the family member or when they are self-employed.
+Figure \@ref(fig:occupationchildcare) shows that the percentage of the employed women sending their kids to school is higher in non-agricultural sectors than in agricultural sectors.
+Lastly, we can see from Figure \@ref(fig:employmentstatuschildcare) that there are more women sending their kids to school when they work all year compare to the ones who work seasonally and occasionally.
+
+Lastly, we can tell that it is rarely the case that the mother stop working after having a birth.
+However, it is worth noting that the percentage of the employed women stop working after the birth is higher in urban areas than in rural areas from Figure \@ref(fig:areachildcare).
+In addition, Figure \@ref(fig:mothereduchildcare) shows that the women who completed high school tend to stop working after having a birth more than the ones with a lower education level.
+Moreover, the fact that the women who work for someone else are more likely to stop work since the last birth than the ones working for themselves or their family can be observed in Figure \@ref(fig:workstatuschildcare).
+Furthermore, Figure \@ref(fig:employmentstatuschildcare) shows that the percentage of the employed women stop working after the birth is higher among the women working all year than the ones working few times of the year.
 
@@
 
-The number does not add up to 100. (truncation error)
+The number does not add up to 100. (round-off error)
+
+'Mother's education level' might not be the accurate terminology to be used as it might be the case that the employed women not having any child.
 

### 2022-03-31 outputs/paper.Rmd
writing on data part

@@
 # install.packages("stringr")
-# install.packages("ggforce")
+#install.packages("ggforce")
 library(stringr) 
@@
 
-```{r map, message=FALSE, echo = FALSE, warning=FALSE}
+```{r map, message=FALSE, echo = FALSE, warning=FALSE, fig.cap="Ghana administrative regions"}
 # install.packages('rnaturalearth')
@@
                  label= woe_name)) +
-  labs(title='Ghana Administrative Regions') +
   theme_minimal()
@@
 
-```{r residence, echo=FALSE}
+Figure \@ref(fig:map) shows a map of Ghana and its administrative regions.
+Ghana has 10 administrative regions, namely, Upper West, Upper East, Northern, Brong Ahato, Western, Ashanti, Central, Eastern, Volta and Greater Accra.
+# Add details on largest provinces + population wise
+
+```{r residence, echo=FALSE, fig.cap="Comparison of the number of working mothers between urban and rural areas"}
 # Urban vs Rural
@@
 
-```{r region, echo=FALSE}
+Figure \@ref(fig:residence) shows the number of employed mothers in urban and rural areas.
+There are 1127 women who were selected in Urban areas while 2338 mothers were selected in rural areas.
+This is not surprising since a larger population live in rural areas.
+
+```{r region, echo=FALSE, fig.cap = "Comparison of the number of working mothers selected in the different administrative regions"}
 # region subdataset
@@
        y = "Number of employed women") +
-  theme_minimal()
+  theme_minimal() +
+  coord_flip()
 ```
 
-```{r, echo = FALSE}
+Figure @\ref(fig:region) shows the number of employed mothers in the different administrative regions.
+There were more working mothers in Greater Accra and Ashanti while Upper West had the least number of working mothers.
+The reason might be because of the number of people living in the different administrative regions are different, therefore, the population sample differed from one region to another.
+
+```{r childstatus, echo = FALSE, fig.cap = "Comparing the percentage of mothers having no child under six to one or more in both Urban and Rural areas"}
 # make dataset in long format
@@
   select(-c(character)) %>% 
-  pivot_longer(!background, names_to = "variables", values_to = "percentage")
+  pivot_longer(!background, names_to = "variables", values_to = "percentage") %>% 
+  mutate(variables = recode(variables,
+                            'no_child_under_six' = "No child under six", 
+                            'one_more_child_under_six' = "One or more child under six",
+                            'caretaker_respondent' = 'respondent',
+                             'caretaker_partner' = 'partner',
+                             'caretaker_other_relative' = 'other relative',
+                             'caretaker_other_male_child' = 'other male child',
+                             'caretaker_other_female_child' = 'other female child',
+                             'caretaker_other' = 'other',
+                             'caretaker_not_worked since_birth' = 'not worked since birth',
+                             'caretaker_neighbor' = 'neighbour',
+                             'caretaker_missing' = 'missing',
+                             'caretaker_hired' = 'hired',
+                             'caretaker_child_in_school' = 'child in school'))
 
@@
 resid_long %>% 
-  filter(variables == 'no_child_under_six' | variables == 'one_more_child_under_six') %>% 
+  filter(variables == 'No child under six' | variables == 'One or more child under six') %>% 
   ggplot(aes(x = background, 
@@
   labs(x = "Area",
-       y = "Percentage of women",
-       fill = "Children under six") +
+       y = "Percentage",
+       fill = "Child status") +
   theme_minimal() +
@@
 
-# need to recode names
-# change legends name
 ```
 
-```{r areachildcare, echo=FALSE}
+Figure \@ref(fig:childstatus) shows the child status of families in Urban and Rural areas.
+In rural areas, there is a larger percentage of working mothers having one or more child under six years old.
+The converse is true in Urban areas.
+Working mothers tend to have no child under six years old.
+
+```{r areachildcare, echo=FALSE, fig.cap = "Comparing child caretaker preferences in Urban and Rural areas"}
 # caretaker aspect
-
 # make dataset into long format
@@
 caretaker <- residence %>% 
-  select(-c(character, no_child_under_six, one_more_child_under_six, total, number_of_employed_women)) %>% 
+  select(-c(character, no_child_under_six, one_more_child_under_six, total, number_of_employed_women, caretaker_missing)) %>% 
   pivot_longer(!background, names_to = "caretakers", values_to = "percentage") %>% 
@@
 
+Figure @\ref(fig:areachildcare) shows the Ghanese families'caretaking preferences in both urban and rural areas.
+The preferred caretaking method in both urban and rural areas is the working mothers looking after their children by themselves.
+The next preferred method for in both areas would be to let the children be looked after by relatives.
+Other notable observations would be that families living in urban areas tend to put their child in school and in rural areas, families let the older female child to care for the under six years old child much more than in urban areas.
+
 ## Also comparison among the different administrative regions
+
+```{r caretakingregions, echo = FALSE, fig.cap = "Caretaking behaviour in the different administrative regions"}
+# make dataset into long format
+# recode names
+child <- region %>% 
+  select(-c(character, total, caretaker_missing)) %>% 
+  pivot_longer(!background, names_to = "x", values_to = "percentage") %>% 
+  mutate(x = recode(x,
+                    'caretaker_respondent' = 'respondent',
+                    'caretaker_partner' = 'partner',
+                    'caretaker_other_relative' = 'other relative',
+                    'caretaker_other_male_child' = 'other male child',
+                    'caretaker_other_female_child' = 'other female child',
+                    'caretaker_other' = 'other',
+                    'caretaker_not_worked_since_birth' = 'not worked since birth',
+                    'caretaker_neighbor' = 'neighbour',
+                    'caretaker_missing' = 'missing',
+                    'caretaker_hired' = 'hired',
+                    'caretaker_child_in_school' = 'child in school',
+                    'no_child_under_six' = 'no child under six',
+                    'one_more_child_under_six' = 'one or more child under six',
+                    'number_of_employed_women' = 'number of employed women'))
+
+# plot bar graph for caretaker comparisons and administrative regions
+child %>% 
+  filter(x != 'number of employed women', x != 'no child under six', x!= 'one or more child under six') %>% 
+  ggplot(aes(x = x,
+             y = percentage,
+             fill = background)) +
+  geom_bar(stat = 'identity') + 
+  labs(x = "caretaking preference",
+       y = "percentage",
+       fill = "Administrative regions") +
+  theme_minimal() +
+  coord_flip() +
+  facet_wrap(~background) +
+  theme(legend.position = "bottom")
+
+```
+
+Figure \@ref(fig:caretakingregions) shows the caretaking preference of Ghanese families in the different administrative regions.
+Working mothers tend to look after their child themselves the most in all regions.
+In Greater Accra, families choose to put their child in school the most compared to other administrative regions.
+Another observation is that the proportions of families opting to put their child in school in Northern, Upper East and Upper West are the lowest, namely 1.3%, 2.7% and 2.0% respectively.
+The other popular caretaking options after by the mother herself are by a relative or by another older female child.
+
+```{r chstatus, echo = FALSE, fig.cap = "Comparing the child status in different administrative regions"}
+# looking at the number of employed women selected in the different administrative regions
+# with the child under six
+child %>% 
+  filter(x == "no child under six" | x == "one or more child under six") %>% 
+  ggplot(aes(x = x,
+             y = percentage,
+             fill = background)) +
+  geom_bar(stat = 'identity') +
+  labs(x = "child status",
+       y = "percentage",
+       fill = "region") +
+  theme_minimal() +
+  theme(legend.position = "bottom") +
+  coord_flip() +
+  facet_wrap(~background)
+
+```
+
+Figure \@ref(fig:chstatus) shows the child status of Ghanese families in the different administrative regions.
+By child status, we mean the whether the families have children under six years old.
+Ghanese families tend to have one or more child under six years old more than no child under six with the exception of Greater Accra.
+The proportion of families with one or more child under six is slightly more pronounced in Northern, Upper West, Brong Ahafo and Upper East regions.
 

### 2022-04-01 outputs/paper.Rmd
small changes in graph for figure 5 &6

@@
   labs(x = "caretaking preference",
-       y = "percentage",
-       fill = "Administrative regions") +
+       y = "percentage") +
   theme_minimal() +
@@
   facet_wrap(~background) +
-  theme(legend.position = "bottom")
+  theme(legend.position = "none")
 
@@
   filter(x == "no child under six" | x == "one or more child under six") %>% 
-  ggplot(aes(x = x,
+  ggplot(aes(x = background,
              y = percentage,
-             fill = background)) +
-  geom_bar(stat = 'identity') +
+             fill = x)) +
+  geom_bar(stat = 'identity', position = "dodge", width = 0.8) +
   labs(x = "child status",
        y = "percentage",
-       fill = "region") +
+       fill = "child status") +
   theme_minimal() +
   theme(legend.position = "bottom") +
-  coord_flip() +
-  facet_wrap(~background)
+  coord_flip()
 

### 2022-04-01 scripts/00-simulation.R

@@ -115,26 +115,8 @@ simulated_dhs <-
              Child_under_six == 'No' ~ 'NA',
              TRUE ~ Caretaker
            ))
-=======
-simulated_data <-
-  tibble(
-    # Use 1 through to 3565 to represent each region
-    'Index' = 1:3565,
-    # Randomly choose one of the two options, with replacement, 3565 times
-    'Region' = sample(
-      x = c(
-        'Urban',
-        'Rural'
-      ),
-      size = 3565,
-      replace = TRUE
-    ))
 
 
 
 
-<<<<<<< HEAD
-a
-=======
->>>>>>> 8fcf61b5b72010f9cdca7652cc2d1aa309d04265
->>>>>>> 3145f6ddc9512cee5ab5f05e80768e5d6b0ec3fb
+

### 2022-04-02 outputs/paper.Rmd
Include Data source and methodology

@@
 ---
-title: "paper"
+title: "Childcare while their mom is working"
 author: 
@@
 # install.packages("stringr")
-#install.packages("ggforce")
+# install.packages("ggforce")
 library(stringr) 
@@
 
-```{r total, echo=FALSE, fig.cap="Data"}
-ghana %>%
-  mutate(
-    character = factor(character,
-                       levels = c("Residence",
-                                "Region",
-                                "Mother\'s_education",
-                                "Work_status",
-                                "Occupation",
-                                "Employment_status",
-                                "Total"
-                                )
-                       )
-           ) %>%
-  group_by(character) %>%
-  summarise(sum = sum(number_of_employed_women))
-```
+## Data Source
 
-Table \@ref(tab:total) shows that 3,566 participated the survey, but there are 3 whom did not answer their employment status, etc.
+This paper uses the Childcare While Working Data [@ghana1998] obtained from the Ghana Demographic and Health Survey 1998.
+The dataset was collected by downloading the final report of the 1988 Ghana census published in the Demographic and Health Surveys (DHS) programme (Do we need to cite dhs program as well?).
+The library 'pdftools' [@citepdftools] is used to download and read the content into R by parsing the pdf.
+
+## Methodology
+
+The 1998 Ghana Demographic and Health Survey (GDHS) is a national-level survey carried out in Ghana.
+This was a part of the worldwide Demographic and Health Surveys (DHS) programme, and was conducted by the Ghana Statistical Service collaborated with the Macro International Inc.
+It is designed to collect data on fertility, family planning, and maternal and child health.
+
+The survey frame was created using the list of Enumeration Areas (EAs) with population and household information from the 1984 Population Census.
+The 1998 GDHS used a two-stage stratified sampling.
+At the first stage of sampling, 400 EAs were selected using systematic sampling with probability proportional to size where the selected EAs are comprised of 138 in the urban areas and 262 in the rural areas.
+A complete household listing operation was then carried out in all the selected EAs to provide a sampling frame for the second stage selection of households.
+At the second stage of sampling, a systematic sample of 20 households per EA was selected in the Northern, Upper West and Upper East Regions, and 15 households per EA was selected in the other regions.
+
+The target sample size for the 1998 GDHS was 6,000 comprising 4,500 women of age 15-49 and men of age 15-59. A total of 4,843 women age 15-49 and 1,546 men age 15-59 completed the survey.
 
@@
 
-The raw data contains the table created in 
-Some key features include background, no child under six, one or more child under six, and character.
-If the respondent answered to have one or more child under six, then they were further asked to indicate the caretaker of the child such as the respondent themselves, their partner, whether they hired a person for it, etc.
+Some key features include background and a percent distribution of currently employed women by whether they have a child under six years of age at home according to selected background characteristics, Ghana 1998.
+If the respondent answered to have one or more child under six, then they were further asked to indicate the caretaker of the child such as the respondent themselves, their partner, or whether they hired a person for it, etc.
 The dataset is processed and analyzed using 'R' [@citeR] mainly with the 'tidyverse' [@citetidyverse] and 'dplyr' [@citedplyr] packages.
-The package 'janitor' [@citejanitor] is used to clean data, and the graphs and the tables are created in 'ggplot2' [@citeggplot2] and 'ggforce' [@citeggforce], and 'kableExtra' [@citekableExtra], respectively.
+The package 'janitor' [@citejanitor] is used to clean data, and the graphs are created in 'ggplot2' [@citeggplot2] and 'ggforce' [@citeggforce].
 The package 'stringr' [@citestringr] is used to manipulate the character string.
@@
 Table \@ref(tab:data) created using 'kableExtra' [@citekableExtra] shows a subset of key features that will be discussed in this paper.
+
+## General
+
+```{r general, echo=FALSE, fig.cap="Distribution of working mothers who have a child under six years"}
+totl <-
+  ghana %>%
+  filter(character=="Total") %>%
+  mutate(
+    no_child_under_six = round(no_child_under_six/100 * number_of_employed_women, 0),
+    one_more_child_under_six = round(one_more_child_under_six/100 * number_of_employed_women, 0)
+  )
+
+# make dataset in long format
+totl_long <-
+  totl %>%
+  select(-c(character, total)) %>%
+  pivot_longer(!background, names_to = "variable", values_to = "count")
+
+totl_long %>%
+  filter(variable == 'no_child_under_six' | variable == 'one_more_child_under_six') %>%
+  ggplot(aes(x = background, y = count, fill = variable)) +
+  geom_bar(stat = "identity", position = "dodge") +
+  geom_text(aes(label=paste(round(count/sum(count),4)*100, '%'), y=count-850),
+            size = 4.5,
+            position = position_dodge(width =.9)) +
+  labs(x = "", y = "Number of employed women", fill = "Child under six") +
+  theme_minimal() +
+  scale_fill_discrete(labels = c("No child under six", 
+                                 "One or more child under six")) +
+  scale_x_discrete(labels = c("No_education" = "No education")) +
+  theme(legend.position = 'bottom')
+```
+
+```{r generalchildcare, echo=FALSE, fig.cap="Distribution of the caretaker of the child when the mother is working", fig.height=4, fig.width=6}
+# caretaker aspect
+totl_caretaker <-
+  totl_long %>%
+  filter(str_detect(variable, "^caretaker_")) %>%
+  mutate(variable = str_replace_all(variable, "caretaker_", "")) %>%
+  rename(caretaker = variable,
+         percentage = count) %>%
+  mutate(
+    caretaker = factor(caretaker, 
+                       levels = c('respondent',
+                                  'partner',
+                                  'other_relative',
+                                  'neighbor',
+                                  'hired',
+                                  'child_in_school',
+                                  'other_female_child',
+                                  'other_male_child',
+                                  'not_worked_since_birth',
+                                  'other',
+                                  'missing')
+    )
+  )
+
+# plot the bar graph
+totl_caretaker %>%
+  ggplot(mapping=aes(x=caretaker, y=percentage, fill=caretaker)) +
+  geom_bar(stat = "identity", position="dodge") +
+  geom_text(aes(label=paste(percentage, '%'), y=percentage+2),
+            size = 3,
+            position = position_dodge(width=0.5)) +
+  theme_minimal() +
+  labs(x='') +
+  theme(legend.position='none') +
+  coord_flip() + 
+  scale_x_discrete(
+    labels = 
+      c("respondent" = "respondent",
+        "partner" = "partner",
+        "other_relative" = "relative",
+        "neighbor" = "neighbor",
+        "hired" = "hired",
+        "child_in_school" = "schooling",
+        "other_female_child" = "other female child",
+        "other_male_child" = "other male child",
+        "not_worked_since_birth" = "not worked since birth",
+        "other" = "other",
+        "missing" = "missing")
+  )
+```
+
+Figure \@ref(fig:general) shows that over a half of working mothers have a child under six years.
+Figure \@ref(fig:generalchildcare) illustrates that 47.6% of these mothers look after their own children while they are at work, 22.1% have their relatives other than their husband/partner to look after the child, 14% send the child to school or other institutional care.
+On top of that, less than 3 percent of women have husbands/partners to look after the child while they are at work.
+
+It should be noted that 1.9% has not worked since the last birth, and this represents the respondents who were not working at the time of the survey but had been employed at some time during the last 12 months.
 
@@
 There are 1127 women who were selected in Urban areas while 2338 mothers were selected in rural areas.
-This is not surprising since a larger population live in rural areas.
+There are less women living in urban who is currently working, and this is not surprising as a larger population live in rural areas.
 
@@
 Figure \@ref(fig:mothereduchildcare) demonstrates that no matter what their education level is, it is mostly the employed women who take care of their children.
-When the level of the women's education is below high school, then it is followed by the relative.
-As the level of the women's education gets higher, then the percentage of schooling their children gets higher as well.
+On the other hand, when the level of education is lower, then it is more likely for the respondent to look after their own children under six years.
+Over 50% of the women with no education takes care of their own children whearas less than 40% of the women with secondary or higher levels of education.
+As the level of the education gets higher, then the percentage of schooling their children gets higher as well.
 Moreover, it is worthwhile to mention that the women who completed high school are more likely to stop working after having a birth compare to the women whose education level is lower than secondary school.
@@
            position = "dodge") +
-  labs(x = "Occupation",
+  labs(x = "Sector",
        y = "Number of employed women",
@@
 This means that it is mostly the case that the employed women taking care of their children under six.
-In particular, more than a half of the employed women working in the agricultural industry are the primary caretaker of the child under six.
+Meanwhile, women who work in the agricultural sector are more likely to care for a child themselves than women in non-agricultural occupations.
+In particular, more than a half of the employed women working in the agricultural industry are the caretaker of the child under six whereas around 45% of the women working in non-agricultural sector take care of a child themselves.
 Also, we can see that it is more likely for the female sibling to take care of the kids under six than the male sibling.
@@
 We can see from Figure \@ref(fig:employmentstatuschildcare) that the percentage of the respondent being the primary caretaker of the child under six is remarkably higher than the others in all four employment status.
-It exceeds 40% in all four cases, and in particular, it is close to 50% when they work all year, full week.
+It exceeds 40% in all four cases, and in particular, full time working mothers are more likely to look after their own children than other mothers are.
 Next, it is the relatives who mainly take care of the child under six.
@@
 In other words, no matter where they live, what their education level is, and what type of a job they have, majority of the employed women is the primary caregiver of a child under six.
-Therefore, we can deduce that in Ghana it was common that the mother is primarily responsible for the care and raising of a child back in 1988.
+Therefore, we can deduce that in Ghana it was common that the mother is primarily responsible for the care and raising of a child back in 1998.
 
@@
 Also, there are some family where the older siblings take care of their kids under six.
-Thus, we can tell that if there is a child under six in the family, then it was usual for the family member to take care of them in Ghana, 1988.
+Thus, we can tell that if there is a child under six in the family, then it was usual for the family member to take care of them in Ghana, 1998.
 
@@
 
+It does not mention whether
+
 \newpage

### 2022-04-02 scripts/01-gather_data.R

@@ -16,10 +16,10 @@ library(tidyverse)
 library(stringi)
 
 download.file("https://dhsprogram.com/pubs/pdf/FR106/FR106.pdf",
-              "outputs/literature/1988_Ghana_DHS.pdf",
+              "outputs/literature/1998_Ghana_DHS.pdf",
               mode="wb")
 
-report <- pdf_text("outputs/literature/1988_Ghana_DHS.pdf")
+report <- pdf_text("outputs/literature/1998_Ghana_DHS.pdf")
 
 page_45<-stri_split_lines(report[[45]])[[1]]
 page_45<-page_45[page_45 != ""]

### 2022-04-02 outputs/paper.Rmd
Fix error in reference.bib

@@
 The dataset was collected by downloading the final report of the 1988 Ghana census published in the Demographic and Health Surveys (DHS) programme (Do we need to cite dhs program as well?).
-The library 'pdftools' [@citepdftools] is used to download and read the content into R by parsing the pdf.
+The package 'pdftools' [@citepdftools] is used to download and read the content into R by parsing the pdf.
 
@@
 ghana %>%
-  select(background, no_child_under_six, one_more_child_under_six, caretaker_respondent, character) %>%
-  slice(5:6, 13:20) %>%
+  select(background, no_child_under_six, one_more_child_under_six, caretaker_respondent, number_of_employed_women, character) %>%
+  slice(5:6, 13:20, 26) %>%
   kable(caption='A subset of key features',
         col.names = c('Background', 'No child under six', '1+ child under six', 
-                      'Child\'s caretaker- respondent', 'Category'),
+                      'Child\'s caretaker- respondent', 'Number of employed women', 'Category'),
         digits = 1,
@@
         linesep = "") %>%
+  kable_styling(position = "center")
   add_footnote("Numbers are in percentage (%).")
@@
 The dataset is processed and analyzed using 'R' [@citeR] mainly with the 'tidyverse' [@citetidyverse] and 'dplyr' [@citedplyr] packages.
+The package 'stringi' [@citestringi] is used to clean and prepare the dataset.
 The package 'janitor' [@citejanitor] is used to clean data, and the graphs are created in 'ggplot2' [@citeggplot2] and 'ggforce' [@citeggforce].
@@
 
-## General
+## General Overview
 
@@
 
-Figure \@ref(fig:general) shows that over a half of working mothers have a child under six years.
+We can tell from Table \@ref(tab:data) that there are 3,564 working mothers, and Figure \@ref(fig:general) shows that over a half of them have a child under six years.
 Figure \@ref(fig:generalchildcare) illustrates that 47.6% of these mothers look after their own children while they are at work, 22.1% have their relatives other than their husband/partner to look after the child, 14% send the child to school or other institutional care.

### 2022-04-02 outputs/paper.Rmd
Small updates in table

@@
   select(background, no_child_under_six, one_more_child_under_six, caretaker_respondent, number_of_employed_women, character) %>%
+  relocate(no_child_under_six, .after = one_more_child_under_six) %>%
   slice(5:6, 13:20, 26) %>%
   kable(caption='A subset of key features',
-        col.names = c('Background', 'No child under six', '1+ child under six', 
-                      'Child\'s caretaker- respondent', 'Number of employed women', 'Category'),
+        col.names = c('Background', 'Yes', 'No', 'Respondent', 'Number of employed women', 'Category'),
         digits = 1,
-        booktabs = FALSE,
-        linesep = "") %>%
-  kable_styling(position = "center")
-  add_footnote("Numbers are in percentage (%).")
+        booktabs = TRUE,
+        linesep = "",
+        align = c('l', 'c', 'c', 'c', 'c', 'l'),) %>%
+  add_header_above(c(" " = 1, "Child under six" = 2, "Child's caretaker" = 1, " " = 2),
+                   escape=F) %>%
+  add_footnote("Decimals are in percentage (%).")
 ```

### 2022-04-02 outputs/paper.Rmd
Complete Data and Discussion sections

--- 2022-04-02 outputs/paper.Rmd
@@
 
-This paper uses the Childcare While Working Data [@ghana1998] obtained from the Ghana Demographic and Health Survey 1998.
-The dataset was collected by downloading the final report of the 1988 Ghana census published in the Demographic and Health Surveys (DHS) programme (Do we need to cite dhs program as well?).
+This paper uses the Childcare While Working Data [@ghana1998] obtained from the 1998 Ghana Demographic and Health Survey (GDHS).
+The dataset was collected by downloading the final report of the 1998 GDHS published in the Demographic and Health Surveys (DHS) programme.
 The package 'pdftools' [@citepdftools] is used to download and read the content into R by parsing the pdf.
+The package 'stringi' [@citestringi] and 'tidyverse' [@citetidyverse] are then used to gather the data.
 
@@
 
-The 1998 Ghana Demographic and Health Survey (GDHS) is a national-level survey carried out in Ghana.
-This was a part of the worldwide Demographic and Health Surveys (DHS) programme, and was conducted by the Ghana Statistical Service collaborated with the Macro International Inc.
-It is designed to collect data on fertility, family planning, and maternal and child health.
+The 1998 Ghana Demographic and Health Survey was a national-level survey carried out in Ghana.
+This was a part of the worldwide Demographic and Health Surveys (DHS) programme and was conducted by the Ghana Statistical Service collaborated with the Macro International Inc.
+It was designed to collect data on fertility, family planning, and maternal and child health.
 
@@
 The 1998 GDHS used a two-stage stratified sampling.
-At the first stage of sampling, 400 EAs were selected using systematic sampling with probability proportional to size where the selected EAs are comprised of 138 in the urban areas and 262 in the rural areas.
+At the first stage of sampling, 400 EAs were selected using systematic sampling with probability proportional to size where the selected EAs comprised 138 in the urban areas and 262 in the rural areas.
 A complete household listing operation was then carried out in all the selected EAs to provide a sampling frame for the second stage selection of households.
@@
 
-The target sample size for the 1998 GDHS was 6,000 comprising 4,500 women of age 15-49 and men of age 15-59. A total of 4,843 women age 15-49 and 1,546 men age 15-59 completed the survey.
+The target sample size for the 1998 GDHS was 6,000 consisted of 4,500 women of age 15-49 and men of age 15-59. A total of 4,843 women age 15-49 and 1,546 men age 15-59 completed the survey.
 
@@
   select(background, no_child_under_six, one_more_child_under_six, caretaker_respondent, number_of_employed_women, character) %>%
+  relocate(no_child_under_six, .after = one_more_child_under_six) %>%
   slice(5:6, 13:20, 26) %>%
   kable(caption='A subset of key features',
-        col.names = c('Background', 'No child under six', '1+ child under six', 
-                      'Child\'s caretaker- respondent', 'Number of employed women', 'Category'),
+        col.names = c('Background Characteristic', 'Yes', 'No', 'Respondent', 'Number of employed women', 'Category'),
         digits = 1,
-        booktabs = FALSE,
-        linesep = "") %>%
-  kable_styling(position = "center")
-  add_footnote("Numbers are in percentage (%).")
+        booktabs = TRUE,
+        linesep = "",
+        align = c('l', 'c', 'c', 'c', 'c', 'l'),) %>%
+  add_header_above(c(" " = 1, "Child under six" = 2, "Child's caretaker" = 1, " " = 2),
+                   escape=F) %>%
+  add_footnote("Decimals are in percentage (%).")
 ```
@@
 If the respondent answered to have one or more child under six, then they were further asked to indicate the caretaker of the child such as the respondent themselves, their partner, or whether they hired a person for it, etc.
+
 The dataset is processed and analyzed using 'R' [@citeR] mainly with the 'tidyverse' [@citetidyverse] and 'dplyr' [@citedplyr] packages.
-The package 'stringi' [@citestringi] is used to clean and prepare the dataset.
-The package 'janitor' [@citejanitor] is used to clean data, and the graphs are created in 'ggplot2' [@citeggplot2] and 'ggforce' [@citeggforce].
+The 'janitor' [@citejanitor] is used to clean data, and the graphs are created in 'ggplot2' [@citeggplot2] and 'ggforce' [@citeggforce] packages.
+The map is created using in 'rnaturalearth' [@citernaturalearth] and 'sf' [@citesf] packages.
 The package 'stringr' [@citestringr] is used to manipulate the character string.
@@
 
-```{r general, echo=FALSE, fig.cap="Distribution of working mothers who have a child under six years"}
+```{r generalchildcare, echo=FALSE, fig.cap="Distribution of the caretaker of the child when the mother is working", fig.width=6, fig.height=4}
 totl <-
@@
   )
-
 # make dataset in long format
@@
 
-totl_long %>%
-  filter(variable == 'no_child_under_six' | variable == 'one_more_child_under_six') %>%
-  ggplot(aes(x = background, y = count, fill = variable)) +
-  geom_bar(stat = "identity", position = "dodge") +
-  geom_text(aes(label=paste(round(count/sum(count),4)*100, '%'), y=count-850),
-            size = 4.5,
-            position = position_dodge(width =.9)) +
-  labs(x = "", y = "Number of employed women", fill = "Child under six") +
-  theme_minimal() +
-  scale_fill_discrete(labels = c("No child under six", 
-                                 "One or more child under six")) +
-  scale_x_discrete(labels = c("No_education" = "No education")) +
-  theme(legend.position = 'bottom')
-```
-
-```{r generalchildcare, echo=FALSE, fig.cap="Distribution of the caretaker of the child when the mother is working", fig.height=4, fig.width=6}
 # caretaker aspect
@@
 
-We can tell from Table \@ref(tab:data) that there are 3,564 working mothers, and Figure \@ref(fig:general) shows that over a half of them have a child under six years.
-Figure \@ref(fig:generalchildcare) illustrates that 47.6% of these mothers look after their own children while they are at work, 22.1% have their relatives other than their husband/partner to look after the child, 14% send the child to school or other institutional care.
+We can tell from Table \@ref(tab:data) that there are 3,564 working mothers, and over a half of them have a child under six years.
+Figure \@ref(fig:generalchildcare) illustrates that 47.6% of these mothers look after their own children while they are at work, 22.1% have their relatives other than their husband/partner to take care of the child, 14% send the child to school or other institutional care.
 On top of that, less than 3 percent of women have husbands/partners to look after the child while they are at work.
 
-It should be noted that 1.9% has not worked since the last birth, and this represents the respondents who were not working at the time of the survey but had been employed at some time during the last 12 months.
+It should be noted that 1.9% has not worked since the last birth, and this indicates the percentage of the respondents who were not working at the time of the survey but had been employed at some time during the last 12 months.
 
@@
 
-```{r caretakingregions, echo = FALSE, fig.cap = "Caretaking behaviour in the different administrative regions"}
+```{r caretakingregions, echo = FALSE, fig.cap = "Caretaking behaviour in the different administrative regions", fig.width=7, fig.height=7}
 # make dataset into long format
@@
 
-Figure \@ref(fig:motheredu) shows that there are significantly less employed women who studied at secondary school and beyond it.
-Also, it can be observed that the employed women who did not continue their education until the secondary school are more likely to have a child under six, whereas there are more employed women who studied beyond the secondary school and have no child under six.
+Figure \@ref(fig:motheredu) shows that there are significantly less employed women who studied at secondary school or higher.
+Also, it can be observed that the working mothers who did not continue their education until the secondary school are more likely to have a child under six, whereas there are more employed women who studied beyond the secondary school and have no child under six.
 In addition, when we take a look at the number of employed women who did not get any education, we can see that there are a lot more women with a child under six than without, and the difference between them is notably big.
-However, as the level of mother's education gets higher, the gap between having a child under six and no child under six decreases, and it gets reversed when the women completed the secondary school.
+However, as the level of working mother's education gets higher, the gap between having a child under six and no child under six decreases, and it gets reversed when the women completed the secondary school.
 
-```{r mothereduchildcare, echo=FALSE, fig.cap="Distribution of child's caretaker by mother's education level"}
+```{r mothereduchildcare, echo=FALSE, fig.cap="Distribution of child's caretaker by mother's education level", fig.width=6, fig.height=4}
 # caretaker aspect
@@
   theme_minimal() +
-  labs(x='',
-       caption = 'Respondent is currently employed but has not worked since last birth.') +
+  labs(x='Caretaker while at work', y="Percentage (in %)") +
   theme(legend.position='none') +
@@
         "child_in_school" = "schooling",
-        "other_female_child" = "female child",
-        "other_male_child" = "male child",
+        "other_female_child" = "other female child",
+        "other_male_child" = "other male child",
         "not_worked_since_birth" = "not worked since birth",
@@
 
-Figure \@ref(fig:mothereduchildcare) demonstrates that no matter what their education level is, it is mostly the employed women who take care of their children.
-On the other hand, when the level of education is lower, then it is more likely for the respondent to look after their own children under six years.
-Over 50% of the women with no education takes care of their own children whearas less than 40% of the women with secondary or higher levels of education.
+Figure \@ref(fig:mothereduchildcare) demonstrates that no matter what their education level is, it is mostly the employed women who take care of their children while working.
+When the level of education is lower, then it is more likely for the respondent to look after their own children under six years.
+Over 50% of the women with no education take care of their own children whearas less than 40% of the women with secondary or higher levels of education do.
 As the level of the education gets higher, then the percentage of schooling their children gets higher as well.
@@
 
-```{r workstatuschildcare, echo=FALSE, fig.cap="Distribution of child's caretaker by work status"}
+```{r workstatuschildcare, echo=FALSE, fig.cap="Distribution of child's caretaker by work status", fig.width=6, fig.height=4}
 # caretaker aspect
@@
 
-It can be observed from Figure \@ref(fig:workstatuschildcare) that most of the employed women take care of their children by themselves regardless of whom they work for, and then it is their relatives who take care of their children.
+It can be observed from Figure \@ref(fig:workstatuschildcare) that most of the employed women take care of their children by themselves regardless of whom they work for, and then it is their relatives who take care of their children while they are at work.
 We can tell that if they are self-employed or work for the family, then it is more likely to have a family member taking care of their children under six, whereas the percentage of schooling their child under six is relatively higher when they work for someone else.
@@
 
-Figure \@ref(fig:occupation) shows that there are more women working in the non-agricultural industry.
-When they work in the agricultural industry, the number of women who have a child under six is twice as many as the number of the ones who have no child under six.
-On the contrary, the number of women with no child under six is slightly higher than that of the ones with a child in the non-agricultural industry.
+Figure \@ref(fig:occupation) shows that there are more women working in non-agricultural occupations.
+When we compare the mothers working in the agricultural sector, the number of women with a child under six is twice as many as the number of the ones without.
+On the contrary, the number of women with no child under six is slightly higher than that of the ones with a child in non-agricultural occupations.
 
-```{r occupationchildcare, echo=FALSE, fig.cap="Distribution of child's caretaker by Occupation"}
+```{r occupationchildcare, echo=FALSE, fig.cap="Distribution of child's caretaker by Occupation", fig.width=6, fig.height=4}
 # caretaker aspect
@@
   geom_bar(stat = "identity", position="dodge") + 
-  labs(x="Caretaker", y="Percentage (in %)", fill="Occupation") +
+  labs(x='Caretaker while at work', y="Percentage (in %)", fill="Occupation") +
   theme_minimal() +
@@
 
-Figure \@ref(fig:occupationchildcare) illustrates that the percentage of the child's caretaker is highest in the respondent followed by the relative and schooling.
-This means that it is mostly the case that the employed women taking care of their children under six.
+Figure \@ref(fig:occupationchildcare) illustrates that the percentage of the child's caretaker is highest in the respondent followed by the relative and schooling regardless of what type of jobs they have.
+This means that it is mostly the case that the employed women taking care of their children under six while they are working.
 Meanwhile, women who work in the agricultural sector are more likely to care for a child themselves than women in non-agricultural occupations.
-In particular, more than a half of the employed women working in the agricultural industry are the caretaker of the child under six whereas around 45% of the women working in non-agricultural sector take care of a child themselves.
-Also, we can see that it is more likely for the female sibling to take care of the kids under six than the male sibling.
+In particular, more than a half of the employed women working in the agricultural industry are the caretaker of the child under six whereas around 45% of the women working in non-agricultural sector take care of a child themselves while working.
+Furthermore, we can see that it is more likely for the female siblings to take care of the kids under six than the male siblings.
 
@@
 
-Figure \@ref(fig:employmentstatus) illustrates that majority of the employed women work for the entire year.
+Figure \@ref(fig:employmentstatus) illustrates that majority of the employed women work throughout the entire year.
 Specifically, majority of them work full week.
 There are few women who work occasionally.
-On top of that, regardless of what their employment status is, there are more women who have one or more child under six.
+On top of that, regardless of what their employment status is, more working mothers tend to have one or more child under six.
 
-```{r employmentstatuschildcare, echo=FALSE, fig.cap="Distribution of child's caretaker by work status"}
+```{r employmentstatuschildcare, echo=FALSE, fig.cap="Distribution of child's caretaker by work status", fig.width=6, fig.height=4}
 # caretaker aspect
@@
 We can see from Figure \@ref(fig:employmentstatuschildcare) that the percentage of the respondent being the primary caretaker of the child under six is remarkably higher than the others in all four employment status.
-It exceeds 40% in all four cases, and in particular, full time working mothers are more likely to look after their own children than other mothers are.
+It exceeds 40% in all four cases, and in particular, mothers working full time are more likely to look after their own children than the others.
 Next, it is the relatives who mainly take care of the child under six.
@@
 
-## Child's caretaker
+## Employed Women
 
-Every figure that demonstrates the distribution of the child's caretaker shows that it is most likely to be the mother primarily taking care of their child under six.
-In other words, no matter where they live, what their education level is, and what type of a job they have, majority of the employed women is the primary caregiver of a child under six.
+We can tell from Table \@ref(tab:data) that 3,564 out of 4,843 women of age 15-49 who completed the survey are employed.
+In other word, around three in four women were employed during the 12 months before the survey.
+Figure \@ref(fig:residence) shows that the number of employed women is greater in rural area.
+It is worth mentioning that even though rural areas typically have low population density, rural women are somewhat more likely than urban women to be currently working.
+Next, Figure \@ref(fig:region) illustrates that women residing in the Upper West Region are least likely to be employed.
+Together with Figure \@ref(fig:map), we can tell that the women are more likely to be employed when they live in the southern part of Ghana.
+The northern part of Ghana including Upper West, Upper East, and Northern Region are the bottom 3 regions in Figure \@ref(fig:region) which demonstrates the distribution of the number of employed women whereas the southern part of Ghana including Greater Accra, Ashanti, and Eastern Region are the top 3.
+
+Additionally, it is surprising to see from Figure \@ref(fig:motheredu) that the number of employed women whose education level is secondary school or higher is remarkably lower than that of the other education levels.
+Meanwhile, Figure \@ref(fig:occupation) shows that women are approximately twice as likely to be employed in the non-agricultural sector than in the agricultural sector.
+Lastly, when women are working, then Figure \@ref(fig:workstatus) tells that they are most likely to be self-employed and Figure \@ref(fig:employmentstatus) shows that they are most likely to work full-time.
+
+## Presence of Child Under Six
+
+Table \@ref(tab:data) shows that more than a half of the employed women has a child under six years.
+Figure \@ref(fig:childstatus) demonstrates that working women in rural area are more likely to have at least one child under six years whereas working women in urban area tend to have no child under six years.
+Figure \@ref(fig:motheredu) shows that as the level of working mother’s education gets higher, it is more likely to not have any child under six.
+
+Figure \@ref(fig:workstatus) illustrates that when they work for themselves or for their family, then there are more women with a child under six whereas when they work for someone else, then there are more women without.
+Figure \@ref(occupation) shows that when women are working in the agricultural sector, they are more likely to have a child under six whereas when they work in the non-agricultural sector, it is equally likely to have a child under six and without.
+Lastly, Figure \@ref(fig:employmentstatus) tells that it is more likely to have a child under six years regardless of their employment status.
+In other words, no matter whether they work full-time or part-time, there are more women who have at least one child under six years.
+
+## Child's Caretaker
+
+Every figure that demonstrates the distribution of the child's caretaker shows that it is most likely to be the mother primarily taking care of their child under six while they are at work.
+In other words, no matter where they live, what their education level is, and what type of a job they have, majority of the employed women is the look after their child.
 Therefore, we can deduce that in Ghana it was common that the mother is primarily responsible for the care and raising of a child back in 1998.
 
-Besides the mother being the primary caregiver of a child under six, it can be observed from Figure \@ref(fig:mothereduchildcare), Figure \@ref(fig:workstatuschildcare), Figure \@ref(fig:occupationchildcare), Figure \@ref(fig:employmentstatuschildcare) that the relatives are likely to be the primary caregiver.
-Also, there are some family where the older siblings take care of their kids under six.
+Besides the mother being the primary caregiver of a child under six, it can be observed from Figure \@ref(fig:mothereduchildcare), Figure \@ref(fig:workstatuschildcare), Figure \@ref(fig:occupationchildcare), Figure \@ref(fig:employmentstatuschildcare) that the relatives other than husband/partner are likely to look after children under six.
+Also, there are some family where the older siblings take care of their siblings under six.
 Thus, we can tell that if there is a child under six in the family, then it was usual for the family member to take care of them in Ghana, 1998.
 
-In addition, we can observe that it is uncommon to hire a person to take care of the child under six.
-Instead of hiring a person, there are more cases reported that they sent the kids to school.
+In addition, we can observe that it was uncommon to hire a person to take care of the child under six.
+Instead of hiring a person, there are more cases reported that they sent the kids to school or to institutional care.
 Figure \@ref(fig:areachildcare) demonstrates that the percentage of the employed women sending their kids to school is higher in urban areas than in rural areas.
-Figure \@ref(fig:mothereduchildcare) shows that there are more women who send their kids to school as their education level gets higher.
+Figure \@ref(fig:mothereduchildcare) shows that the number of working mothers sending their kids to school increases as their mother's education level gets higher.
 Figure \@ref(fig:workstatuschildcare) illustrates that it is more likely to have their kids in school when they work for someone else than when they work for the family member or when they are self-employed.
@@
 
-Lastly, we can tell that it is rarely the case that the mother stop working after having a birth.
+Lastly, we can tell that it is rarely the case that the mother stops working after having a birth.
 However, it is worth noting that the percentage of the employed women stop working after the birth is higher in urban areas than in rural areas from Figure \@ref(fig:areachildcare).
-In addition, Figure \@ref(fig:mothereduchildcare) shows that the women who completed high school tend to stop working after having a birth more than the ones with a lower education level.
-Moreover, the fact that the women who work for someone else are more likely to stop work since the last birth than the ones working for themselves or their family can be observed in Figure \@ref(fig:workstatuschildcare).
-Furthermore, Figure \@ref(fig:employmentstatuschildcare) shows that the percentage of the employed women stop working after the birth is higher among the women working all year than the ones working few times of the year.
+In addition, Figure \@ref(fig:mothereduchildcare) shows that the women who completed high school have more tendency to stop working after having a birth than the ones with a lower education level.
+Furthermore, Figure \@ref(fig:employmentstatuschildcare) shows that the percentage of the employed women stop working after the birth is highest when they work all year, full week.
 
@@
 
-The number does not add up to 100. (round-off error)
+4,843 women of age 15-49 completed the survey, and 3,564 of them responded that they are employed.
+Then, they were further asked whether they have a child under six.
+However, it is not mentioned whether their marital status was asked.
+If the question was asked to every women who participated the survey, then the respondents who answered to have no child under six might be single.
+This dataset is created to identify woman's overall status, and the percentage of the employed mothers not having a child is one of the important indicators.
+However, as it is unclear which group that not having a child under six refers to, it is hard to tell what factor this survey focuses on.
 
-'Mother's education level' might not be the accurate terminology to be used as it might be the case that the employed women not having any child.
+Additionally, it would have been better if they were first asked for their marital status and the presence of dependent children.
+They could have then asked the age of youngest child in the household or whether they have a child under six in the household.
+As married life has been reported to have a gendered effect on women and men's labour market outcomes [@maritalstatus], the distribution of the marital status among the employed women would be useful to tell the woman's overall status.
+In this context, if the respondent answered that they stopped working since the last birth, they could have further asked the reason for stopping working and about the job that they used to have before having a birth.
 
-It does not mention whether
+Lastly, only the employed women who have a child under six were further asked to indicate who takes care of their children while they are at work.
+The dataset included the percentage of the missing values, and we purposely excluded in plotting the graphs as they do not tell anything about the data itself and there were only few missing values.
+However, when we add up the percentage of all possible items including the missing values, there are several background characteristics where the numbers did not add up to a 100.
+As only the percentage is provided in the report, there might be a round-off error.
+Particularly, since the numbers were rounded to one-decimal place, there is a high possibility that there was a rounding error.
+To make the dataset more precise, they could have rounded to two-decimal places.
+
+On top of that, the survey asked for the employment situation during the 12-month reference period preceding the survey.
+However, the respondents were allowed to answer using their previous experiences.
+In particular, this applies to the respondents who had a job before having a birth but stopped working since the birth.
+Since we do not know the age of the youngest child in their household, they might have answered the questionnaire based on their employment situation prior to the 12-month reference period.
+Therefore, the time period does not match among the questions.
 

### 2022-04-02 outputs/paper.Rmd
intro + abstract

--- 2022-04-02 outputs/paper.Rmd
@@
 date: "`r format(Sys.time(), '%d %B %Y')`"
-abstract: "Four sentences"
+abstract: "Working mothers are often faced with the conflict of responsibility towards their children and the role they play at work.
+The Ghana Demographic and Health Survey (GDHS) forms part of a global initiative to collect data on family, fertility, and child health.
+In this paper, we used the 1998 GDHS and focused on the child care and working mothers aspect.
+Demographics and other aspects such as education tend to predict the child care preference.
+We found that families living in Greater Accra are more likely to send their child to school and the majority of working mothers look after their child by themselves.
+The analysis of the child care and working mothers data provides an insight on current trends and has significant implications for public policy and program decisions."
 output:
@@
 
-```{r library, echo=FALSE, message=FALSE}
+```{r library, echo=FALSE, message=FALSE, warning = FALSE}
 # install.packages('bookdown')
@@
 # Introduction
+
+Child care matter to the development of a child.
+Previously, women were thought to fit the traditional role of a mother, being at home and looking after her children.
+This thought is being challenged with a growing presence of women in the workforce, contributing to economic activity.
+Women are often faced with the conflicting role they have at home and at work.
+However, sometimes, mothers have to work out of necessity to contribute to the financial situation of their families.
+Families have to find ways to raise their children.
+The quality of child care given tend to have positive effects on the development of the child [@care].
+Having an idea of the current child care practices is important since it gives crucial information on the weaknesses of current policies and would give an insight on how to improve the situation around child care.
+
+In this paper, we examined child care decisions of working mothers across regions, the mothers' highest education level attained, their occupation, work and employment status in Ghana.
+We conducted a descriptive analysis of child status and childcare preferences.
+We first looked at the number of working mothers from the sample population, then examined child care practices based on employment status, education level among other factors.
+The differences in child care practices were noticeable in different regions.
+We found that most working mothers tend to look after their young child by themselves and those living in Greater Accra have a higher tendency to put their child in child care centres compared to other regions.
+Another observation was the highest level of education attained may have an influence on the number of children they have.
+The proportion of working mothers with at least secondary education with no child under six years old is lower than those with at least one or more child under six.
+
+The rest of the paper is divided into 4 sections.
+Section \@ref(data) explains the data source, the survey methodology and some of its key features, strengths and weaknesses.
+Section \@ref(results) relays the findings through graphs.
+Section @\ref(discussions) discusses in more detail what was found and some limitations of what we did and Section \@ref(appendix) contains a datasheet for the dataset we used.
 
@@
 Ghana has 10 administrative regions, namely, Upper West, Upper East, Northern, Brong Ahato, Western, Ashanti, Central, Eastern, Volta and Greater Accra.
-# Add details on largest provinces + population wise
+In 1998, about 57.6% of the Ghanese population were living in rural areas [@population].
 

### 2022-04-02 outputs/paper.Rmd
strength and weaknesses of methodology survey

@@
 The 1998 Ghana Demographic and Health Survey was a national-level survey carried out in Ghana.
-This was a part of the worldwide Demographic and Health Surveys (DHS) programme and was conducted by the Ghana Statistical Service collaborated with the Macro International Inc.
+This was a part of the worldwide Demographic and Health Surveys (DHS) programme and was conducted by the Ghana Statistical Service in collaboration with the Macro International Inc.
 It was designed to collect data on fertility, family planning, and maternal and child health.
+The 1998 GDHS was conducted from mid-November 1998 to mid-February 1999.
 
 The survey frame was created using the list of Enumeration Areas (EAs) with population and household information from the 1984 Population Census.
-The 1998 GDHS used a two-stage stratified sampling.
+The 1998 GDHS used a two-stage stratified sampling method.
 At the first stage of sampling, 400 EAs were selected using systematic sampling with probability proportional to size where the selected EAs comprised 138 in the urban areas and 262 in the rural areas.
@@
 
-The target sample size for the 1998 GDHS was 6,000 consisted of 4,500 women of age 15-49 and men of age 15-59. A total of 4,843 women age 15-49 and 1,546 men age 15-59 completed the survey.
+The target sample size for the 1998 GDHS was 6,000 consisted of 4,500 women of age 15-49 and men of age 15-59.
+A total of 4,843 women age 15-49 and 1,546 men age 15-59 completed the survey.
+To account for non-response, 6375 households were selected for interview.
+
+The GDHS was composed of 3 parts: the Household's questionnaire, the Women's questionnaire and the Men's questionnaire. All the questionnaires were modified to account for the situation in Ghana.
+
+The survey was conducted in person.
+The interview staff were first trained for a period of three weeks.
+It was conducted by a total of 14 teams, comprising a team supervisor, a field editor, three interviewers and a driver.
+The response rate was 97% for individual men and women selected.
+Non-response was mainly due to inability to find the selected interviewee at home.
+Repeated callbacks were made to try to reach the selected respondents.
+
+## Strengths
+
+The questionnaires were made available into the five major local languages (Akan, Ga, Ewe, Hausa, and Dagbani), making the survey accessible to a larger population.
+After the household listing, sport checks were conducted to make sure the work has been done correctly.
+Before the actual survey, a test was conducted and adjustments were made to the questionnaires based on the feedback obtained from the test.
+The questionnaire questions were comprehensive and detailed
+
+## Weaknesses
+
+Since the questionnaires were only available in the five major local languages, if the selected household was from a minor ethnic group and know only their own language, then it would be difficult for the interviewee to understand and answer the survey.
+Visitors who stayed a night before in the selected household were eligible for the interview.
+The visitor may be from a different region, so the targeted sample size for each region may be skewed.
 

### 2022-04-02 outputs/paper.Rmd
some grammar corrections

@@
 Section \@ref(results) relays the findings through graphs.
-Section @\ref(discussions) discusses in more detail what was found and some limitations of what we did and Section \@ref(appendix) contains a datasheet for the dataset we used.
+Section @\ref(discussion) discusses in more detail what was found and some limitations of what we did and Section \@ref(appendix) contains a datasheet for the dataset we used.
 
@@
 
-The GDHS was composed of 3 parts: the Household's questionnaire, the Women's questionnaire and the Men's questionnaire. All the questionnaires were modified to account for the situation in Ghana.
+The GDHS was composed of 3 parts: the Household's questionnaire, the Woman's questionnaire and the Man's questionnaire. All the questionnaires were modified to account for the situation in Ghana.
 
@@
 Repeated callbacks were made to try to reach the selected respondents.
+The results of the survey did not disclose any confidential information that might identify the respondents.
+The survey was a voluntary one but it is unclear if the purpose of the survey explained to the respondents for them to make an informed decision.
 
@@
 In 1998, about 57.6% of the Ghanese population were living in rural areas [@population].
+The Greater Accra is considered the most urbanized region of Ghana.
 
@@
 There are 1127 women who were selected in Urban areas while 2338 mothers were selected in rural areas.
-There are less women living in urban who is currently working, and this is not surprising as a larger population live in rural areas.
+There are less women living in urban who are currently working, and this is not surprising as a larger population live in rural areas.
 
@@
 There were more working mothers in Greater Accra and Ashanti while Upper West had the least number of working mothers.
-The reason might be because of the number of people living in the different administrative regions are different, therefore, the population sample differed from one region to another.
+The reason might be because of the number of people living in the different administrative regions are different, therefore, the sample size differed from one region to another.
+Greater Accra is the most urbanized region which implies more work opportunities and therefore, a larger population would be concentrated there.
 
@@
   labs(x = "Area",
-       y = "Percentage",
+       y = "Percent",
        fill = "Child status") +
@@
   labs(x = "Caretaker",
-       y = "Percentage of women",
+       y = "Percentage of working mothers",
        fill = "Area") +
@@
 Other notable observations would be that families living in urban areas tend to put their child in school and in rural areas, families let the older female child to care for the under six years old child much more than in urban areas.
-
-## Also comparison among the different administrative regions
 
@@
   labs(x = "caretaking preference",
-       y = "percentage") +
+       y = "percent") +
   theme_minimal() +
@@
 When the level of education is lower, then it is more likely for the respondent to look after their own children under six years.
-Over 50% of the women with no education take care of their own children whearas less than 40% of the women with secondary or higher levels of education do.
-As the level of the education gets higher, then the percentage of schooling their children gets higher as well.
-Moreover, it is worthwhile to mention that the women who completed high school are more likely to stop working after having a birth compare to the women whose education level is lower than secondary school.
+Over 50% of the women with no education take care of their own children whereas less than 40% of the women with secondary or higher levels of education do.
+As the level of the education gets higher, then the percentage of families choosing the option of schooling their children gets higher as well.
+Moreover, it is worthwhile to mention that the women who completed high school are more likely to stop working after having a birth compared to the women whose education level is lower than secondary school.
 
@@
 
-Figure \@ref(fig:workstatus) shows that most of the employed women are self-employed.
-If the women work for themselves or for their family, then it is more likely to have one or more than one child under six, whereas when they work for someone else, there are more women who do not have a child under six.
+Figure \@ref(fig:workstatus) shows that most employed mothers are self-employed.
+If the women work for themselves or for their family, then it is more likely to have one or more than one child under six years old, whereas when they work for someone else, there are more women who do not have a child under six years old.
 It should be noted that no child under six does not mean that they have no child.
@@
   theme_minimal() +
-  labs(x='Caretaker while at work', y="Percentage (in %)") +
+  labs(x='Caretaker while at work', y="Percent") +
   theme(legend.position='none') +
@@
 
-It can be observed from Figure \@ref(fig:workstatuschildcare) that most of the employed women take care of their children by themselves regardless of whom they work for, and then it is their relatives who take care of their children while they are at work.
-We can tell that if they are self-employed or work for the family, then it is more likely to have a family member taking care of their children under six, whereas the percentage of schooling their child under six is relatively higher when they work for someone else.
+It can be observed from Figure \@ref(fig:workstatuschildcare) that most employed women take care of their children by themselves regardless of whom they work for.
+It is their relatives who take care of their children while they are at work.
+We can tell that if they are self-employed or work for the family, then it is more likely to have a family member taking care of their children under six years old, whereas the percentage of families opting for schooling option is relatively higher when they work for someone else.
 
@@
 
-```{r occupationchildcare, echo=FALSE, fig.cap="Distribution of child's caretaker by Occupation", fig.width=6, fig.height=4}
+```{r occupationchildcare, echo=FALSE, fig.cap="Distribution of child's caretaker by occupation", fig.width=6, fig.height=4}
 # caretaker aspect
@@
   geom_bar(stat = "identity", position="dodge") + 
-  labs(x='Caretaker while at work', y="Percentage (in %)", fill="Occupation") +
+  labs(x='Caretaker while at work', y="Percent", fill="Occupation") +
   theme_minimal() +
@@
 
-Figure \@ref(fig:occupationchildcare) illustrates that the percentage of the child's caretaker is highest in the respondent followed by the relative and schooling regardless of what type of jobs they have.
-This means that it is mostly the case that the employed women taking care of their children under six while they are working.
-Meanwhile, women who work in the agricultural sector are more likely to care for a child themselves than women in non-agricultural occupations.
-In particular, more than a half of the employed women working in the agricultural industry are the caretaker of the child under six whereas around 45% of the women working in non-agricultural sector take care of a child themselves while working.
-Furthermore, we can see that it is more likely for the female siblings to take care of the kids under six than the male siblings.
+Figure \@ref(fig:occupationchildcare) illustrates that the percentage of the respondent herself being the child's caretaker is highest,followed by relative and schooling regardless of the type of jobs they have.
+Women who work in the agricultural sector are more likely to care for a child themselves than women in non-agricultural occupations.
+In particular, more than a half of the employed women working in the agricultural industry take care of their child themselves whereas around 45% of the women working in non-agricultural sector take care of their child themselves.
+Another observation is that female siblings are more likely to look after their younger siblings compared to male siblings.
 
@@
 
-Figure \@ref(fig:employmentstatus) illustrates that majority of the employed women work throughout the entire year.
+Figure \@ref(fig:employmentstatus) illustrates that majority of employed women work throughout the entire year.
 Specifically, majority of them work full week.
 There are few women who work occasionally.
-On top of that, regardless of what their employment status is, more working mothers tend to have one or more child under six.
+On top of that, regardless of their employment status, more working mothers tend to have one or more child under six years old.
 
@@
 
-We can see from Figure \@ref(fig:employmentstatuschildcare) that the percentage of the respondent being the primary caretaker of the child under six is remarkably higher than the others in all four employment status.
+We can see from Figure \@ref(fig:employmentstatuschildcare) that the proportion of respondents being the primary caretaker is remarkably higher than the other caretaker options in all four employment status.
 It exceeds 40% in all four cases, and in particular, mothers working full time are more likely to look after their own children than the others.
@@
 
-# Discussions
+# Discussion
 
@@
 
-We can tell from Table \@ref(tab:data) that 3,564 out of 4,843 women of age 15-49 who completed the survey are employed.
-In other word, around three in four women were employed during the 12 months before the survey.
+We can tell from Table \@ref(tab:data) that 3,564 out of 4,843 women of age 15-49 who completed the survey are employed and have children.
+In other words, around three in four women were employed during the 12 months before the survey.
 Figure \@ref(fig:residence) shows that the number of employed women is greater in rural area.
@@
 
-## Presence of Child Under Six
+## Presence of Child Under Six Years Old
 

### 2022-04-03 outputs/paper.Rmd
Completed except for the title

--- 2022-04-02 outputs/paper.Rmd
@@
 abstract: "Working mothers are often faced with the conflict of responsibility towards their children and the role they play at work.
-The Ghana Demographic and Health Survey (GDHS) forms part of a global initiative to collect data on family, fertility, and child health.
+The Ghana Demographic and Health Survey (GDHS) forms a part of a global initiative to collect data on family, fertility, and child health.
 In this paper, we used the 1998 GDHS and focused on the child care and working mothers aspect.
-Demographics and other aspects such as education tend to predict the child care preference.
-We found that families living in Greater Accra are more likely to send their child to school and the majority of working mothers look after their child by themselves.
-The analysis of the child care and working mothers data provides an insight on current trends and has significant implications for public policy and program decisions."
+Geographics and other aspects such as education are used to predict child care preference.
+We found that families living in Greater Accra are more likely to send their children to school and the majority of working mothers look after their children by themselves.
+The analysis of the child care and working mothers data provides insight into current trends and has significant implications for public policy and program decisions."
 output:
@@
 
-```{r library, echo=FALSE, message=FALSE, warning = FALSE}
+```{r library, echo=FALSE, message=FALSE}
 # install.packages('bookdown')
@@
 
-Child care matter to the development of a child.
+Child care matters to the development of a child.
 Previously, women were thought to fit the traditional role of a mother, being at home and looking after her children.
@@
 Families have to find ways to raise their children.
-The quality of child care given tend to have positive effects on the development of the child [@care].
+The quality of child care given tends to have positive effects on the development of the child [@care].
 Having an idea of the current child care practices is important since it gives crucial information on the weaknesses of current policies and would give an insight on how to improve the situation around child care.
@@
 The differences in child care practices were noticeable in different regions.
-We found that most working mothers tend to look after their young child by themselves and those living in Greater Accra have a higher tendency to put their child in child care centres compared to other regions.
+We found that most working mothers tend to look after their young child by themselves and those living in Greater Accra have a higher tendency to put their children in child care centres compared to other regions.
 Another observation was the highest level of education attained may have an influence on the number of children they have.
-The proportion of working mothers with at least secondary education with no child under six years old is lower than those with at least one or more child under six.
+The proportion of working mothers with at least secondary education with no child under six years old is lower than those with at least one or more children under six.
 
 The rest of the paper is divided into 4 sections.
-Section \@ref(data) explains the data source, the survey methodology and some of its key features, strengths and weaknesses.
+Section \@ref(data) explains the data source, the survey methodology, and some of its key features, strengths, and weaknesses.
 Section \@ref(results) relays the findings through graphs.
-Section @\ref(discussions) discusses in more detail what was found and some limitations of what we did and Section \@ref(appendix) contains a datasheet for the dataset we used.
+Section @\ref(discussion) discusses in more detail what was found and some limitations of what we did and Section \@ref(appendix) contains a datasheet for the dataset we used.
 
@@
 The 1998 Ghana Demographic and Health Survey was a national-level survey carried out in Ghana.
-This was a part of the worldwide Demographic and Health Surveys (DHS) programme and was conducted by the Ghana Statistical Service in collaboration with the Macro International Inc.
+It was conducted by the Ghana Statistical Service collaborated with the Macro International Inc.
 It was designed to collect data on fertility, family planning, and maternal and child health.
-The 1998 GDHS was conducted from mid-November 1998 to mid-February 1999.
 
 The survey frame was created using the list of Enumeration Areas (EAs) with population and household information from the 1984 Population Census.
-The 1998 GDHS used a two-stage stratified sampling method.
+The 1998 GDHS used a two-stage stratified sampling.
 At the first stage of sampling, 400 EAs were selected using systematic sampling with probability proportional to size where the selected EAs comprised 138 in the urban areas and 262 in the rural areas.
@@
 
-The GDHS was composed of 3 parts: the Household's questionnaire, the Women's questionnaire and the Men's questionnaire. All the questionnaires were modified to account for the situation in Ghana.
+This was a part of the worldwide Demographic and Health Surveys (DHS) programme, and the GDHS was composed of 3 parts: the Household's questionnaire, the Woman's questionnaire and the Man's questionnaire.
+All the questionnaires were modified to account for the situation in Ghana.
 
@@
 
-The questionnaires were made available into the five major local languages (Akan, Ga, Ewe, Hausa, and Dagbani), making the survey accessible to a larger population.
-After the household listing, sport checks were conducted to make sure the work has been done correctly.
+The questionnaires were made available in the five major local languages (Akan, Ga, Ewe, Hausa, and Dagbani), making the survey accessible to a larger population.
+After the household listing, sports checks were conducted to make sure the work has been done correctly.
 Before the actual survey, a test was conducted and adjustments were made to the questionnaires based on the feedback obtained from the test.
-The questionnaire questions were comprehensive and detailed
+The questions were comprehensive and detailed to collect information on the socio-economic status of the household.
 
@@
 Some key features include background and a percent distribution of currently employed women by whether they have a child under six years of age at home according to selected background characteristics, Ghana 1998.
-If the respondent answered to have one or more child under six, then they were further asked to indicate the caretaker of the child such as the respondent themselves, their partner, or whether they hired a person for it, etc.
+If the respondent answered to have one or more children under six, then they were further asked to indicate the caretaker of the child such as the respondent themselves, their partner, or whether they hired a person for it, etc.
 
@@
 
-It should be noted that 1.9% has not worked since the last birth, and this indicates the percentage of the respondents who were not working at the time of the survey but had been employed at some time during the last 12 months.
+It should be noted that 1.9% have not worked since their last birth, and this indicates the percentage of the respondents who were not working at the time of the survey but had been employed at some time during the last 12 months.
 
@@
 # install.packages('sf')
-library(rnaturalearth) # we need to cite these packages as well
+library(rnaturalearth)
 library(sf)
@@
 Figure \@ref(fig:map) shows a map of Ghana and its administrative regions.
-Ghana has 10 administrative regions, namely, Upper West, Upper East, Northern, Brong Ahato, Western, Ashanti, Central, Eastern, Volta and Greater Accra.
+Ghana has 10 administrative regions, namely, Upper West, Upper East, Northern, Brong Ahato, Western, Ashanti, Central, Eastern, Volta, and Greater Accra.
 In 1998, about 57.6% of the Ghanese population were living in rural areas [@population].
+Greater Accra is considered the most urbanized region of Ghana.
 
@@
 There were more working mothers in Greater Accra and Ashanti while Upper West had the least number of working mothers.
-The reason might be because of the number of people living in the different administrative regions are different, therefore, the population sample differed from one region to another.
+The reason might be because the number of people living in the different administrative regions is different, therefore, the sample size differed from one region to another.
+Greater Accra is the most urbanized region which implies more work opportunities and therefore, a larger population would be concentrated there.
 
@@
                              'caretaker_missing' = 'missing',
-                             'caretaker_hired' = 'hired',
-                             'caretaker_child_in_school' = 'child in school'))
+                             'caretaker_hired' = 'hired help',
+                             'caretaker_child_in_school' = 'schooling'))
 
@@
 Figure \@ref(fig:childstatus) shows the child status of families in Urban and Rural areas.
-In rural areas, there is a larger percentage of working mothers having one or more child under six years old.
+In rural areas, there is a larger percentage of working mothers having one or more children under six years old.
 The converse is true in Urban areas.
@@
 
-Figure @\ref(fig:areachildcare) shows the Ghanese families'caretaking preferences in both urban and rural areas.
+Figure @\ref(fig:areachildcare) shows the Ghanese families' caretaking preferences in both urban and rural areas.
 The preferred caretaking method in both urban and rural areas is the working mothers looking after their children by themselves.
-The next preferred method for in both areas would be to let the children be looked after by relatives.
-Other notable observations would be that families living in urban areas tend to put their child in school and in rural areas, families let the older female child to care for the under six years old child much more than in urban areas.
-
-## Also comparison among the different administrative regions
+The next preferred method in both areas would be to let the children be looked after by relatives.
+Other notable observations would be that families living in urban areas tend to put their children in school and in rural areas, families let the older female child care for the under six years old child much more than in urban areas.
 
@@
                     'caretaker_missing' = 'missing',
-                    'caretaker_hired' = 'hired',
-                    'caretaker_child_in_school' = 'child in school',
+                    'caretaker_hired' = 'hired help',
+                    'caretaker_child_in_school' = 'schooling',
                     'no_child_under_six' = 'no child under six',
@@
 Figure \@ref(fig:caretakingregions) shows the caretaking preference of Ghanese families in the different administrative regions.
-Working mothers tend to look after their child themselves the most in all regions.
+Working mothers tend to look after their children themselves the most in all regions.
 In Greater Accra, families choose to put their child in school the most compared to other administrative regions.
-Another observation is that the proportions of families opting to put their child in school in Northern, Upper East and Upper West are the lowest, namely 1.3%, 2.7% and 2.0% respectively.
-The other popular caretaking options after by the mother herself are by a relative or by another older female child.
+Another observation is that the proportions of families opting to put their child in school in Northern, Upper East, and Upper West are the lowest, namely 1.3%, 2.7%, and 2.0% respectively.
+The other popular caretaking options after the mother herself are by a relative or by another older female child.
 
@@
 Figure \@ref(fig:chstatus) shows the child status of Ghanese families in the different administrative regions.
-By child status, we mean the whether the families have children under six years old.
-Ghanese families tend to have one or more child under six years old more than no child under six with the exception of Greater Accra.
-The proportion of families with one or more child under six is slightly more pronounced in Northern, Upper West, Brong Ahafo and Upper East regions.
+By child status, we mean whether the families have children under six years old.
+Ghanese families tend to have one or more children under six years old rather than no child under six with the exception of Greater Accra.
+The proportion of families with one or more children under six is slightly more pronounced in Northern, Upper West, Brong Ahafo, and Upper East regions.
 
@@
 
-Figure \@ref(fig:motheredu) shows that there are significantly less employed women who studied at secondary school or higher.
-Also, it can be observed that the working mothers who did not continue their education until the secondary school are more likely to have a child under six, whereas there are more employed women who studied beyond the secondary school and have no child under six.
+Figure \@ref(fig:motheredu) shows that there are significantly fewer employed women who studied at secondary school or higher.
+Also, it can be observed that the working mothers who did not continue their education until secondary school are more likely to have a child under six, whereas there are more employed women who studied beyond secondary school and have no child under six.
 In addition, when we take a look at the number of employed women who did not get any education, we can see that there are a lot more women with a child under six than without, and the difference between them is notably big.
-However, as the level of working mother's education gets higher, the gap between having a child under six and no child under six decreases, and it gets reversed when the women completed the secondary school.
+However, as the level of working mothers' education gets higher, the gap between having a child under six and no child under six decreases, and it gets reversed when the women complete secondary school.
 
@@
         "neighbor" = "neighbor",
-        "hired" = "hired",
+        "hired" = "hired help",
         "child_in_school" = "schooling",
@@
 When the level of education is lower, then it is more likely for the respondent to look after their own children under six years.
-Over 50% of the women with no education take care of their own children whearas less than 40% of the women with secondary or higher levels of education do.
-As the level of the education gets higher, then the percentage of schooling their children gets higher as well.
-Moreover, it is worthwhile to mention that the women who completed high school are more likely to stop working after having a birth compare to the women whose education level is lower than secondary school.
+Over 50% of the women with no education take care of their own children whereas less than 40% of the women with secondary or higher levels of education do.
+As the level of education gets higher, then the percentage of schooling their children gets higher as well.
+Moreover, it is worthwhile to mention that the women who completed high school are more likely to stop working after having a birth compared to the women whose education level is lower than secondary school.
 
@@
 
-Figure \@ref(fig:occupationchildcare) illustrates that the percentage of the child's caretaker is highest in the respondent followed by the relative and schooling regardless of what type of jobs they have.
-This means that it is mostly the case that the employed women taking care of their children under six while they are working.
-Meanwhile, women who work in the agricultural sector are more likely to care for a child themselves than women in non-agricultural occupations.
+Figure \@ref(fig:occupationchildcare) illustrates that the percentage of the child's caretaker is highest among the respondent followed by the relative and schooling regardless of what type of jobs they have.
+This means that it is mostly the case that the employed women take care of their children under six while they are working.
+Meanwhile, women who work in the agricultural sector are more likely to care for a child themselves than women in the non-agricultural occupations.
 In particular, more than a half of the employed women working in the agricultural industry are the caretaker of the child under six whereas around 45% of the women working in non-agricultural sector take care of a child themselves while working.
@@
 
-Figure \@ref(fig:employmentstatus) illustrates that majority of the employed women work throughout the entire year.
-Specifically, majority of them work full week.
+Figure \@ref(fig:employmentstatus) illustrates that the majority of the employed women work throughout the entire year.
+Specifically, the majority of them work full week.
 There are few women who work occasionally.
-On top of that, regardless of what their employment status is, more working mothers tend to have one or more child under six.
+On top of that, regardless of their employment status, more working mothers tend to have one or more children under six.
 
@@
 
-We can see from Figure \@ref(fig:employmentstatuschildcare) that the percentage of the respondent being the primary caretaker of the child under six is remarkably higher than the others in all four employment status.
+We can see from Figure \@ref(fig:employmentstatuschildcare) that the percentage of the respondent being the primary caretaker of a child under six is remarkably higher than the others in all four employment statuses.
 It exceeds 40% in all four cases, and in particular, mothers working full time are more likely to look after their own children than the others.
 Next, it is the relatives who mainly take care of the child under six.
-It should be noted that there are more women sending their kids under six to school when they work all year compare to the ones who do not work throughout the entire year.
+It should be noted that there are more women sending their kids under six to school when they work all year compared to the ones who do not work throughout the entire year.
+
+\newpage
 
@@
 
-We can tell from Table \@ref(tab:data) that 3,564 out of 4,843 women of age 15-49 who completed the survey are employed.
-In other word, around three in four women were employed during the 12 months before the survey.
-Figure \@ref(fig:residence) shows that the number of employed women is greater in rural area.
-It is worth mentioning that even though rural areas typically have low population density, rural women are somewhat more likely than urban women to be currently working.
+Table \@ref(tab:data) illustrates that 3,564 out of 4,843 women of age 15-49 who completed the survey are employed.
+In other words, around three in four women were employed during the 12 months before the survey.
+Figure \@ref(fig:residence) shows that there are more employed women in the rural area, and this is because Ghana's population is predominantly rural.
+34% of the country's population was reported to be residing in urban areas, and 66% percent were living in rural areas [@ghana1998].
+
 Next, Figure \@ref(fig:region) illustrates that women residing in the Upper West Region are least likely to be employed.
-Together with Figure \@ref(fig:map), we can tell that the women are more likely to be employed when they live in the southern part of Ghana.
+Together with Figure \@ref(fig:map), we can tell that women are more likely to be employed when they live in the southern part of Ghana.
 The northern part of Ghana including Upper West, Upper East, and Northern Region are the bottom 3 regions in Figure \@ref(fig:region) which demonstrates the distribution of the number of employed women whereas the southern part of Ghana including Greater Accra, Ashanti, and Eastern Region are the top 3.
 
-Additionally, it is surprising to see from Figure \@ref(fig:motheredu) that the number of employed women whose education level is secondary school or higher is remarkably lower than that of the other education levels.
+Additionally, it is surprising to see from Figure \@ref(fig:motheredu) that the number of employed women whose education level is a secondary school or higher is remarkably lower than that of the other education levels.
 Meanwhile, Figure \@ref(fig:occupation) shows that women are approximately twice as likely to be employed in the non-agricultural sector than in the agricultural sector.
@@
 
-Table \@ref(tab:data) shows that more than a half of the employed women has a child under six years.
-Figure \@ref(fig:childstatus) demonstrates that working women in rural area are more likely to have at least one child under six years whereas working women in urban area tend to have no child under six years.
+Table \@ref(tab:data) shows that more than a half of the employed women have a child under six years.
+Figure \@ref(fig:childstatus) demonstrates that working women in rural areas are more likely to have at least one child under six years whereas working women in urban areas tend to have no child under six years.
 Figure \@ref(fig:motheredu) shows that as the level of working mother’s education gets higher, it is more likely to not have any child under six.
@@
 Every figure that demonstrates the distribution of the child's caretaker shows that it is most likely to be the mother primarily taking care of their child under six while they are at work.
-In other words, no matter where they live, what their education level is, and what type of a job they have, majority of the employed women is the look after their child.
+In other words, no matter where they live, what their education level is, and what type of job they have, the majority of the employed women are the ones who look after their children.
 Therefore, we can deduce that in Ghana it was common that the mother is primarily responsible for the care and raising of a child back in 1998.
+In 2002, UNICEF conducted a survey from 31 countries, and it asked working women with children under the age of 6 years about the typical childcare arrangement while they are working [@unicef].
+It was reported that 39% of the respondents took care of their children themselves on average, while in poor countries, the percentage rose up to 44% [@unicef].
+Thus, we can tell that the notably high percentage of working mothers looking after the children themselves indicates that Ghana was a low-income country.
 
-Besides the mother being the primary caregiver of a child under six, it can be observed from Figure \@ref(fig:mothereduchildcare), Figure \@ref(fig:workstatuschildcare), Figure \@ref(fig:occupationchildcare), Figure \@ref(fig:employmentstatuschildcare) that the relatives other than husband/partner are likely to look after children under six.
-Also, there are some family where the older siblings take care of their siblings under six.
+Besides the mother being the primary caregiver of a child under six, it can be observed in Figure \@ref(fig:mothereduchildcare), Figure \@ref(fig:workstatuschildcare), Figure \@ref(fig:occupationchildcare), Figure \@ref(fig:employmentstatuschildcare) that the relatives other than husband/partner are likely to look after children under six.
+Also, there are some families where the older siblings take care of their siblings under six.
 Thus, we can tell that if there is a child under six in the family, then it was usual for the family member to take care of them in Ghana, 1998.
 
-In addition, we can observe that it was uncommon to hire a person to take care of the child under six.
+In addition, we can observe that the proportion of households hiring people to look after their kids is very low.
+This is presumably because of poverty, which is discussed above.
 Instead of hiring a person, there are more cases reported that they sent the kids to school or to institutional care.
-Figure \@ref(fig:areachildcare) demonstrates that the percentage of the employed women sending their kids to school is higher in urban areas than in rural areas.
+Figure \@ref(fig:areachildcare) demonstrates that the percentage of employed women sending their kids to school is higher in urban areas than in rural areas.
 Figure \@ref(fig:mothereduchildcare) shows that the number of working mothers sending their kids to school increases as their mother's education level gets higher.
-Figure \@ref(fig:workstatuschildcare) illustrates that it is more likely to have their kids in school when they work for someone else than when they work for the family member or when they are self-employed.
-Figure \@ref(fig:occupationchildcare) shows that the percentage of the employed women sending their kids to school is higher in non-agricultural sectors than in agricultural sectors.
-Lastly, we can see from Figure \@ref(fig:employmentstatuschildcare) that there are more women sending their kids to school when they work all year compare to the ones who work seasonally and occasionally.
+Figure \@ref(fig:workstatuschildcare) illustrates that it is more likely to have their kids in school when they work for someone else than when they work for a family member or when they are self-employed.
+Figure \@ref(fig:occupationchildcare) shows that the percentage of employed women sending their kids to school is higher in non-agricultural sectors than in agricultural sectors.
+Lastly, we can see from Figure \@ref(fig:employmentstatuschildcare) that there are more women sending their kids to school when they work all year compared to the ones who work seasonally and occasionally.
 
-Lastly, we can tell that it is rarely the case that the mother stops working after having a birth.
-However, it is worth noting that the percentage of the employed women stop working after the birth is higher in urban areas than in rural areas from Figure \@ref(fig:areachildcare).
-In addition, Figure \@ref(fig:mothereduchildcare) shows that the women who completed high school have more tendency to stop working after having a birth than the ones with a lower education level.
-Furthermore, Figure \@ref(fig:employmentstatuschildcare) shows that the percentage of the employed women stop working after the birth is highest when they work all year, full week.
+Lastly, we can tell that it is rarely the case that the mother stops working after having birth.
+However, it is worth noting that the percentage of employed women who stop working after birth is higher in urban areas than in rural areas from Figure \@ref(fig:areachildcare).
+In addition, Figure \@ref(fig:mothereduchildcare) shows that the women who completed high school have more tendency to stop working after having birth than the ones with a lower education level.
+Furthermore, Figure \@ref(fig:employmentstatuschildcare) shows that the percentage of employed women who stop working after birth is highest when they work all year, full week.
 
@@
 4,843 women of age 15-49 completed the survey, and 3,564 of them responded that they are employed.
-Then, they were further asked whether they have a child under six.
-However, it is not mentioned whether their marital status was asked.
-If the question was asked to every women who participated the survey, then the respondents who answered to have no child under six might be single.
-This dataset is created to identify woman's overall status, and the percentage of the employed mothers not having a child is one of the important indicators.
-However, as it is unclear which group that not having a child under six refers to, it is hard to tell what factor this survey focuses on.
+Then, they were further asked to indicate whether they have a child under six.
+However, it is not mentioned whether their marital status was asked prior to this question.
+If the question was asked to every woman who participated in the survey, then the respondents who answered that they have no child under six might be single.
+This dataset is created to identify a woman's overall status, and the percentages of the employed women by their marital status and the presence of a child are considered important indicators.
+However, it is unclear what they are trying to say by grouping women only by the presence of a child under six years.
 
 Additionally, it would have been better if they were first asked for their marital status and the presence of dependent children.
-They could have then asked the age of youngest child in the household or whether they have a child under six in the household.
+They could have then asked the age of the youngest child in the household or whether they have a child under six in the household.
 As married life has been reported to have a gendered effect on women and men's labour market outcomes [@maritalstatus], the distribution of the marital status among the employed women would be useful to tell the woman's overall status.
-In this context, if the respondent answered that they stopped working since the last birth, they could have further asked the reason for stopping working and about the job that they used to have before having a birth.
+In this context, if the respondent answered that they stopped working after the last birth, they could have further asked the reason for stopping working and about the job that they used to have before having birth.
 
 Lastly, only the employed women who have a child under six were further asked to indicate who takes care of their children while they are at work.
-The dataset included the percentage of the missing values, and we purposely excluded in plotting the graphs as they do not tell anything about the data itself and there were only few missing values.
-However, when we add up the percentage of all possible items including the missing values, there are several background characteristics where the numbers did not add up to a 100.
+The dataset included the percentage of the missing values, and we purposely excluded them in plotting the graphs as they do not tell anything about the data itself and there were only a few missing values.
+However, when we add up the percentage of all possible items including the missing values, there are several background characteristics where the numbers did not add up to 100.
 As only the percentage is provided in the report, there might be a round-off error.
-Particularly, since the numbers were rounded to one-decimal place, there is a high possibility that there was a rounding error.
-To make the dataset more precise, they could have rounded to two-decimal places.
+Particularly, since the numbers were rounded to one decimal place, there is a high possibility that there was a rounding error.
+To make the dataset more precise, they could have rounded to two decimal places.
 
-On top of that, the survey asked for the employment situation during the 12-month reference period preceding the survey.
+On top of that, the survey asked about the employment situation during the 12-month reference period preceding the survey.
 However, the respondents were allowed to answer using their previous experiences.
-In particular, this applies to the respondents who had a job before having a birth but stopped working since the birth.
+In particular, this applies to the respondents who had a job before having birth but stopped working after the last birth.
 Since we do not know the age of the youngest child in their household, they might have answered the questionnaire based on their employment situation prior to the 12-month reference period.

### 2022-04-03 outputs/paper.Rmd

@@
 It was designed to collect data on fertility, family planning, and maternal and child health.
+The 1998 GDHS was conducted from mid-November 1998 to mid-February 1999.
 
 The survey frame was created using the list of Enumeration Areas (EAs) with population and household information from the 1984 Population Census.
-The 1998 GDHS used a two-stage stratified sampling.
+The 1998 GDHS used a two-stage stratified sampling method.
 At the first stage of sampling, 400 EAs were selected using systematic sampling with probability proportional to size where the selected EAs comprised 138 in the urban areas and 262 in the rural areas.
@@
 At the second stage of sampling, a systematic sample of 20 households per EA was selected in the Northern, Upper West and Upper East Regions, and 15 households per EA was selected in the other regions.
+
+The target sample size for the 1998 GDHS was 6,000 consisted of 4,500 women of age 15-49 and men of age 15-59.
+A total of 4,843 women age 15-49 and 1,546 men age 15-59 completed the survey.
+To account for non-response, 6375 households were selected for interview.
+
+The GDHS was composed of 3 parts: the Household's questionnaire, the Woman's questionnaire and the Man's questionnaire. All the questionnaires were modified to account for the situation in Ghana.
+
+The survey was conducted in person.
+The interview staff were first trained for a period of three weeks.
+It was conducted by a total of 14 teams, comprising a team supervisor, a field editor, three interviewers and a driver.
+The response rate was 97% for individual men and women selected.
+Non-response was mainly due to inability to find the selected interviewee at home.
+Repeated callbacks were made to try to reach the selected respondents.
+The results of the survey did not disclose any confidential information that might identify the respondents.
+The survey was a voluntary one but it is unclear if the purpose of the survey explained to the respondents for them to make an informed decision.
 

### 2022-04-03 inputs/data/datasheet.Rmd
renaming the datasheet files

--- 2022-03-27 inputs/data/datasheet_template.Rmd
@@
 ---
-title: "My title"
-subtitle: "My subtitle if needed"
+title: "Datasheet for the child care of working mothers dataset"
+subtitle: ""
 author: 
@@
   - Yunkyung Park
-thanks: "Code and data are available at: LINK."
+thanks: "Code and data are available at: https://github.com/Pascal-304/dhs_analysis."
 date: "`r format(Sys.time(), '%d %B %Y')`"
-abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
+abstract: "The datasheet serves the purpose of documenting the creation of a dataset.
+It has two main objectives, one for data creators and the other for data consumers.
+For data creators, it allows the reflection on the data gathering and cleaning process.
+While for data consumers, it provides an understanding of how the dataset was created.
+The key idea behind it would be transparency and accountability."
 output:
@@
 
-Extract of the questions from @gebru2021datasheets
+The questions were extracted from @gebru2021datasheets
 
@@
 1. *For what purpose was the dataset created? Was there a specific task in mind? Was there a specific gap that needed to be filled? Please provide a description.*
-    - The dataset was created to enable analysis of Australian politicians.
-We were unable to find a publicly available dataset in a structured format that had the biographical and political information on Australian politicians that was needed for modelling.
+    - The dataset was created to enable a descriptive analysis of the child care situation of working mothers in Ghana.
+The dataset would be used to look at the trends concerning child caretaking across different factors such as region, work status or occupation area.
+We were unable to find a publicly available dataset.
 2. *Who created the dataset (for example, which team, research group) and on behalf of which entity (for example, company, institution, organization)?*
-    - TBD
+    - The dataset was created by Yunkyung Park and Pascal Lee Slew from the University of Toronto.
 3. *Who funded the creation of the dataset? If there is an associated grant, please provide the name of the grantor and the grant name and number.*
-    - TBD
+    - No funding was obtained/required for the creation of the dataset.
 4. *Any other comments?*
-    - TBD
+    -  None.
 
@@
 Please provide a description.*
-	- TBD
+	- The dataset consists of categories: residence (urban or rural), regions of Ghana, mothers' education level, work status, occupation and employment status.
+For each category, we have different features: child status (whether families have children under six years old), childcare preferences and the number of employed women.
 2. *How many instances are there in total (of each type, if appropriate)?*
-	- TBD
+	- There are 26 rows and 17 columns in the dataset.
+The residence category has 2 rows,  regions has 10 rows, mothers' education level has 4 rows, work status has 3 rows, occupation has 2 rows and employment status has 4 rows.
 3.
@@
 If it is not representative of the larger set, please describe why not (for example, to cover a more diverse range of instances, because instances were withheld or unavailable).*
-	- TBD
+	- The dataset contains all the data possible.
 4. *What data does each instance consist of? "Raw" data (for example, unprocessed text or images) or features? In either case, please provide a description.*
-	- TBD
+	- Each category consists of already processed data. The observations are mostly percentages which represent the proportions of categories. 
 5. *Is there a label or target associated with each instance? If so, please provide a description.*
-	- TBD
+	- No
 6.
@@
 This does not include intentionally removed information, but might include, for example, redacted text.*
-	- TBD
+	- Yes, some participants did not respond to all survey questions, leading to some missing data in the data collection process.
 7. *Are relationships between individual instances made explicit (for example, users' movie ratings, social network links)? If so, please describe how these relationships are made explicit.*
-	- TBD
+	- No
 8. *Are there recommended data splits (for example, training, development/validation, testing)? If so, please provide a description of these splits, explaining the rationale behind them.*
-	- TBD
+	- No
 9. *Are there any errors, sources of noise, or redundancies in the dataset? If so, please provide a description.*
-	- TBD
+	- There may be possible sampling error.
 10.
@@
 Please provide descriptions of all external resources and any restrictions associated with them, as well as links or other access points, as appropriate.*
-	- TBD
+	- The dataset was extracted from a publicly available pdf at https://dhsprogram.com/publications/publication-FR106-DHS-Final-Reports.cfm
 11.
@@
 If so, please provide a description.*
-	- TBD
+	- No, the results of the survey used to create the dataset were made confidential so that we are unable to identify the participants.
 12. *Does the dataset contain data that, if viewed directly, might be offensive, insulting, threatening, or might otherwise cause anxiety? If so, please describe why.*
-	- TBD
+	- None
 13.
@@
 If so, please describe how these subpopulations are identified and provide a description of their respective distributions within the dataset.*
-	- TBD
+	- Yes, the population would be the working mothers.
+Sub-populations would be identified by the categories mentionned above such as employment status, occupation, mothers' education, region, residence and work status.
 14.
@@
 If so, please describe how.*
-	- TBD
+	- No
 15.
@@
 If so, please provide a description.*
-	- TBD
+	- No
 16. *Any other comments?*
-	- TBD
+	- None
 
@@
 If so, please describe how.*
-	- TBD
+	- No, the data are percentages of categories based on results from the 1998 Ghana Demographic and Health Survey responses.
 2.
@@
 How were these mechanisms or procedures validated?*
-	- TBD
+	- The data was collected by extracting data from a pdf.
+In our case, we extracted data from a table located at page 45 in the 1998 Ghana Demographic and Health Survey pdf available at the link: https://dhsprogram.com/publications/publication-FR106-DHS-Final-Reports.cfm
+	- The data collection was done using R [@citeR] and R packages tidyverse [@citetidyverse], pdftools [@citepdftools] and stringi [@citestringi].
+	- We used the R package pointblank [@pointblank] to set up tests and check on our dataset.
 3. *If the dataset is a sample from a larger set, what was the sampling strategy (for example, deterministic, probabilistic with specific sampling probabilities)?*
-	- TBD
+	- No
 4. *Who was involved in the data collection process (for example, students, crowdworkers, contractors) and how were they compensated (for example, how much were crowdworkers paid)?*
-	- TBD
+	- The raw survey data was collected by teams consisting of a team supervisor, a field editor, three interviewers and a driver. They were trained for 3 weeks. No mention of compensation was made.
 5.
@@
 If not, please describe the timeframe in which the data associated with the instances was created.*
-	- TBD
+	- The raw GDHS data was collected from mid-November 1998 to mid-February 1999.
 6.
@@
 If so, please provide a description of these review processes, including the outcomes, as well as a link or other access point to any supporting documentation.*
-	- TBD
+	- The GDHS procedures and survey questionnaires were reviewed by the ICF Institutional Review Board (IRB) of Ghana.
 7. *Did you collect the data from the individuals in question directly, or obtain it via third parties or other sources (for example, websites)?*
-	- TBD
+	- The GDHS raw data was collected from individuals directly while the dataset created was created from a publicly available pdf on the DHS website.
 8.
@@
 If so, please describe (or show with screenshots or other information) how notice was provided, and provide a link or other access point to, or otherwise reproduce, the exact language of the notification itself.*
-	- TBD
+	- Yes, the individuals in questions were informed since data collection of the GDHS survey was in person.
+However, for the "raw" data from the pdf, it did not involve individuals directly since their responses were already processed together.
 9.
@@
 If so, please describe (or show with screenshots or other information) how consent was requested and provided, and provide a link or other access point to, or otherwise reproduce, the exact language to which the individuals consented.*
-	- TBD
+	- For the GDHS survey, the participants consented to the collection and use of their data.
+Their data would be made anonymous and public but they were not explicitly informed that it would be used in this way.
 10.
@@
 If so, please provide a description, as well as a link or other access point to the mechanism (if appropriate).*
-	- TBD
+	- N/A
 11.
@@
 If so, please provide a description of this analysis, including the outcomes, as well as a link or other access point to any supporting documentation.*
-	- TBD
+	- N/A
 12. *Any other comments?*
-	- TBD
+	- None
 
@@
 If not, you may skip the remaining questions in this section.*
-	- TBD
+	- Yes. The "raw" data obtained from the pdf was cleaned using the tidyverse r package [@citetidyverse] in R [@citeR].
 2.
@@
 If so, please provide a link or other access point to the "raw" data.*
-	- TBD
+	- Yes, both the clean and "raw" data are saved and available at the link:
+	https://github.com/Pascal-304/dhs_analysis/tree/main/outputs/data
 3. *Is the software that was used to preprocess/clean/label the data available? If so, please provide a link or other access point.*
-	- TBD
+	- We used the statistical software R [@citeR].
 4. *Any other comments?*
-	- TBD
+	- None
 
@@
 1. *Has the dataset been used for any tasks already? If so, please provide a description.*
-	- TBD
+	- The dataset has been used to conduct a descriptive analysis of the child care situation of working mothers in Ghana. We used the dataset to create graphs.
 2. *Is there a repository that links to any or all papers or systems that use the dataset? If so, please provide a link or other access point.*
-	- TBD
+	- The repository containing all the files pertaining to the dataset is available at https://github.com/Pascal-304/dhs_analysis
 3. *What (other) tasks could the dataset be used for?*
-	- TBD
-4.
-*Is there anything about the composition of the dataset or the way it was collected and preprocessed/cleaned/labeled that might impact future uses?
+	- None since the dataset pertained to the childcare situation of working mothers in Ghana only at one time point(1998), so it cannot be used to generalize in other countries or other time points.
+4.	*Is there anything about the composition of the dataset or the way it was collected and preprocessed/cleaned/labeled that might impact future uses?
 For example, is there anything that a dataset consumer might need to know to avoid uses that could result in unfair treatment of individuals or groups (for example, stereotyping, quality of service issues) or other risks or harms (for example, legal risks, financial harms)?
@@
 Is there anything a dataset consumer could do to mitigate these risks or harms?*
-	- TBD
+	- N/A
 5. *Are there tasks for which the dataset should not be used? If so, please provide a description.*
-	- TBD
+	- N/A
 6. *Any other comments?*
-	- TBD
+	- None
 
@@
 If so, please provide a description.*
-	- TBD
+	- Yes, the dataset is publicly available on the internet.
 2. *How will the dataset be distributed (for example, tarball on website, API, GitHub)? Does the dataset have a digital object identifier (DOI)?*
-	- TBD
-3. *When will the dataset be distributed?*
-	- TBD
+	- The dataset can be obtained by running the r script "01-gather_data.R" available at the link: https://github.com/Pascal-304/dhs_analysis/blob/main/scripts/01-gather_data.R
+
 4.
@@
 If so, please describe this license and/ or ToU, and provide a link or other access point to, or otherwise reproduce, any relevant licensing terms or ToU, as well as any fees associated with these restrictions.*
-	- TBD
+	- No
 5.
@@
 If so, please describe these restrictions, and provide a link or other access point to, or otherwise reproduce, any relevant licensing terms, as well as any fees associated with these restrictions.*
-	- TBD
+	- Unknown to the authors of the dataset
 6.
@@
 If so, please describe these restrictions, and provide a link or other access point to, or otherwise reproduce, any supporting documentation.*
-	- TBD
-7. *Any other comments?*
-	- TBD
+	- Unknown to the authors of the dataset
 
@@
 1. *Who will be supporting/hosting/maintaining the dataset?*
-	- TBD
+	- Yunkyung Park and Pascal Lee Slew
 2. *How can the owner/curator/manager of the dataset be contacted (for example, email address)?*
-	- TBD
+	- If anyone want to reach out to us about the dataset, you can contact us at clara.park@mail.utoronto.ca or pascal.leeslew@mail.utoronto.ca
 3. *Is there an erratum? If so, please provide a link or other access point.*
-	- TBD
+	- No
 4.
@@
 If so, please describe how often, by whom, and how updates will be communicated to dataset consumers (for example, mailing list, GitHub)?*
-	- TBD
+	- If there is any error made in the creation of the dataset, the dataset will be updated by either Yunkyung Park or Pascal Lee Slew.
+Any updates will be communicated as a note in the Readme file at the link below: https://github.com/Pascal-304/dhs_analysis/blob/main/README.md
 5.
@@
 If so, please describe these limits and explain how they will be enforced.*
-	- TBD
+	- N/A
 6. *Will older versions of the dataset continue to be supported/hosted/maintained? If so, please describe how. If not, please describe how its obsolescence will be communicated to dataset consumers.*
-	- TBD
+	- The dataset has just been created. If there are any updates, older versions will still be kept for consistency.
 7.
@@
 If so, please provide a description.*
-	- TBD
+	- Others may do so and should contact the original authors about incorporating fixes/extensions.
+
 8. *Any other comments?*
-	- TBD
+  - None
 

### 2022-04-03 inputs/data/datasheet_template.Rmd
Fix cross-reference issues

@@
 ---
-title: "My title"
-subtitle: "My subtitle if needed"
+title: "Datasheet"
 author: 

### 2022-04-03 outputs/paper.Rmd
small changes
Fix cross-reference issues

@@
 ---
-title: "Childcare while their mom is working"
+title: "Child care situation of working mothers in Ghana 1998"
 author: 
@@
 Section \@ref(results) relays the findings through graphs.
-Section @\ref(discussion) discusses in more detail what was found and some limitations of what we did and Section \@ref(appendix) contains a datasheet for the dataset we used.
+Section \@ref(discussion) discusses in more detail what was found and some limitations of what we did and Section \@ref(appendix) contains a datasheet for the dataset we used.
 
@@
 
-Figure @\ref(fig:region) shows the number of employed mothers in the different administrative regions.
+Figure \@ref(fig:region) shows the number of employed mothers in the different administrative regions.
 There were more working mothers in Greater Accra and Ashanti while Upper West had the least number of working mothers.
@@
 
-Figure @\ref(fig:areachildcare) shows the Ghanese families' caretaking preferences in both urban and rural areas.
+Figure \@ref(fig:areachildcare) shows the Ghanese families' caretaking preferences in both urban and rural areas.
 The preferred caretaking method in both urban and rural areas is the working mothers looking after their children by themselves.
@@
 
+# Appendix
+
+\newpage
+
 # References

### 2022-04-03 inputs/data/datasheet.Rmd
Update figure labels

@@
 title: "Datasheet for the child care of working mothers dataset"
-subtitle: ""
 author: 
@@
 1. *Who will be supporting/hosting/maintaining the dataset?*
-	- Yunkyung Park and Pascal Lee Slew
+	- Pascal Lee Slew and Yunkyung Park
 2. *How can the owner/curator/manager of the dataset be contacted (for example, email address)?*
-	- If anyone want to reach out to us about the dataset, you can contact us at clara.park@mail.utoronto.ca or pascal.leeslew@mail.utoronto.ca
+	- If anyone want to reach out to us about the dataset, you can contact us at pascal.leeslew@mail.utoronto.ca or clara.park@mail.utoronto.ca
 3. *Is there an erratum? If so, please provide a link or other access point.*

### 2022-04-03 outputs/paper.Rmd
Update figure labels

@@
 The results of the survey did not disclose any confidential information that might identify the respondents.
-The survey was a voluntary one but it is unclear if the purpose of the survey explained to the respondents for them to make an informed decision.
+The survey was a voluntary one and participants were informed first.
 
@@
 
-```{r generalchildcare, echo=FALSE, fig.cap="Distribution of the caretaker of the child when the mother is working", fig.width=6, fig.height=4}
+```{r generalchildcare, echo=FALSE, fig.cap="Distribution of the caretaker of the child while mother is working", fig.width=6, fig.height=4}
 totl <-
@@
   totl %>%
-  select(-c(character, total)) %>%
+  select(-c(character, total, caretaker_missing)) %>%
   pivot_longer(!background, names_to = "variable", values_to = "count")
@@
                                   'not_worked_since_birth',
-                                  'other',
-                                  'missing')
+                                  'other')
     )
@@
   theme_minimal() +
-  labs(x='') +
+  labs(x='Percentage', y='Caretaker while at work') +
   theme(legend.position='none') +
@@
         "not_worked_since_birth" = "not worked since birth",
-        "other" = "other",
-        "missing" = "missing")
+        "other" = "other")
   )
@@
 
-```{r residence, echo=FALSE, fig.cap="Comparison of the number of working mothers between urban and rural areas"}
+```{r residence, echo=FALSE, fig.cap="Comparison of the number of working mothers between urban and rural areas", fig.width=6, fig.height=4}
 # Urban vs Rural
@@
   geom_bar(stat = 'identity', fill = "burlywood") +
+  geom_text(aes(label=number_of_employed_women),
+            size = 4,
+            position=position_stack(vjust = 0.6)) +
   labs(x = "Area",
@@
 Figure \@ref(fig:residence) shows the number of employed mothers in urban and rural areas.
-There are 1127 women who were selected in Urban areas while 2338 mothers were selected in rural areas.
+There are 1,227 women who were selected in Urban areas while 2,338 mothers were selected in rural areas.
 There are less women living in urban who are currently working, and this is not surprising as a larger population live in rural areas.
 
-```{r region, echo=FALSE, fig.cap = "Comparison of the number of working mothers selected in the different administrative regions"}
+```{r region, echo=FALSE, fig.cap = "Comparison of the number of working mothers selected in the different administrative regions", fig.height=5, fig.width=6}
 # region subdataset
@@
   filter(character == "Region") %>% 
+  mutate(background = factor(background,
+                             levels = c('Western',
+                                        'Central',
+                                        'Greater_Accra',
+                                        'Volta',
+                                        'Eastern',
+                                        'Ashanti',
+                                        'Brong_Ahafo',
+                                        'Northern',
+                                        'Upper_West',
+                                        'Upper_East')
+  )
+  ) %>%
   mutate(background = recode(background,
@@
 
-```{r childstatus, echo = FALSE, fig.cap = "Comparing the percentage of mothers having no child under six to one or more in both Urban and Rural areas"}
+```{r childstatus, echo = FALSE, fig.cap = "Comparing the percentage of mothers having no child under six to one or more in both Urban and Rural areas", fig.width=6, fig.height=4}
 # make dataset in long format
@@
   labs(x = "Area",
-       y = "Percent",
-       fill = "Child status") +
+       y = "Percentage",
+       fill = "Child under six") +
   theme_minimal() +
@@
   theme(legend.position = "bottom")
-
 ```
@@
 
-```{r areachildcare, echo=FALSE, fig.cap = "Comparing child caretaker preferences in Urban and Rural areas"}
+```{r areachildcare, echo=FALSE, fig.cap = "Comparing child caretaker preferences in Urban and Rural areas", fig.width=6, fig.height=4}
 # caretaker aspect
@@
   pivot_longer(!background, names_to = "caretakers", values_to = "percentage") %>%
+  mutate(
+    caretakers = factor(caretakers,
+                        levels = c('caretaker_respondent',
+                                   'caretaker_partner',
+                                   'caretaker_other_relative',
+                                   'caretaker_neighbor',
+                                   'caretaker_hired',
+                                   'caretaker_child_in_school',
+                                   'caretaker_other_female_child',
+                                   'caretaker_other_male_child',
+                                   'caretaker_not_worked_since_birth',
+                                   'caretaker_other')
+    )
+    ) %>%
   mutate(caretakers = recode(caretakers,
@@
                              'caretaker_not_worked_since_birth' = 'not worked since birth',
-                             'caretaker_neighbor' = 'neighbour',
-                             'caretaker_missing' = 'missing',
+                             'caretaker_neighbor' = 'neighbor',
                              'caretaker_hired' = 'hired help',
@@
            position = "dodge") +
-  labs(x = "Caretaker",
-       y = "Percentage of working mothers",
+  labs(x = "Caretaker while at work",
+       y = "Percentage",
        fill = "Area") +
@@
 
-```{r caretakingregions, echo = FALSE, fig.cap = "Caretaking behaviour in the different administrative regions", fig.width=7, fig.height=7}
+```{r caretakingregions, echo = FALSE, fig.cap = "Caretaking behaviour in the different administrative regions", fig.width=8, fig.height=7}
 # make dataset into long format
@@
   select(-c(character, total, caretaker_missing)) %>% 
-  pivot_longer(!background, names_to = "x", values_to = "percentage") %>% 
-  mutate(x = recode(x,
+  pivot_longer(!background, names_to = "variable", values_to = "percentage") %>% 
+  mutate(
+    variable = factor(variable, 
+                      levels = c('caretaker_respondent',
+                                 'caretaker_partner',
+                                 'caretaker_other_relative',
+                                 'caretaker_neighbor',
+                                 'caretaker_hired',
+                                 'caretaker_child_in_school',
+                                 'caretaker_other_female_child',
+                                 'caretaker_other_male_child',
+                                 'caretaker_not_worked_since_birth',
+                                 'caretaker_other')
+    )
+  ) %>%
+  mutate(variable = recode(variable,
                            'caretaker_respondent' = 'respondent',
@@
                            'caretaker_not_worked_since_birth' = 'not worked since birth',
-                    'caretaker_neighbor' = 'neighbour',
-                    'caretaker_missing' = 'missing',
+                           'caretaker_neighbor' = 'neighbor',
                            'caretaker_hired' = 'hired help',
@@
 child %>% 
-  filter(x != 'number of employed women', x != 'no child under six', x!= 'one or more child under six') %>% 
-  ggplot(aes(x = x,
+  filter(variable != 'number of employed women', variable != 'no child under six', variable != 'one or more child under six') %>% 
+  ggplot(aes(x = variable,
              y = percentage,
@@
   geom_bar(stat = 'identity') + 
-  labs(x = "caretaking preference",
-       y = "percent") +
+  labs(x = "Caretaker while at work",
+       y = "Percentage") +
   theme_minimal() +
@@
   theme(legend.position = "none")
-
 ```
@@
 child %>% 
-  filter(x == "no child under six" | x == "one or more child under six") %>% 
+  filter(variable == "no child under six" | variable == "one or more child under six") %>% 
   ggplot(aes(x = background,
              y = percentage,
-             fill = x)) +
+             fill = variable)) +
   geom_bar(stat = 'identity', position = "dodge", width = 0.8) +
-  labs(x = "child status",
-       y = "percentage",
-       fill = "child status") +
+  labs(x = "Administrative regions",
+       y = "Percentage",
+       fill = "Child under six") +
   theme_minimal() +
@@
   coord_flip() 
-
 ```
@@
   mother_edu %>%
-  select(-c(character, total)) %>%
+  select(-c(character, total, caretaker_missing)) %>%
   pivot_longer(!background, names_to = "variable", values_to = "count") %>%
@@
   theme_minimal() +
-  labs(x='Caretaker while at work', y="Percentage (in %)") +
+  labs(x='Caretaker while at work', y="Percentage") +
   theme(legend.position='none') +
@@
         "not_worked_since_birth" = "not worked since birth",
-        "other" = "other",
-        "missing" = "missing")
+        "other" = "other")
   ) +
@@
   work_status %>%
-  select(-c(character, total)) %>%
+  select(-c(character, total, caretaker_missing)) %>%
   pivot_longer(!background, names_to = "variable", values_to = "count") %>%
@@
   theme_minimal() +
-  labs(x='Caretaker while at work', y="Percent") +
+  labs(x='Caretaker while at work', y="Percentage") +
   theme(legend.position='none') +
@@
   occupation %>%
-  select(-c(character, total)) %>%
+  select(-c(character, total, caretaker_missing)) %>%
   pivot_longer(!background, names_to = "variable", values_to = "count") %>%
@@
                                   'not_worked_since_birth',
-                                  'other',
-                                  'missing'))
+                                  'other'))
   )
@@
   geom_bar(stat = "identity", position="dodge") + 
-  labs(x='Caretaker while at work', y="Percent", fill="Occupation") +
+  labs(x='Caretaker while at work', y="Percentage", fill="Occupation") +
   theme_minimal() +
@@
   employment_status %>%
-  select(-c(character, total)) %>%
+  select(-c(character, total, caretaker_missing)) %>%
   pivot_longer(!background, names_to = "variable", values_to = "count") %>%
@@
 
+```{r}
+library(pointblank)
+
+agent <-
+  create_agent(tbl = column_names_as_contracts) %>%
+  col_is_character(columns = vars(chr_area, chr_group_gender)) %>%
+  col_is_factor(columns = vars(fctr_group_age)) %>%
+  col_is_integer(columns = vars(int_group_count)) %>%
+  col_vals_in_set(columns = chr_group_gender,
+                  set = c("male", "female", "total")) %>%
+  interrogate()
+
+agent
+
+```
+
 # Discussion

### 2022-04-03 outputs/paper.Rmd
Exclude pointblank tests

@@
 
-```{r}
-library(pointblank)
-
-agent <-
-  create_agent(tbl = column_names_as_contracts) %>%
-  col_is_character(columns = vars(chr_area, chr_group_gender)) %>%
-  col_is_factor(columns = vars(fctr_group_age)) %>%
-  col_is_integer(columns = vars(int_group_count)) %>%
-  col_vals_in_set(columns = chr_group_gender,
-                  set = c("male", "female", "total")) %>%
-  interrogate()
-
-agent
-
-```
-
 # Discussion

### 2022-04-03 outputs/paper.Rmd
Fix errors

@@
 The survey was a voluntary one and participants were informed first.
-
-The target sample size for the 1998 GDHS was 6,000 consisted of 4,500 women of age 15-49 and men of age 15-59.
-A total of 4,843 women age 15-49 and 1,546 men age 15-59 completed the survey.
-To account for non-response, 6375 households were selected for interview.
-
-This was a part of the worldwide Demographic and Health Surveys (DHS) programme, and the GDHS was composed of 3 parts: the Household's questionnaire, the Woman's questionnaire and the Man's questionnaire.
-All the questionnaires were modified to account for the situation in Ghana.
-
-The survey was conducted in person.
-The interview staff were first trained for a period of three weeks.
-It was conducted by a total of 14 teams, comprising a team supervisor, a field editor, three interviewers and a driver.
-The response rate was 97% for individual men and women selected.
-Non-response was mainly due to inability to find the selected interviewee at home.
-Repeated callbacks were made to try to reach the selected respondents.
-The results of the survey did not disclose any confidential information that might identify the respondents.
-The survey was a voluntary one but it is unclear if the purpose of the survey explained to the respondents for them to make an informed decision.
 
@@
                                  'caretaker_not_worked_since_birth',
-                                 'caretaker_other')
+                                 'caretaker_other',
+                                 'no_child_under_six',
+                                 'one_more_child_under_six')
     )
@@
 child %>%
-  filter(variable == "no child under six" | variable == "one or more child under six") %>% 
+  filter(variable=='no child under six'|variable=='one or more child under six') %>% 
   ggplot(aes(x = background,

### 2022-04-03 scripts/02-clean_and_prepare_data.R
Update scripts

@@ -11,6 +11,7 @@
 
 #### Workspace set-up ####
 library(tidyverse)
+library(pointblank)
 
 raw_data <- read_csv("outputs/data/raw_data.csv")
 
@@ -41,44 +42,26 @@ rm(col_len,
    i,
    j)
 
-# check the numbers add up to a hundred
-clean$sum_child <- (clean$no_child_under_six + clean$one_more_child_under_six) == 100
-clean_caretaker <- 
-  clean %>%
-  select(starts_with("caretaker_")) %>%
-  mutate(sum_caretaker = rowSums(.))
+agent <-
+  create_agent(tbl = clean) %>%
+  col_is_character(columns = vars(background, character)) %>%
+  col_is_integer(columns = vars(no_child_under_six,
+                                one_more_child_under_six,
+                                caretaker_respondent,
+                                caretaker_partner,
+                                caretaker_other_relative,
+                                caretaker_neighbor,
+                                caretaker_hired,
+                                caretaker_child_in_school,
+                                caretaker_other_female_child,
+                                caretaker_other_male_child,
+                                caretaker_not_worked_since_birth,
+                                caretaker_other,
+                                caretaker_missing,
+                                total,
+                                number_of_employed_women)) %>%
+  interrogate()
 
-clean_caretaker <-
-  bind_cols(clean$background, clean_caretaker, clean$character)
-
-clean<-
-  clean %>%
-  select(-sum_child)
-
-clean2<-
-  clean %>%
-  mutate(
-    no_child_under_six = round(no_child_under_six/100 * number_of_employed_women, 0),
-    one_more_child_under_six = round(one_more_child_under_six/100 * number_of_employed_women, 0)
-  ) %>%
-  mutate(
-    caretaker_respondent = round(caretaker_respondent/100 * one_more_child_under_six, 0),
-    caretaker_partner = round(caretaker_partner/100 * one_more_child_under_six, 0),
-    caretaker_other_relative = round(caretaker_other_relative/100 * one_more_child_under_six, 0),
-    caretaker_neighbor = round(caretaker_neighbor/100 * one_more_child_under_six, 0),
-    caretaker_hired = round(caretaker_hired/100 * one_more_child_under_six, 0),
-    caretaker_child_in_school = round(caretaker_child_in_school/100 * one_more_child_under_six, 0),
[…]

### 2022-04-03 outputs/paper.Rmd

@@
 abstract: "Working mothers are often faced with the conflict of responsibility towards their children and the role they play at work.
-The Ghana Demographic and Health Survey (GDHS) forms a part of a global initiative to collect data on family, fertility, and child health.
+The Ghana Demographic and Health Survey (GDHS) forms part of a global initiative to collect data on family, fertility, and child health.
 In this paper, we used the 1998 GDHS and focused on the child care and working mothers aspect.
@@
 This paper uses the Childcare While Working Data [@ghana1998] obtained from the 1998 Ghana Demographic and Health Survey (GDHS).
-The dataset was collected by downloading the final report of the 1998 GDHS published in the Demographic and Health Surveys (DHS) programme.
+The dataset was collected by downloading the final report of the 1998 GDHS published in the Demographic and Health Surveys (DHS) program.
 The package 'pdftools' [@citepdftools] is used to download and read the content into R by parsing the pdf.
@@
 The questionnaires were made available in the five major local languages (Akan, Ga, Ewe, Hausa, and Dagbani), making the survey accessible to a larger population.
-After the household listing, sports checks were conducted to make sure the work has been done correctly.
+After the household listing, spots checks were conducted to make sure the work has been done correctly.
 Before the actual survey, a test was conducted and adjustments were made to the questionnaires based on the feedback obtained from the test.
 The questions were comprehensive and detailed to collect information on the socio-economic status of the household.
+They were also adapted to the laws and norms of the nation.
 
@@
 The visitor may be from a different region, so the targeted sample size for each region may be skewed.
+There is also the possibility of sampling error.
 
@@
 
-```{r generalchildcare, echo=FALSE, fig.cap="Distribution of the caretaker of the child while mother is working", fig.width=6, fig.height=4}
+```{r generalchildcare, echo=FALSE, fig.cap="Distribution of the child caretaker for working mothers", fig.width=6, fig.height=4}
 totl <-
@@
   theme_minimal() +
-  labs(x='Percentage', y='Caretaker while at work') +
+  labs(x='Caretaker', y='Percent') +
   theme(legend.position='none') +
@@
 
-```{r map, message=FALSE, echo = FALSE, warning=FALSE, fig.cap="Ghana administrative regions"}
+```{r map, message=FALSE, echo = FALSE, warning=FALSE, fig.cap="Ghana administrative regions map"}
 # install.packages('rnaturalearth')
@@
   labs(x = "Area",
-       y = "Percentage",
-       fill = "Child under six") +
+       y = "Percent",
+       fill = "Child status") +
   theme_minimal() +
@@
            position = "dodge") +
-  labs(x = "Caretaker while at work",
-       y = "Percentage",
+  labs(x = "Caretaker",
+       y = "Percent",
        fill = "Area") +
@@
   geom_bar(stat = 'identity') + 
-  labs(x = "Caretaker while at work",
-       y = "Percentage") +
+  labs(x = "Caretaker",
+       y = "Percent") +
   theme_minimal() +
@@
 
-```{r chstatus, echo = FALSE, fig.cap = "Comparing the child status in different administrative regions"}
+```{r chstatus, echo = FALSE, fig.cap = "Comparing child status in different administrative regions"}
 # looking at the number of employed women selected in the different administrative regions
@@
   labs(x = "Administrative regions",
-       y = "Percentage",
-       fill = "Child under six") +
+       y = "Percent",
+       fill = "Child status") +
   theme_minimal() +
@@
 
-```{r motheredu, echo=FALSE, fig.cap="Mother's Education level", fig.width=6, fig.height=4}
+```{r motheredu, echo=FALSE, fig.cap="Comparing the child status of working mothers based on their education level", fig.width=6, fig.height=4}
 # select mother edu
@@
   geom_bar(stat = "identity", position = "dodge") +
-  labs(x = "Mother's education", y = "Number of employed women", fill = "Child under six") +
+  labs(x = "Mother's education level", y = "Number of employed women", fill = "Child status") +
   theme_minimal() +
@@
   theme_minimal() +
-  labs(x='Caretaker while at work', y="Percentage") +
+  labs(x='Caretaker', y="Percent") +
   theme(legend.position='none') +
@@
 
-```{r workstatus, echo=FALSE, message=FALSE, fig.cap="Work status", fig.width=6, fig.height=4}
+```{r workstatus, echo=FALSE, message=FALSE, fig.cap="Comparing the child status of working mothers based on work status", fig.width=6, fig.height=4}
 # select work status
@@
   geom_bar(stat = "identity", position = "dodge") +
-  labs(x = "Work status", y = "Number of employed women", fill = "Child under six") +
+  labs(x = "Work status", y = "Number of employed women", fill = "Child status") +
   theme_minimal() +
@@
 
-```{r occupation, echo=FALSE, message=FALSE, fig.cap="Occupation", fig.width=6, fig.height=4}
+```{r occupation, echo=FALSE, message=FALSE, fig.cap="Comapring child status based on occupation", fig.width=6, fig.height=4}
 # select occupation
@@
        y = "Number of employed women",
-       fill = "Child under six") +
+       fill = "Child status") +
   theme_minimal() +
@@
   geom_bar(stat = "identity", position="dodge") + 
-  labs(x='Caretaker while at work', y="Percentage", fill="Occupation") +
+  labs(x='Caretaker', y="Percent", fill="Occupation") +
   theme_minimal() +
@@
 
-```{r employmentstatus, echo=FALSE, message=FALSE, fig.cap="Employment status", fig.width=6, fig.height=4}
+```{r employmentstatus, echo=FALSE, message=FALSE, fig.cap="Comparing child status based on employment status", fig.width=6, fig.height=4}
 # select employment status
@@
   geom_bar(stat = "identity", position = "dodge") +
-  labs(x = "Employment status", y = "Number of employed women", fill = "Child under six") +
+  labs(x = "Employment status", y = "Number of employed women", fill = "Child status") +
   theme_minimal() +

### 2022-04-03 outputs/paper.Rmd
added the datasheet to the paper appendix

@@
 
+## Datasheet
+
+The questions were extracted from @gebru2021datasheets
+
+**Motivation**
+
+1. *For what purpose was the dataset created? Was there a specific task in mind? Was there a specific gap that needed to be filled? Please provide a description.*
+    - The dataset was created to enable a descriptive analysis of the child care situation of working mothers in Ghana.
+The dataset would be used to look at the trends concerning child caretaking across different factors such as region, work status or occupation area.
+We were unable to find a publicly available dataset.
+2. *Who created the dataset (for example, which team, research group) and on behalf of which entity (for example, company, institution, organization)?*
+    - The dataset was created by Yunkyung Park and Pascal Lee Slew from the University of Toronto.
+3. *Who funded the creation of the dataset? If there is an associated grant, please provide the name of the grantor and the grant name and number.*
+    - No funding was obtained/required for the creation of the dataset.
+4. *Any other comments?*
+    -  None.
+
+**Composition**
+
+1.
+*What do the instances that comprise the dataset represent (for example, documents, photos, people, countries)?
+Are there multiple types of instances (for example, movies, users, and ratings; people and interactions between them; nodes and edges)?
+Please provide a description.*
+	- The dataset consists of categories: residence (urban or rural), regions of Ghana, mothers' education level, work status, occupation and employment status.
+For each category, we have different features: child status (whether families have children under six years old), childcare preferences and the number of employed women.
+2. *How many instances are there in total (of each type, if appropriate)?*
+	- There are 26 rows and 17 columns in the dataset.
+The residence category has 2 rows,  regions has 10 rows, mothers' education level has 4 rows, work status has 3 rows, occupation has 2 rows and employment status has 4 rows.
+3.
+*Does the dataset contain all possible instances or is it a sample (not necessarily random) of instances from a larger set?
+If the dataset is a sample, then what is the larger set?
+Is the sample representative of the larger set (for example, geographic coverage)?
+If so, please describe how this representativeness was validated/verified.
+If it is not representative of the larger set, please describe why not (for example, to cover a more diverse range of instances, because instances were withheld or unavailable).*
+	- The dataset contains all the data possible.
+4. *What data does each instance consist of? "Raw" data (for example, unprocessed text or images) or features? In either case, please provide a description.*
+	- Each category consists of already processed data. The observations are mostly percentages which represent the proportions of categories. 
+5. *Is there a label or target associated with each instance? If so, please provide a description.*
+	- No
+6.
+*Is any information missing from individual instances?
+If so, please provide a description, explaining why this information is missing (for example, because it was unavailable).
+This does not include intentionally removed information, but might include, for example, redacted text.*
+	- Yes, some participants did not respond to all survey questions, leading to some missing data in the data collection process.
+7. *Are relationships between individual instances made explicit (for example, users' movie ratings, social network links)? If so, please describe how these relationships are made explicit.*
+	- No
+8. *Are there recommended data splits (for example, training, development/validation, testing)? If so, please provide a description of these splits, explaining the rationale behind them.*
+	- No
+9. *Are there any errors, sources of noise, or redundancies in the dataset? If so, please provide a description.*
+	- There may be possible sampling error.
+10.
+*Is the dataset self-contained, or does it link to or otherwise rely on external resources (for example, websites, tweets, other datasets)?
+If it links to or relies on external resources, a) are there guarantees that they will exist, and remain constant, over time; b) are there official archival versions of the complete dataset (that is, including the external resources as they existed at the time the dataset was created); c) are there any restrictions (for example, licenses, fees) associated with any of the external resources that might apply to a dataset consumer?
+Please provide descriptions of all external resources and any restrictions associated with them, as well as links or other access points, as appropriate.*
+	- The dataset was extracted from a publicly available pdf at https://dhsprogram.com/publications/publication-FR106-DHS-Final-Reports.cfm
+11.
+*Does the dataset contain data that might be considered confidential (for example, data that is protected by legal privilege or by doctor-patient confidentiality, data that includes the content of individuals' non-public communications)?
+If so, please provide a description.*
+	- No, the results of the survey used to create the dataset were made confidential so that we are unable to identify the participants.
+12. *Does the dataset contain data that, if viewed directly, might be offensive, insulting, threatening, or might otherwise cause anxiety? If so, please describe why.*
+	- None
+13.
+*Does the dataset identify any sub-populations (for example, by age, gender)?
+If so, please describe how these subpopulations are identified and provide a description of their respective distributions within the dataset.*
+	- Yes, the population would be the working mothers.
+Sub-populations would be identified by the categories mentionned above such as employment status, occupation, mothers' education, region, residence and work status.
+14.
+*Is it possible to identify individuals (that is, one or more natural persons), either directly or indirectly (that is, in combination with other data) from the dataset?
+If so, please describe how.*
+	- No
+15.
+*Does the dataset contain data that might be considered sensitive in any way (for example, data that reveals race or ethnic origins, sexual orientations, religious beliefs, political opinions or union memberships, or locations; financial or health data; biometric or genetic data; forms of government identification, such as social security numbers; criminal history)?
+If so, please provide a description.*
+	- No
+16. *Any other comments?*
+	- None
+
+**Collection process**
+
+1.
+*How was the data associated with each instance acquired?
+Was the data directly observable (for example, raw text, movie ratings), reported by subjects (for example, survey responses), or indirectly inferred/derived from other data (for example, part-of-speech tags, model-based guesses for age or language)?
+If the data was reported by subjects or indirectly inferred/derived from other data, was the data validated/verified?
+If so, please describe how.*
+	- No, the data are percentages of categories based on results from the 1998 Ghana Demographic and Health Survey responses.
+2.
+*What mechanisms or procedures were used to collect the data (for example, hardware apparatuses or sensors, manual human curation, software programs, software APIs)?
+How were these mechanisms or procedures validated?*
+	- The data was collected by extracting data from a pdf.
+In our case, we extracted data from a table located at page 45 in the 1998 Ghana Demographic and Health Survey pdf available at the link: https://dhsprogram.com/publications/publication-FR106-DHS-Final-Reports.cfm
+	- The data collection was done using R [@citeR] and R packages tidyverse [@citetidyverse], pdftools [@citepdftools] and stringi [@citestringi].
+	- We used the R package pointblank [@pointblank] to set up tests and check on our dataset.
+3. *If the dataset is a sample from a larger set, what was the sampling strategy (for example, deterministic, probabilistic with specific sampling probabilities)?*
+	- No
+4. *Who was involved in the data collection process (for example, students, crowdworkers, contractors) and how were they compensated (for example, how much were crowdworkers paid)?*
+	- The raw survey data was collected by teams consisting of a team supervisor, a field editor, three interviewers and a driver. They were trained for 3 weeks. No mention of compensation was made.
+5.
+*Over what timeframe was the data collected?
+Does this timeframe match the creation timeframe of the data associated with the instances (for example, recent crawl of old news articles)?
+If not, please describe the timeframe in which the data associated with the instances was created.*
+	- The raw GDHS data was collected from mid-November 1998 to mid-February 1999.
+6.
+*Were any ethical review processes conducted (for example, by an institutional review board)?
+If so, please provide a description of these review processes, including the outcomes, as well as a link or other access point to any supporting documentation.*
+	- The GDHS procedures and survey questionnaires were reviewed by the ICF Institutional Review Board (IRB) of Ghana.
+7. *Did you collect the data from the individuals in question directly, or obtain it via third parties or other sources (for example, websites)?*
+	- The GDHS raw data was collected from individuals directly while the dataset created was created from a publicly available pdf on the DHS website.
+8.
+*Were the individuals in question notified about the data collection?
+If so, please describe (or show with screenshots or other information) how notice was provided, and provide a link or other access point to, or otherwise reproduce, the exact language of the notification itself.*
+	- Yes, the individuals in questions were informed since data collection of the GDHS survey was in person.
+However, for the "raw" data from the pdf, it did not involve individuals directly since their responses were already processed together.
+9.
+*Did the individuals in question consent to the collection and use of their data?
+If so, please describe (or show with screenshots or other information) how consent was requested and provided, and provide a link or other access point to, or otherwise reproduce, the exact language to which the individuals consented.*
+	- For the GDHS survey, the participants consented to the collection and use of their data.
+Their data would be made anonymous and public but they were not explicitly informed that it would be used in this way.
+10.
+*If consent was obtained, were the consenting individuals provided with a mechanism to revoke their consent in the future or for certain uses?
+If so, please provide a description, as well as a link or other access point to the mechanism (if appropriate).*
+	- N/A
+11.
+*Has an analysis of the potential impact of the dataset and its use on data subjects (for example, a data protection impact analysis) been conducted?
+If so, please provide a description of this analysis, including the outcomes, as well as a link or other access point to any supporting documentation.*
+	- N/A
+12. *Any other comments?*
+	- None
+
+**Preprocessing/cleaning/labeling**
+
+1.
+*Was any preprocessing/cleaning/labeling of the data done (for example, discretization or bucketing, tokenization, part-of-speech tagging, SIFT feature extraction, removal of instances, processing of missing values)?
+If so, please provide a description.
+If not, you may skip the remaining questions in this section.*
+	- Yes. The "raw" data obtained from the pdf was cleaned using the tidyverse r package [@citetidyverse] in R [@citeR].
+2.
+*Was the "raw" data saved in addition to the preprocessed/cleaned/labeled data (for example, to support unanticipated future uses)?
+If so, please provide a link or other access point to the "raw" data.*
+	- Yes, both the clean and "raw" data are saved and available at the link:
+	https://github.com/Pascal-304/dhs_analysis/tree/main/outputs/data
+3. *Is the software that was used to preprocess/clean/label the data available? If so, please provide a link or other access point.*
+	- We used the statistical software R [@citeR].
+4. *Any other comments?*
+	- None
+
+**Uses**
+
+1. *Has the dataset been used for any tasks already? If so, please provide a description.*
+	- The dataset has been used to conduct a descriptive analysis of the child care situation of working mothers in Ghana. We used the dataset to create graphs.
+2. *Is there a repository that links to any or all papers or systems that use the dataset? If so, please provide a link or other access point.*
+	- The repository containing all the files pertaining to the dataset is available at https://github.com/Pascal-304/dhs_analysis
+3. *What (other) tasks could the dataset be used for?*
+	- None since the dataset pertained to the childcare situation of working mothers in Ghana only at one time point(1998), so it cannot be used to generalize in other countries or other time points.
+4.	*Is there anything about the composition of the dataset or the way it was collected and preprocessed/cleaned/labeled that might impact future uses?
+For example, is there anything that a dataset consumer might need to know to avoid uses that could result in unfair treatment of individuals or groups (for example, stereotyping, quality of service issues) or other risks or harms (for example, legal risks, financial harms)?
+If so, please provide a description.
+Is there anything a dataset consumer could do to mitigate these risks or harms?*
+	- N/A
+5. *Are there tasks for which the dataset should not be used? If so, please provide a description.*
+	- N/A
+6. *Any other comments?*
+	- None
+
+**Distribution**
+
+1.
+*Will the dataset be distributed to third parties outside of the entity (for example, company, institution, organization) on behalf of which the dataset was created?
+If so, please provide a description.*
+	- Yes, the dataset is publicly available on the internet.
+2. *How will the dataset be distributed (for example, tarball on website, API, GitHub)? Does the dataset have a digital object identifier (DOI)?*
+	- The dataset can be obtained by running the r script "01-gather_data.R" available at the link: https://github.com/Pascal-304/dhs_analysis/blob/main/scripts/01-gather_data.R
+
+4.
+*Will the dataset be distributed under a copyright or other intellectual property (IP) license, and/or under applicable terms of use (ToU)?
+If so, please describe this license and/ or ToU, and provide a link or other access point to, or otherwise reproduce, any relevant licensing terms or ToU, as well as any fees associated with these restrictions.*
+	- No
+5.
+*Have any third parties imposed IP-based or other restrictions on the data associated with the instances?
+If so, please describe these restrictions, and provide a link or other access point to, or otherwise reproduce, any relevant licensing terms, as well as any fees associated with these restrictions.*
+	- Unknown to the authors of the dataset
+6.
+*Do any export controls or other regulatory restrictions apply to the dataset or to individual instances?
+If so, please describe these restrictions, and provide a link or other access point to, or otherwise reproduce, any supporting documentation.*
+	- Unknown to the authors of the dataset
+
+**Maintenance**
+
+1. *Who will be supporting/hosting/maintaining the dataset?*
+	- Pascal Lee Slew and Yunkyung Park
+2. *How can the owner/curator/manager of the dataset be contacted (for example, email address)?*
+	- If anyone want to reach out to us about the dataset, you can contact us at pascal.leeslew@mail.utoronto.ca or clara.park@mail.utoronto.ca
+3. *Is there an erratum? If so, please provide a link or other access point.*
+	- No
+4.
+*Will the dataset be updated (for example, to correct labeling errors, add new instances, delete instances)?
+If so, please describe how often, by whom, and how updates will be communicated to dataset consumers (for example, mailing list, GitHub)?*
+	- If there is any error made in the creation of the dataset, the dataset will be updated by either Yunkyung Park or Pascal Lee Slew.
+Any updates will be communicated as a note in the Readme file at the link below: https://github.com/Pascal-304/dhs_analysis/blob/main/README.md
+5.
+*If the dataset relates to people, are there applicable limits on the retention of the data associated with the instances (for example, were the individuals in question told that their data would be retained for a fixed period of time and then deleted)?
+If so, please describe these limits and explain how they will be enforced.*
+	- N/A
+6. *Will older versions of the dataset continue to be supported/hosted/maintained? If so, please describe how. If not, please describe how its obsolescence will be communicated to dataset consumers.*
+	- The dataset has just been created. If there are any updates, older versions will still be kept for consistency.
+7.
+*If others want to extend/augment/build on/contribute to the dataset, is there a mechanism for them to do so?
+If so, please provide a description.
+Will these contributions be validated/verified?
+If so, please describe how.
+If not, why not?
+Is there a process for communicating/distributing these contributions to dataset consumers?
+If so, please provide a description.*
+	- Others may do so and should contact the original authors about incorporating fixes/extensions.
+
+8. *Any other comments?*
+  - None
+
 \newpage

### 2022-04-03 outputs/paper.Rmd
Appendix
Update paper

--- 2022-04-03 outputs/paper.Rmd
@@
 
-```{r generalchildcare, echo=FALSE, fig.cap="Distribution of the child caretaker for working mothers", fig.width=6, fig.height=4}
+```{r generalchildcare, echo=FALSE, fig.cap="Distribution of the caretaker for working mothers", fig.width=6, fig.height=4}
 totl <-
@@
 It should be noted that 1.9% have not worked since their last birth, and this indicates the percentage of the respondents who were not working at the time of the survey but had been employed at some time during the last 12 months.
+
+\newpage
 
@@
 
-# Appendix
+# (APPENDIX) Appendix {-}
+
+# Datasheet
 

### 2022-04-03 scripts/00-simulation.R
Update preamble

@@ -1,5 +1,5 @@
 #### Preamble ####
-# Purpose: Simulate some data that could resemble the 1988 Ghana census dataset.
+# Purpose: Simulate some data that could resemble the 1988 Ghana Demographic and Health Survey dataset.
 # Author: Pascal Lee Slew, Yunkyung Park
 # Data: 3 April 2022
 # Contact: pascal.leeslew@mail.utoronto.ca, clara.park@mail.utoronto.ca

### 2022-04-03 scripts/02-clean_and_prepare_data.R

@@ -1,5 +1,5 @@
 #### Preamble ####
-# Purpose: Clean and prepare the 1988 clean census data downloaded from the DHS Program
+# Purpose: Clean and prepare the 1988 clean Ghana Demographic and Health Survey data downloaded from the DHS Program
 # Author: Pascal Lee Slew, Yunkyung Park
 # Data: 3 April 2022
 # Contact: pascal.leeslew@mail.utoronto.ca, clara.park@mail.utoronto.ca

### 2022-04-03 scripts/00-simulation.R
Final update in scripts

@@ -18,14 +18,14 @@ set.seed(304)
 simulated_dhs <-
   tibble(
     # Unique identifier
-    'caseID' = 1:3565,
-    # Randomly choose one of the two options, with replacement, 3565 times
+    'caseID' = 1:3564,
+    # Randomly choose one of the two options, with replacement, 3564 times
     'Residence' = sample(
       x = c(
         'Urban',
         'Rural'
       ),
-      size = 3565,
+      size = 3564,
       replace = TRUE
     ),
     'Region' = sample(
@@ -41,7 +41,7 @@ simulated_dhs <-
         'Upper_West',
         'Upper_East'
       ),
-      size = 3565,
+      size = 3564,
       replace = TRUE
     ),
     "Mother's_education" = sample(
@@ -51,7 +51,7 @@ simulated_dhs <-
         'Middle',
         'Secondary+'
       ),
-      size = 3565,
+      size = 3564,
       replace = TRUE
     ),
     'Work_status' = sample(
@@ -60,7 +60,7 @@ simulated_dhs <-
         'For_someone_else',
         'Self-employed'
       ),
-      size = 3565,
+      size = 3564,
       replace = TRUE
     ),
     'Occupation' = sample(
@@ -68,7 +68,7 @@ simulated_dhs <-
         'Agricultural',
         'Nonagricultural'
       ),
-      size = 3565,
+      size = 3564,
       replace = TRUE
     ),
     'Employment_status' = sample(
@@ -78,7 +78,7 @@ simulated_dhs <-
         'Seasonal',
         'Occasional'
       ),
-      size = 3565,
+      size = 3564,
       replace = TRUE
     ),
     'Child_under_six' = sample(
@@ -86,7 +86,7 @@ simulated_dhs <-
         'No',
         'Yes'
       ),
-      size = 3565,
+      size = 3564,
       replace = TRUE
     ),
     'Caretaker' = sample(
@@ -103,7 +103,7 @@ simulated_dhs <-
         'Other',
         'Missing'
         ),
-      size = 3565,
+      size = 3564,
       replace = TRUE
     ),
     )

### 2022-04-03 scripts/02-clean_and_prepare_data.R
Final update in scripts

@@ -45,7 +45,7 @@ rm(col_len,
 agent <-
   create_agent(tbl = clean) %>%
   col_is_character(columns = vars(background, character)) %>%
-  col_is_integer(columns = vars(no_child_under_six,
+  col_is_numeric(columns = vars(no_child_under_six,
                                 one_more_child_under_six,
                                 caretaker_respondent,
                                 caretaker_partner,

### 2022-04-03 scripts/02-clean_and_prepare_data.R
Final update

@@ -1,5 +1,5 @@
 #### Preamble ####
-# Purpose: Clean and prepare the 1988 clean Ghana Demographic and Health Survey data downloaded from the DHS Program
+# Purpose: Clean and prepare the 1988 Ghana Demographic and Health Survey data downloaded from the DHS Program
 # Author: Pascal Lee Slew, Yunkyung Park
 # Data: 3 April 2022
 # Contact: pascal.leeslew@mail.utoronto.ca, clara.park@mail.utoronto.ca
